### 2023-02-20 Conference Submission/DraftDoc.tex
more edits

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[
backend=biber,
style=nature,
sorting=ynt
]{biblatex}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{tikz}
\usepackage{standalone}
\usepackage{svg}
\usepackage{gensymb}
\usepackage{float}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{graphicx, animate}
\usepackage{caption, subcaption}
\usepackage{pgffor}
\usepackage{mathtools}
\addbibresource{bibliography.bib}

\begin{document}

\begin{section}{Introduction}
The modelling of temporal networks is an important task in many real world applications XXXRef.
Temporal networks can be seen as dynamical systems: XXX.
Discovering the underlying equations governing these dynamical systems proves is challenging, because XXX.
Here, we proposes an hybrid statistical and deep learning framework that allows to model temporal networks as continous-time dynamical system, discover a fitting set of differential equations describing it, and, exploiting that discovery, predict the time evolution of a network.

XXX Nodes within the network influence each other and XXX so we might wish to draw on the rich mathematical literature of differential equation modelling.

In the common representation of networks as binary-valued adjacency matrices, the events recorded in a temporal sequence of networks correspond to topological events, such as the appearence or the disappearance of link.
Because of the discrete nature of events, directly modelling the temporal networks as dynamical systems would require to handle discrete jumps.
The topological nature of temporal networks, and the discontinuous character of their temporal evolution, make it challenging to use differential equations techniques.

Here, we overcome the discretness problem by interpreting networks as Random Dot Product Graphs; a well established statistical model for complex networks, that embeds nodes in a low-dimensional metric space[citation]. Creating a singular value decomposition of each of our network observations allows us to view the temporal network as a sample, from which we can model the dynamics of edge existence probabilities across time, now a continuous function. Because the progression of the system can now be viewed as a continuous transformation, we can now look to model the change of this system. To regenerate the network from the embedding, we can simply multiply our embedding matrices together. This will give us a random dot product graph, where the entries (i,j) of the matrix will be the probability of an edge from i to j existing[citation]. In this form, the problem can be viewed as a dynamical system We believe this approach will be useful when applied to areas of medicine, especially protein interaction networks; population dynamics for network ecology; and social network modelling.

By using this process, we also open the possibility of using the endlessly flexible toolbox of machine learning. In this paper we explore the usefulness of neural ODEs, a neural network that is trained to differential equation of temporal data, for discovering the governing function of a set of simple, synthetic temporal networks. This results in a black box DE, which is not very helpful for understanding our systems. To give more insight into what is really going on, we then use symbolic regression to find a function whose output is similar to that of the neural network. By doing this we may further understand the important factors that govern our temporal network.

\end{section}

\begin{section}{Methodology}
    We used a singular value decomposition of each matrix to embed our network in a low dimensional space.\
        \[
        A = U\Sigma V'
        \]
    Where $\Sigma_{ii} = \sigma_i$ and $\sigma_i > sigma_{i+1}$ and each $\sigma_i$ is a non-negative square root of the matrices $AA', \space A'A$. $U$ is a matrix made from the orthonormalised eigenvectors of $AA'$ associated with $\sigma_i$, and $V$ is a matrix made from the orthonormalised eigenvectors of $A'A$ associated with $\sigma_i$. Each row $i$ of $U$ and $V$ represents the in and out position of node $i$ respectively. This can be truncated at an arbitrary number of eigenpairs to form a low dimentional approximation to $A$.
        \[
        A \approx \hat U \hat \Sigma \hat V'
        \]\\
    Where $\hat U, \hat \Sigma, \hat V$ are the first $d$ columns of $U, \Sigma, V$ \cite{golub1971singular}. $\hat U \sqrt{\hat \Sigma}$ is still associated with the in edges of our nodes, and $\sqrt{\hat \Sigma} \hat V' $ is still associated with the out edges of our nodes, but now we have simplified our system whilst keeping as much information as possible due to our descending order of singular values. These two matrices form our $d$ dimensional embedding.\\

    The approximation given by this formula can be interpreted as a graph where the entry $(i,j)$ of the matrix are the probability that an edge exists from $i \rightarrow j$.This approach creates a random dot product graph\cite{athreya2017statistical}, a class of Latent Position Models \cite{hoff2002latent}. Finding the embedding is not trivial; we need to find the eigenpairs of each of $AA'$ and $A'A$. Because of the computational complexity we use the SVD function in Arpack.jl to approximate each matrix. This then changes the problem of discovering edge formation and destruction into learning a dynamical system.\\
    It is important to note that the SVD is not unique. The distances between points will be the same for every embedding, but the orientation may be different, and so, if the SVD of each time step is not alligned, learning will be effectively impossible [<- show this]. Since our approximation method is an iterative approach, to align each SVD, we can simply pick the same initial vector guess for each [probably worth getting a reference].

    Once we have this embedding of points, we look to model the trajectories of each point. That is, with some input data, point location, distance to neighbours, etc, we want to model the ODE of each point. To do this we make use of the SciML ecosystem of packages in the Julia programming language \cite{SciML_C_Rak}. To explore which architectures perform best for this system we then test various types. ~~~~~~~~~~~~~~~~~~~~~~~~\\

    % KNN Explaination
    As a way of limiting the complexity of our model, we limit the input of the neural network to the euclidean distances between the target node and its $k$ nearest neighbours. The target node is the node that we are looking to model the movement of and stays the same throughout each of the temporal networks. 
    \begin{equation}
        \begin{aligned}
            %\centering
            \mathbb{P}(i\rightarrow j)&\coloneqq L_i \cdot R_j\\
            \mathbb{P}(\hat{i}\rightarrow j)&\coloneqq L_{\hat{i}} \cdot R_j
        \end{aligned}
    \end{equation}
    Where $(i,j)$ are nodes in the network and $\hat{i}$ is another node at the same timestep to $i$. This implies that the distance between these two nodes with respect to node $j$ is given by
    \begin{equation}
        \begin{gathered}
            %\centering
            ||\mathbb{P}(i\rightarrow j)-\mathbb{P}(\hat{i}\rightarrow j)||_2 = 
            ||L_i \cdot R_j-L_{\hat{i}} \cdot R_j||_2\\
            =||(L_i -L_{\hat{i}}) \cdot R_j||_2
        \end{gathered}
    \end{equation}
    If we look at the expectation of this, we see
    \begin{equation}
        \begin{gathered}
            %\centering
            \mathbb{E}_j(||(L_i -L_{\hat{i}}) \cdot R_j||_2) = ||L_i -L_{\hat{i}} \cdot \frac{1}{k}\sum_{j\ne i}R_j||_2
        \end{gathered}
    \end{equation}
    Where $k$ is the number of neighbours we chose for the neural network input. Because the distance between points is discribed by the euclidean distance, we use this as our loss metric.

    % Symbolic Regression Explaination
    !!expand on sym reg!! 
    With our trained NODE, we have a black box that approximates the system that governs the movement of Twitter users. To make this more interpretable we then look to approximate this black box into a combination of known functions using symbolic regression[citation (use the one from symreg package)]. For this process we need to define a set of functions which the algorithm will use to generate a tree of functions to find the best approximation to our NODE with. When using this method we usually are required to make two assumptions: that we have paired observations of $y(t), \frac{dy}{dt}$, and that the tree of expressions we will need is shallow. We will train the symbolic regression on the predictions of the neural network. By doing this, we can remove these assumptions\cite{kidger2022neural}.
\end{section}

\begin{section}{Data}
    In this paper we explore this process using three synthetic networks, one which consists of the node we are interested in modelling, the target node, transitioning from one large group to another large group. In the other network the target node slowly moves along a long chain of connected nodes.

    In the 2 community network the communities are of size 40 and 50 and are each fully connected. The target node is initially fully connected to the 50 node community; at each time step one edge is removed between the target node and the 50 node community and replaced with an edge between the target node and the 40 node community \ref{2community train series}. This temporal network has 40 time steps in total, we use the first 20 to train the neural network and the last 20 to test it.

    Figures obtained from \cite{Emma2023}.
    \begin{figure}[H]
        \centering
        \centering
        \begin{subfigure}[c]{0.3\textwidth}
            \centering
            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/2community1.tex}}
            \caption{Simplification of the 2 Community network at $t=1$.}
        \end{subfigure}
        \hfill
        \centering
        \begin{subfigure}[c]{0.3\textwidth}
            \centering
            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/2community2.tex}}
            \caption{Simplification of the 2 Community network at $t=2$.}
        \end{subfigure}
        \hfill
        \centering
        \begin{subfigure}[c]{0.3\textwidth}
            \centering
            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/2community3.tex}}
            \caption{Simplification of the 2 Community network at $t=3$.}
        \end{subfigure}
        \caption{First 3 time steps of synthetic 2 community network.}
        \label{2community train series}
    \end{figure}

    For the long tail network we have a large (50 nodes) fully connected component at one end. This is used to orient the embedding and model. The target node starts attatched to the node that is attatched to this large componet. At each time step the target node move one node further down the tail.
    \begin{figure}[H]
        \centering
        \begin{subfigure}[c]{0.3\textwidth}
            \centering
            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/longTail1.tex}}
            \caption{Simplification of the long tail network at $t=1$.}
        \end{subfigure}
        \hfill
        \centering
        \begin{subfigure}[c]{0.3\textwidth}
            \centering
            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/longTail2.tex}}
            \caption{Simplification of the long tail network at $t=2$.}
        \end{subfigure}
        \hfill
        \centering
        \begin{subfigure}[c]{0.3\textwidth}
            \centering
            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/longTail3.tex}}
            \caption{Simplification of the long tail network at $t=3$.}
        \end{subfigure}\\
        \caption{First 3 time steps of synthetic long tail network.}
    \end{figure}

    We also create a set of three communities. The target node starts connected to all of these communities with each community having a different number of edges. The community with the fewest edges between the target node will have one edge removed at each timestep. The communities have sizes 40, 35, 30 and have 25, 24, and 23 edges to the target node respectively. 
    \begin{figure}[H]
        \centering
        \centering
        \begin{subfigure}[c]{0.3\textwidth}
            \centering
            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/3community1.tex}}
            \caption{Simplification of the 3 Community network at $t=1$.}
        \end{subfigure}
        \hfill
        \centering
        \begin{subfigure}[c]{0.3\textwidth}
            \centering
            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/3community2.tex}}
            \caption{Simplification of the 3 Community network at $t=2$.}
        \end{subfigure}
        \hfill
        \centering
        \begin{subfigure}[c]{0.3\textwidth}
            \centering
            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/3community3.tex}}
            \caption{Simplification of the 3 Community network at $t=3$.}
        \end{subfigure}
        \caption{First 3 time steps of synthetic 3 community network.}
        \label{3community train series}
    \end{figure}
    The 2 community temporal network was selected to illustrate that this process can be used to model a node changing communities in ideal conditions, and the long tail network was selected because we wanted to present these models with a range of problems. The two community problem is difficult for the neural network to learn because the same set of distances as input need to result in different outputs. The long tail problem is difficult for the embedding because a large portion of the network is along the off diagonals; meaning that, to get an accurate embedding, the dimension of the embedding would need to be close to the length of the tail. The three community problem should be the easiest to solve because it has been dileberately constructed to avoid the problems the other two models face.

\end{section}
\begin{section}{Results}
    For each of theses systems, we took embedded the temporal network in two dimensions at each time step. The temporal embeddings were then divided into a training set of 20 and a testing set of 15. The output of the trained neural networks was then used to train a symbolic regression model that could use a simple set of addition, subtraction, division, and multiplication.

    \begin{subsection}{2 Community}
        \begin{figure}
            \foreach \i in {1,...,15} {%
                \begin{subfigure}[p]{0.3\textwidth}
                    \includegraphics[width=\linewidth]{/home/stirling/thesis/Conference Submission/Plots/Test Only/2communities/2communities \i.png}
                    \caption{t=\i}
                \end{subfigure}\quad
            }
            \caption{2 Community test series. This series shows the comparison of the neural network model, the symbolic regression model trained on the neural network model, and the true solution of the two community system.}
            \label{2community series}
        \end{figure}
        In fig \ref{2community series} the green points are the embedded coordinates of the node in each of the communities. Each cluster is one separate community. The orange point is the true coordinate of the embedded target node at each time step. The blue point is our model prediction from the true target node at the first time step. As the time progresses, we see the true node move from one community cluster to the other. This is expected from the embedding; the target node starts as very similar to the first community (as it has many connections with nodes in that community) and as time progresses, it gradually becomes less and less similar to the first community and more similar to the second (as the edges between the target node and the first community are replaced with edges to the second community). As such, we see the target node move towards the second community.

        In this case we see the symbolic regression overshoot the location of the target node and move far ahead of its location by the end of the training data. In contrast, the neural network moves away from the target node at first, then maintain that distance throughout the training data. This system was set up and trained multiple times, and each time we saw the symbolic regression model behave more erratically than the neural network model predictions.
    \end{subsection}

    \begin{subsection}{Long Tail}
        \begin{figure}
            \foreach \i in {1,...,15} {%
                \begin{subfigure}[p]{0.3\textwidth}
                    \includegraphics[width=\linewidth]{/home/stirling/thesis/Conference Submission/Plots/Test Only/longTail/longTail \i.png}
                    \caption{t=\i}
                \end{subfigure}\quad
            }
            \caption{3 Community test series. This series shows the comparison of the neural network model, the symbolic regression model trained on the neural network model, and the true solution of the long tail system.}
            \label{longtail series}
        \end{figure}
        In fig \ref{longtail series} we see the true embedding of the target node jump from one arm to the other at each timestep. It is clear that neither the the symbolic regression model nor the neural network model capture this movement, but the symbolic regression model does not move away from the data as quickly as the neural network model does.

        In contrast to this, the symbolic regression model remains close to the true target node throughout the test data.       
    \end{subsection}

    \begin{subsection}{Three Community (Please Review)}
        \begin{figure}
            \foreach \i in {1,...,15} {%
                \begin{subfigure}[p]{0.3\textwidth}
                    \includegraphics[width=\linewidth]{/home/stirling/thesis/Conference Submission/Plots/Test Only/3community/3community \i.png}
                    \caption{t=\i}
                \end{subfigure}\quad
            }
            \caption{Long tail test series. This series shows the comparison of the neural network model, the symbolic regression model trained on the neural network model, and the true solution of the 3 community system.}
            \label{3community series}
        \end{figure}
        In fig \ref{3community series} we again, as the edges between the community with the fewest edges are removed, we see the target node move away from it in the embedding and towards the other two clusters of points (communities).

        In the neural network only model, we see the prediction follow the true target node very closely at first. We then see the node drift further and further from the true target node. In contrast, the symbolic regression model remains much closer to the true position of the target node as the test data progresses. We see the symbolic regression move slightly ahead of the true location at first, but this distance remains relatively constant thereafter.
    \end{subsection}

\end{section}

\begin{section}{Discussion}
    \begin{subsection}{Two Community}
        It is interesting to see the symbolic regression model perform so much more poorly than the neural network model in this system. When we view the training section of the data, we see that there is a downward curve in the neural network predictions towards the end of the training data. It seems that the symbolic regression model picked this up and continued the downward trajectory throughout the test data. This downward curve may be because the problem that we are trying to solve is symmetrical. That is the same set of distances as input into the neural network, the target node needs to move away from its nearest neighbours in the first half, then move towards its nearest neighbours in the second half. Potential ways of breaking this symmetry may be to include information of the previous timestep, or to include the absolute position of the target node as input into the neural network.

    \end{subsection}

    \begin{subsection}{Long Tail}
        We see that neither the neural network model capture the movement of the target node to any real extent. One reason for this may again be an issue of symmetrical input. The distances from the k nearest neighbours to the target node do not seem to change much as the target node jumps from one arm to the other, but the neural network somehow needs to learn to jump left then right at alternating timesteps. The solutions to this would be the same as for the two community system.
    \end{subsection}
    \begin{subsection}{Three Community}
        This was by far the largest improvement between the neural network and the symbolic regression. This could be because this system had the least difference between the training predictions and the true position of the target node. At the end of the test data we see the true target node move towards the origin. This is because it now only has edges to one community and so at each timestep it removes one of these. If this had continued, the target node would have no edges. Nodes with no edges are mapped to the origin. When this happened, the symbolic regression model prediction began to move further from the true node.

        We see a large difference in the training predictions between the 2 and 3 community systems. In the 2 community system, even in the training period, the predictions tended to wander and be less accurate. Whereas the 3 community training predictions remained very close to the true target node. The movement of the target node in the embedding was very similar between the two systems, and so the difference seems to be that the 2 community has symmetrical inputs.
    \end{subsection}
    Using symbolic regression to approximate the neural network output seems to increase the stability of the extrapolation. This is most pronounced

\begin{section}{Conclusion}
    Not sure what to write for this
\end{section}
\end{section}

% \begin{section}{What Next?}
%     - optimisation\\
%     - Scale up\\
%     - Include more structural knowledge with underlying\\
%     - Find and use real world data to test against
% \end{section}
\printbibliography

\end{document}

% draft for miguel
% all absolute pos of nodes
% polar positions

% questions for Giulio:
%     Why both NN and sym reg not just sym reg
%     Why cos dist

### 2023-02-20 Conference Submission/DraftDoc.tex
more edit 2

@@
 Here, we overcome the discretness problem by interpreting networks as Random Dot Product Graphs; a well established statistical model for complex networks, that embeds nodes in a low-dimensional metric space[citation].
-Creating a singular value decomposition of each of our network observations allows us to view the temporal network as a sample, from which we can model the dynamics of edge existence probabilities across time, now a continuous function.
+In this way we translate the hard problem of modelling discrete events in the space of networks to the easier problem of modelling continous change in the embedding space.
 Because the progression of the system can now be viewed as a continuous transformation, we can now look to model the change of this system.

### 2023-02-21 Conference Submission/DraftDoc.tex
more edits from giulio

@@
 \begin{section}{Introduction}
-The modelling of temporal networks is an important task in many real world applications XXXRef.
-Temporal networks can be seen as dynamical systems: XXX.
-Discovering the underlying equations governing these dynamical systems proves is challenging, because XXX.
-Here, we proposes an hybrid statistical and deep learning framework that allows to model temporal networks as continous-time dynamical system, discover a fitting set of differential equations describing it, and, exploiting that discovery, predict the time evolution of a network.
+The modelling of temporal networks is an important task in many real world applications including symptom interactions for mental health, epidemiology, and protein interactions \cite{jordan2020current,contreras2020temporal,lucas2021inferring,jin2009identifying,masuda2013predicting}.
+Temporal networks can be seen as dynamical systems: that is a system in which we have points, in our case nodes in a network, whose states, the edges connecting them, that vary dependent in time.
+Discovering the underlying equations governing these dynamical systems proves challenging, because changes in network structure are typically observed in the form of discrete jumps from one state to another, for example an edge between two nodes not being observed at the first timestep then appearing at the next.
+Here, we proposes a hybrid statistical and deep learning framework that allows us to model temporal networks as continous-time dynamical systems, discover a fitting set of differential equations describing it, and, exploiting that discovery, predict the time evolution of a network.
 
-XXX Nodes within the network influence each other and XXX so we might wish to draw on the rich mathematical literature of differential equation modelling.
+Differential equations are useful for modelling systems where the state of one variable can effect the trajectories of other variables.
+We observe this behaviour in temporal networks; nodes' connections within the network can influence the formation and decay of edges between other nodes, for example the phenonmenon of preferential attatchment observed in \cite{newman2001clustering,capocci2006preferential}.
+With this in mind we might wish to draw on the rich mathematical literature of differential equation modelling.
 
@@
 
-Here, we overcome the discretness problem by interpreting networks as Random Dot Product Graphs; a well established statistical model for complex networks, that embeds nodes in a low-dimensional metric space[citation].
+Here, we overcome the discretness problem by interpreting networks as Random Dot Product Graphs; a well established statistical model for complex networks, that embeds nodes in a low-dimensional metric space\cite{athreya2017statistical}.
 In this way we translate the hard problem of modelling discrete events in the space of networks to the easier problem of modelling continous change in the embedding space.
-Because the progression of the system can now be viewed as a continuous transformation, we can now look to model the change of this system.
-To regenerate the network from the embedding, we can simply multiply our embedding matrices together.
-This will give us a random dot product graph, where the entries (i,j) of the matrix will be the probability of an edge from i to j existing[citation].
-In this form, the problem can be viewed as a dynamical system We believe this approach will be useful when applied to areas of medicine, especially protein interaction networks; population dynamics for network ecology; and social network modelling.
+Then, we define and use systems of Neural Network Differential Equations (NNDE) to approximate the time evolution of the embedding space, and symbolic regression techniques to discover the functional form of the fitted NNDEs.
+These functional forms are interpretable (as they read as classic differential equations) and allow to predict forward in time the evolution of the temporal networks.
 
-By using this process, we also open the possibility of using the endlessly flexible toolbox of machine learning.
-In this paper we explore the usefulness of neural ODEs, a neural network that is trained to differential equation of temporal data, for discovering the governing function of a set of simple, synthetic temporal networks.
-This results in a black box DE, which is not very helpful for understanding our systems.
-To give more insight into what is really going on, we then use symbolic regression to find a function whose output is similar to that of the neural network.
-By doing this we may further understand the important factors that govern our temporal network.
+In this manuscript, we prove that the temporal network prediction problem can be successfully re-interpreted as a dynamical system modelling problem.
+In particular, we apply our proposed framework to three small example temporal networks with the hope of exploring the limitations and strengths of the proposed framework.
+The framework we are introducing is extremely flexible, and our research regarding the optimal structure of the Neural Networks used for the NNDEs is just started.
+We are confident that future research can identify more fitting Neural Network structures than the simple one adopted here.
+For this reason, we did not yet attempt to benchmark our model against other classic temporal network prediction methods.
+As it is completely general, we believe that the framework we are introducing can be usefully applied to areas of medicine, especially protein interaction networks; population dynamics for network ecology; and social network modelling.
+In particular, we discuss how specific domain knowledge relative to the prediction scenario can be taken into account, moving from NNDEs to Universal Differential Equations.
 
@@
 \begin{section}{Methodology}
-    We used a singular value decomposition of each matrix to embed our network in a low dimensional space.\
+
+    XXX A couple of rows about RDPG XXX
+
+    XXX what are these matrix XXX
+
+    We used a Singular Value Decomposition of each matrix to embed our network in a low dimensional space.\
         \[
@@
         \]
-    Where $\Sigma_{ii} = \sigma_i$ and $\sigma_i > sigma_{i+1}$ and each $\sigma_i$ is a non-negative square root of the matrices $AA', \space A'A$.
-$U$ is a matrix made from the orthonormalised eigenvectors of $AA'$ associated with $\sigma_i$, and $V$ is a matrix made from the orthonormalised eigenvectors of $A'A$ associated with $\sigma_i$.
-Each row $i$ of $U$ and $V$ represents the in and out position of node $i$ respectively.
+    XXX Let's not explain SVD, at most give a ref XXX
     This can be truncated at an arbitrary number of eigenpairs to form a low dimentional approximation to $A$.

### 2023-02-23 Conference Submission/DraftDoc.tex
Updated diagrams for red target node

@@
 \begin{section}{Data}
-    In this paper we explore this process using three synthetic networks, one which consists of the node we are interested in modelling, the target node, transitioning from one large group to another large group.
-In the other network the target node slowly moves along a long chain of connected nodes.
 
-    In the 2 community network the communities are of size 40 and 50 and are each fully connected.
-The target node is initially fully connected to the 50 node community; at each time step one edge is removed between the target node and the 50 node community and replaced with an edge between the target node and the 40 node community \ref{2community train series}.
-This temporal network has 40 time steps in total, we use the first 20 to train the neural network and the last 20 to test it.
+    In this paper we simulate three temporal sequences of graphs.
+For each sequence we will be modelling the node in red, we will refer to this as the target node.
+For each sequence we train the model on the first 20 timesteps and compare the predictions for the next 15 timesteps.
+For clarity, each diagram \ref{2community train series} \ref{longTail train series} \ref{3community train series} has been simplified and illustrates the movement of the target node in each sequence.\\
+
+    The 2 community network has communities of size 40 and 50, each of which are fully connected.
+The target node is initially fully connected to the 50 node community.
+In our simplified diagram \ref{2community train series}\subref{2community train series, a} that is represented by the five node community.
+At each time step one edge is removed between the target node and the larger community and replaced with an edge between the target node and the smaller community \ref{2community train series}\subref{2community train series, b}.
+This process is then continued \ref{2community train series}\subref{2community train series, c} for thirty five timesteps to generate our training and test data.
 
@@
             \caption{Simplification of the 2 Community network at $t=1$.}
+            \label{2community train series, a}
         \end{subfigure}
@@
             \caption{Simplification of the 2 Community network at $t=2$.}
+            \label{2community train series, b}
         \end{subfigure}
@@
             \caption{Simplification of the 2 Community network at $t=3$.}
+            \label{2community train series, c}
         \end{subfigure}
@@
         \caption{First 3 time steps of synthetic long tail network.}
+        \label{longTail train series}
     \end{figure}

### 2023-02-23 Conference Submission/DraftDoc.tex
finisting up for the day

@@
 
-    In this paper we simulate three temporal sequences of graphs.
+    In this paper we simulate three temporal sequences of undirected graphs.
 For each sequence we will be modelling the node in red, we will refer to this as the target node.
@@
 
-    For the long tail network we have a large (50 nodes) fully connected component at one end.
+    In the long tail network \ref{longTail train series}, we have a long chain with fifty nodes and a fully connected component with forty nodes at one end of the chain.
 This is used to orient the embedding and model.
-The target node starts attatched to the node that is attatched to this large componet.
-At each time step the target node move one node further down the tail.
+The target node starts attatched to the node that is attatched to this large componet\ref{longTail train series, a}.
+At each time step the target node move one node further down the tail\ref{longTail train series, b}.
+Again, this is repeated to generate the training and test data \ref{longTail train series, c}.
     \begin{figure}[H]
@@
             \caption{Simplification of the long tail network at $t=1$.}
+            \label{longTail train series, a}
         \end{subfigure}
@@
             \caption{Simplification of the long tail network at $t=2$.}
+            \label{longTail train series, b}
         \end{subfigure}
@@
             \caption{Simplification of the long tail network at $t=3$.}
+            \label{longTail train series, c}
         \end{subfigure}\\

### 2023-03-01 Conference Submission/DraftDoc.tex
Updating on friday

@@
 \addbibresource{bibliography.bib}
+\usepackage{hyperref,thmtools}
+
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{remark*}[theorem]{Remark}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{sublemma}{}[theorem]
+\newtheorem{conjecture}[theorem]{Conjecture}
+
+% Override ugly default link
+\hypersetup{
+  colorlinks   = true, %Colours links instead of ugly boxes
+  urlcolor     = blue, %Colour for external hyperlinks
+  linkcolor    = blue, %Colour of internal links
+  citecolor   = blue    %Colour of citations
+}
 
@@
 \begin{section}{Methodology}
+    We are given a sequence of graphs, and our goal is to predict the next graph in the sequence.
+To do this we read each graph as a Random Dot Product Graph (RDPG); a visual representation of this can be seen in \autoref{framework illustration}.
+To obtain the RDPG, we take each network observation \autoref{method nets} and represent them in the form of an adjacency matrix \autoref{method adjacency}.
+We then use a truncated singular value decomposition to reduce the dimensionality of our adjacency matrices[ref].
+The rows of the output of the SVD can then be viewed as vector points in a d-dimensional space[ref], where d is the number of singular values we take for our SVD.
+In this space nodes that are similar, ie, nodes have many common neighbours, will be mapped to similar points in the space.
+    \begin{figure}
+    \centering
+    \begin{subfigure}[c]{1\textwidth}
+        \begin{tabular}{llll}
+        \begin{subfigure}[c]{0.25\textwidth}
+            \centering
+            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology1.tex}}
+            \label{method net, a}
+        \end{subfigure}
+        &
+        \centering
+        \begin{subfigure}[c]{0.25\textwidth}
+            \centering
+            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology2.tex}}
+            \label{method net, b}
+        \end{subfigure}
+        &
+        $\cdots$
+        &
+        \centering
+        \begin{subfigure}[c]{0.25\textwidth}
+            \centering
+            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology3.tex}}
+            \label{method net, c}
+        \end{subfigure}
 
-    XXX A couple of rows about RDPG XXX
+        \end{tabular}
+        \caption{Example sequence of networks.}
+        \label{method nets}
 
-    XXX what are these matrix XXX
+    \end{subfigure}
+    \begin{subfigure}[c]{1\textwidth}
+        \begin{tabular}{llll}
+            $\begin{bmatrix}
+                \cdot & 1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
+                1 & \cdot & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
+                1 & 1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot\\
+                1 & \cdot & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
+                \cdot & \cdot & 1 & \cdot & \cdot & 1 & 1 & \cdot\\
+                \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & \cdot\\
+                \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & 1\\
+                \cdot & \cdot & \cdot & \cdot & \cdot & \cdot & 1 & \cdot
+            \end{bmatrix}$
+            &
+            $\begin{bmatrix}
+                \cdot & 1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
+                1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
+                1 & 1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot\\
+                1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
+                \cdot & \cdot & 1 & \cdot & \cdot & 1 & 1 & \cdot\\
+                \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & 1\\
+                \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & 1\\
+                \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot
+            \end{bmatrix}$
+            &
+            $\cdots$
+            &
+            $\begin{bmatrix}
+                \cdot & 1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
+                1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
+                1 & 1 & \cdot & 1 & \cdot & \cdot & \cdot & \cdot\\
+                1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
+                \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot\\
+                \cdot & \cdot & \cdot & \cdot & 1 & \cdot & 1 & 1\\
+                \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot & 1\\
+                \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot
+            \end{bmatrix}$
 
-    We used a Singular Value Decomposition of each matrix to embed our network in a low dimensional space.\
-        \[
-        A = U\Sigma V'
-        \]
-    XXX Let's not explain SVD, at most give a ref XXX
-    This can be truncated at an arbitrary number of eigenpairs to form a low dimentional approximation to $A$.
-        \[
-        A \approx \hat U \hat \Sigma \hat V'
-        \]\\
-    Where $\hat U, \hat \Sigma, \hat V$ are the first $d$ columns of $U, \Sigma, V$ \cite{golub1971singular}.
+        \end{tabular}
+        \caption{Sequence of sparce adjacency matrices associated with the networks in \autoref{method nets}.}
+        \label{method adjacency}
+    \end{subfigure}
+
+        \begin{tabular}{llll}
+
+        \end{tabular}
+
+        \caption{Visual illustration of the proposed framework.}
+        \label{framework illustration}
+    \end{figure}
+
+    We used a Singular Value Decomposition of each adjacency matrix to embed our network in a low dimensional space.
+To execute the SVD\cite{golub1971singular} we use the Julia package [cite].
+This package uses implicitly restarted Lanczos iterations\cite{lehoucq1996deflation} to approximate the eigen vectors and singular values of each of our adjacency matrices.
+From the "svds" function, we obtain two matrices, $L$ and $R$ where:\\
+    \begin{align}
+        L&=\hat L \sqrt{\hat \Sigma }\\
+        R &= \hat R \sqrt{\hat \Sigma }\\
+        A &\approx \hat L \hat \Sigma \hat R'\\
+        &\approx LR'
+    \end{align}
+    $L,\hat L, R, \hat R$ are each real valued $n\times d$ matrices, where the columns of $\hat L$ and $\hat R$ are the first $d$ eigenvectors of $AA'$ and $A'A$ respectively ordered by the size of their associated singular values.
+$\hat \Sigma$ is a $d\times d$ diagonal matrix whose entries are the singular values associated with each eigenvector.
+\\
+    It is important to note that the SVD is not unique.
+The distances between points will be the same for every embedding, but the orientation may be different, and so, if the SVD of each time step is not alligned, learning will be effectively impossible [<- show this].
+Since our approximation method is an iterative approach, to align each SVD, we can simply pick the same initial vector guess for each [probably worth getting a reference]; this will cause the outputs of the Arpack function to each be aligned with eachother XXX with some requirements of the matrix/initial vec?XXX.
+Altenatively we can use Procrustes alignmet[cite package] to align the matrices after they have been generated.\\
+    The approximation  given by this formula can be interpreted as a graph where the entry $(i,j)$ of the matrix are the probability that an edge exists from $i \rightarrow j$.This approach creates a Random Dot Product Graph\cite{athreya2017statistical}, a class of Latent Position Models \cite{hoff2002latent}.
+Once we have this embedding of points, we look to model the trajectories of each point.
+That is, with some input data, point location, distance to neighbours, etc, we want to model the ODE of each point.
+To do this we make use of the SciML ecosystem of packages in the Julia programming language \cite{SciML_C_Rak}.\\
+
+    % IN THE THESIS MAYBE
+    % This can be truncated at an arbitrary number of eigenpairs to form a low dimentional approximation to $A$.
+    %     \[
+    %     A \approx \hat U \hat \Sigma \hat V'
+    %     \]\\
+    % Where $\hat U, \hat \Sigma, \hat V$ are the first $d$ columns of $U, \Sigma, V$ \cite{golub1971singular}.
 $\hat U \sqrt{\hat \Sigma}$ is still associated with the in edges of our nodes, and $\sqrt{\hat \Sigma} \hat V' $ is still associated with the out edges of our nodes, but now we have simplified our system whilst keeping as much information as possible due to our descending order of singular values.
 These two matrices form our $d$ dimensional embedding.\\
-
-    The approximation given by this formula can be interpreted as a graph where the entry $(i,j)$ of the matrix are the probability that an edge exists from $i \rightarrow j$.This approach creates a random dot product graph\cite{athreya2017statistical}, a class of Latent Position Models \cite{hoff2002latent}.
-Finding the embedding is not trivial; we need to find the eigenpairs of each of $AA'$ and $A'A$.
-Because of the computational complexity we use the SVD function in Arpack.jl to approximate each matrix.
-This then changes the problem of discovering edge formation and destruction into learning a dynamical system.\\
-    It is important to note that the SVD is not unique.
-The distances between points will be the same for every embedding, but the orientation may be different, and so, if the SVD of each time step is not alligned, learning will be effectively impossible [<- show this].
-Since our approximation method is an iterative approach, to align each SVD, we can simply pick the same initial vector guess for each [probably worth getting a reference].
-
-    Once we have this embedding of points, we look to model the trajectories of each point.
-That is, with some input data, point location, distance to neighbours, etc, we want to model the ODE of each point.
-To do this we make use of the SciML ecosystem of packages in the Julia programming language \cite{SciML_C_Rak}.
-To explore which architectures perform best for this system we then test various types.
-~~~~~~~~~~~~~~~~~~~~~~~~\\
 
@@
 The target node is the node that we are looking to model the movement of and stays the same throughout each of the temporal networks.
-    \begin{equation}
-        \begin{aligned}
+    \begin{align}
         %\centering
@@
         \mathbb{P}(\hat{i}\rightarrow j)&\coloneqq L_{\hat{i}} \cdot R_j
-        \end{aligned}
-    \end{equation}
+    \end{align}
     Where $(i,j)$ are nodes in the network and $\hat{i}$ is another node at the same timestep to $i$. This implies that the distance between these two nodes with respect to node $j$ is given by
@@
     % Symbolic Regression Explaination
-    !!expand on sym reg!! 
     With our trained NODE, we have a black box that approximates the system that governs the movement of Twitter users.
@@
 For each sequence we train the model on the first 20 timesteps and compare the predictions for the next 15 timesteps.
-For clarity, each diagram \ref{2community train series} \ref{longTail train series} \ref{3community train series} has been simplified and illustrates the movement of the target node in each sequence.\\
+For clarity, each diagram \autoref{2community train series} \autoref{longTail train series} \autoref{3community train series} has been simplified and illustrates the movement of the target node in each sequence.\\
 
@@
 The target node is initially fully connected to the 50 node community.
-In our simplified diagram \ref{2community train series}\subref{2community train series, a} that is represented by the five node community.
-At each time step one edge is removed between the target node and the larger community and replaced with an edge between the target node and the smaller community \ref{2community train series}\subref{2community train series, b}.
-This process is then continued \ref{2community train series}\subref{2community train series, c} for thirty five timesteps to generate our training and test data.
+In our simplified diagram \autoref{2community train series, a} that is represented by the five node community.
+At each time step one edge is removed between the target node and the larger community and replaced with an edge between the target node and the smaller community \autoref{2community train series, b}.
+This process is then continued \autoref{2community train series, c} for thirty five timesteps to generate our training and test data.
 
@@
 
-    In the long tail network \ref{longTail train series}, we have a long chain with fifty nodes and a fully connected component with forty nodes at one end of the chain.
+    In the long tail network \autoref{longTail train series}, we have a long chain with fifty nodes and a fully connected component with forty nodes at one end of the chain.
 This is used to orient the embedding and model.
-The target node starts attatched to the node that is attatched to this large componet\ref{longTail train series, a}.
-At each time step the target node move one node further down the tail\ref{longTail train series, b}.
-Again, this is repeated to generate the training and test data \ref{longTail train series, c}.
+The target node starts attatched to the node that is attatched to this large componet \autoref{longTail train series, a}.
+At each time step the target node move one node further down the tail \autoref{longTail train series, b}.
+Again, this is repeated to generate the training and test data \autoref{longTail train series, c}.
     \begin{figure}[H]
@@
 
-    We also create a set of three communities.
-The target node starts connected to all of these communities with each community having a different number of edges.
-The community with the fewest edges between the target node will have one edge removed at each timestep.
+    We also simulate a sequence with three communities.
 The communities have sizes 40, 35, 30 and have 25, 24, and 23 edges to the target node respectively.
+In \autoref{3community train series} the communities have been simplified to have sizes of five, four, and 3.
+The target node starts connected to all of these communities with each community having a different number of edges \autoref{3community train series, a}.
+The community with the fewest edges between the target node will have one edge removed at each timestep \autoref{3community train series, b}, and this process is repeated to create the required number of timesteps \autoref{3community train series, c}.
     \begin{figure}[H]
@@
             \caption{Simplification of the 3 Community network at $t=1$.}
+            \label{3community train series, a}
         \end{subfigure}
@@
             \caption{Simplification of the 3 Community network at $t=2$.}
+            \label{3community train series, b}            
         \end{subfigure}
@@
             \caption{Simplification of the 3 Community network at $t=3$.}
+            \label{3community train series, c}
         \end{subfigure}
@@
 \end{section}
-\begin{section}{Results}
+
+\begin{section}{Results and Discussion}
     For each of theses systems, we took embedded the temporal network in two dimensions at each time step.
@@
 The output of the trained neural networks was then used to train a symbolic regression model that could use a simple set of addition, subtraction, division, and multiplication.
-
+\\
+    In fig \autoref{2community series}, \autoref{longtail series},\autoref{3community series} the green points are the embedded coordinates of the node in each of the communities.
+Each cluster is one separate community.
+The orange point is the true coordinate of the embedded target node at each time step.
+The blue point is our model prediction from the true target node at the first time step.
+As the time progresses, we see the true node move from one community cluster to the other.
+This is expected from the embedding; the target node starts as very similar to the first community (as it has many connections with nodes in that community) and as time progresses, it gradually becomes less and less similar to the first community and more similar to the second (as the edges between the target node and the first community are replaced with edges to the second community).
+As such, we see the target node move towards the second community.
     \begin{subsection}{2 Community}
@@
         \end{figure}
-        In fig \ref{2community series} the green points are the embedded coordinates of the node in each of the communities.
-Each cluster is one separate community.
-The orange point is the true coordinate of the embedded target node at each time step.
-The blue point is our model prediction from the true target node at the first time step.
-As the time progresses, we see the true node move from one community cluster to the other.
-This is expected from the embedding; the target node starts as very similar to the first community (as it has many connections with nodes in that community) and as time progresses, it gradually becomes less and less similar to the first community and more similar to the second (as the edges between the target node and the first community are replaced with edges to the second community).
-As such, we see the target node move towards the second community.
 
@@
 In contrast, the neural network moves away from the target node at first, then maintain that distance throughout the training data.
-This system was set up and trained multiple times, and each time we saw the symbolic regression model behave more erratically than the neural network model predictions.
+This system was set up and trained multiple times, and each time we saw the symbolic regression model behave more erratically than the neural network model predictions.\\
+
+        It is interesting to see the symbolic regression model perform so much more poorly than the neural network model in this system.
+When we view the training section of the data, we see that there is a downward curve in the neural network predictions towards the end of the training data.
+It seems that the symbolic regression model picked this up and continued the downward trajectory throughout the test data.
+This downward curve may be because the problem that we are trying to solve is symmetrical.
+That is the same set of distances as input into the neural network, the target node needs to move away from its nearest neighbours in the first half, then move towards its nearest neighbours in the second half.
+Potential ways of breaking this symmetry may be to include information of the previous timestep, or to include the absolute position of the target node as input into the neural network.
     \end{subsection}
@@
         \end{figure}
-        In fig \ref{longtail series} we see the true embedding of the target node jump from one arm to the other at each timestep.
+        In fig \autoref{longtail series} we see the true embedding of the target node jump from one arm to the other at each timestep.
 It is clear that neither the the symbolic regression model nor the neural network model capture this movement, but the symbolic regression model does not move away from the data as quickly as the neural network model does.
@@
         In contrast to this, the symbolic regression model remains close to the true target node throughout the test data.
+
+        We see that neither the neural network model capture the movement of the target node to any real extent.
+One reason for this may again be an issue of symmetrical input.
+The distances from the k nearest neighbours to the target node do not seem to change much as the target node jumps from one arm to the other, but the neural network somehow needs to learn to jump left then right at alternating timesteps.
+The solutions to this would be the same as for the two community system.
     \end{subsection}
@@
         \end{figure}
-        In fig \ref{3community series} we again, as the edges between the community with the fewest edges are removed, we see the target node move away from it in the embedding and towards the other two clusters of points (communities).
+        In fig \autoref{3community series} we again, as the edges between the community with the fewest edges are removed, we see the target node move away from it in the embedding and towards the other two clusters of points (communities).
 
@@
 We see the symbolic regression move slightly ahead of the true location at first, but this distance remains relatively constant thereafter.
-    \end{subsection}
 
-\end{section}
-
-\begin{section}{Discussion}
-    \begin{subsection}{Two Community}
-        It is interesting to see the symbolic regression model perform so much more poorly than the neural network model in this system.
-When we view the training section of the data, we see that there is a downward curve in the neural network predictions towards the end of the training data.
-It seems that the symbolic regression model picked this up and continued the downward trajectory throughout the test data.
-This downward curve may be because the problem that we are trying to solve is symmetrical.
-That is the same set of distances as input into the neural network, the target node needs to move away from its nearest neighbours in the first half, then move towards its nearest neighbours in the second half.
-Potential ways of breaking this symmetry may be to include information of the previous timestep, or to include the absolute position of the target node as input into the neural network.
-
-    \end{subsection}
-
-    \begin{subsection}{Long Tail}
-        We see that neither the neural network model capture the movement of the target node to any real extent.
-One reason for this may again be an issue of symmetrical input.
-The distances from the k nearest neighbours to the target node do not seem to change much as the target node jumps from one arm to the other, but the neural network somehow needs to learn to jump left then right at alternating timesteps.
-The solutions to this would be the same as for the two community system.
-    \end{subsection}
-    \begin{subsection}{Three Community}
         This was by far the largest improvement between the neural network and the symbolic regression.
@@
     \end{subsection}
-    Using symbolic regression to approximate the neural network output seems to increase the stability of the extrapolation. This is most pronounced
+
+\end{section}
 
 \begin{section}{Conclusion}
-    Not sure what to write for this
-\end{section}
+    Not sure what to write for this\\
+    Using symbolic regression to approximate the neural network output seems to increase the stability of the extrapolation. This is most pronounced 
 \end{section}
 
-% \begin{section}{What Next?}
-%     - optimisation\\
-%     - Scale up\\
-%     - Include more structural knowledge with underlying\\
-%     - Find and use real world data to test against
-% \end{section}
 \printbibliography

### 2023-04-03 Code/Model Tweaks/1NN vs 2NN/1NN with for loop.jl
First try for final results

@@ -23,10 +23,8 @@ include("../../_Modular Functions/reconstructRDPG.jl")
 
 rng = Random.default_rng()
 nn = Lux.Chain(x -> x,
-      Lux.Dense(input_data_length, 32, tanh),
-      Lux.Dense(32, 8),
-      Lux.Dense(8, 4),
-      Lux.Dense(4, output_data_length))
+      Lux.Dense(input_data_length, 64, tanh),
+      Lux.Dense(64, output_data_length))
 
 p, st = Lux.setup(rng, nn)
 
@@ -70,16 +68,35 @@ TNode_data = targetNode(t_data[1:datasize],1)
 
 #prob_neuralode = remake(prob_neuralode, u0=u0)
 result = Optimization.solve(optprob,
-                            ADAM(0.005),
+                            Optim.SimulatedAnnealing(),
                             callback = callback,
-                            maxiters = 600)
+                            maxiters = 10^4, 
+                            maxtime=5*10^2)
 optprob = remake(optprob, u0=result.u)
+println("ping")
 
+predict_neuralode(result.u)
+
+result = Optimization.solve(optprob,
+                            Optim.SimulatedAnnealing(),
+                            callback = callback,
+                            maxiters = 10^4, 
+                            maxtime=10^4)
+optprob = remake(optprob, u0=result.u)
+println("ping")
+loss_neuralode(result.u)
 result = Optimization.solve(optprob,
                             Optim.BFGS(initial_stepnorm=0.001),
                             callback = callback,
-                            maxiters = 200)
-optprob = remake(optprob, u0=result.u)
+                            maxiters = 500)
+
+# result = Optimization.solve(optprob,
+# ADAM(0.001),
+# callback = callback,
+# maxiters = 100)
+# optprob = remake(optprob, u0=result.u)
+
+
 # println("Part 2")
 # result = Optimization.solve(optprob,
 #                             BFGS(),
@@ -91,8 +108,10 @@ println("Done")
 
 #include("../../_Modular Functions/createFullSltn.jl")
 
+collect(1.0:0.01:datasize)
+
 global train_data = withoutNode(t_data,1)
-global tsteps = range(1.0, Float64(length(t_data)), length = 100*length(t_data))
+global tsteps = tspan[1]:0.01:tspan[2]
 prob_neuralode = ODEProblem{false}(dudt_pred_, u0, tspan, p)
 prob_neuralode = remake(prob_neuralode, tspan=(1.0,Float64(length(t_data))))
 function predict_neuralode(θ)

### 2023-04-03 Code/Symbolic Regression/symreg.jl

@@ -1,4 +1,5 @@
 using SymbolicRegression
+using SymbolicUtils
 using DelimitedFiles
 include("../_Modular Functions/helperFunctions.jl")
 
@@ -6,8 +7,9 @@ sltn = readdlm("./Code/Solutions/$net_name.csv", ',')
 sltnt = readdlm("./Code/Solutions/$net_name test only.csv", ',')
 grad_sltn = sltn[:,2:end].-sltn[:,1:end-1]
 
+test_range = eachindex(1.0:0.01:Float64(datasize))
 
-trace = scatter(x=sltn[1,1:datasize*100],y=sltn[2,1:datasize*100], mode="markers", name="sltn from start")
+trace = scatter(x=sltn[1,:],y=sltn[2,:], mode="markers", name="sltn from start")
 trace2 =  scatter(x=[t_data[i][1,1] for i in 1:datasize],y=[t_data[i][2,1] for i in 1:datasize], mode="markers", name="train")
 trace3 =  scatter(x=[t_data[i+datasize][1,1] for i in 1:length(t_data)-datasize],y=[t_data[i+datasize][2,1] for i in 1:length(t_data)-datasize], mode="markers", name="test")
 trace4 =  scatter(x=sltnt[1,1:end],y=sltnt[2,1:end], mode="markers", name="sltn from test")
@@ -15,7 +17,7 @@ trace4 =  scatter(x=sltnt[1,1:end],y=sltnt[2,1:end], mode="markers", name="sltn 
 plot([trace, trace2, trace3, trace4])
 
 train_data = withoutNode(t_data,1)
-
+train_data[1]
 
 function dists(u,t)
     M = train_data[t]
@@ -28,7 +30,7 @@ function dists(u,t)
 end
 
 iter_sltn = [sltn[:,i] for i in 1:size(sltn)[2]]
-data = dists.(iter_sltn, 1.0:0.01:Float64(length(t_data)))
+data = dists.(iter_sltn, 1.0:0.01:Float64(datasize))
 data = hcat(data...)
 
 options = SymbolicRegression.Options(
@@ -37,7 +39,7 @@ options = SymbolicRegression.Options(
 )
 halls = [
     EquationSearch(
-    data[:,1:datasize*100], grad_sltn[i,1:datasize*100], niterations=40, options=options,
[…]

### 2023-04-03 Code/_Modular Functions/plotSltn.jl

@@ -24,7 +24,7 @@ using DelimitedFiles
 
 sltn = readdlm("./Code/Solutions/$net_name test only.csv", ',')
 
-for i in 1:datasize
+for i in 1:length(t_data)-datasize
     pts = t_data[i+datasize]'#get_embedding([sltn_sym_reg[:,i]'; t_data[i+datasize]], sltn[:,i])
     mid = convert(Int, dims[1]/2)
     traces0 = PlotlyJS.scatter(x=[sltn[1,i]], y=[sltn[2,i]], mode="markers", name="Neural Network Pred", marker_size=12)

### 2023-04-06 Conference Submission/DraftDoc.tex
Started on the lit review

@@
-\documentclass{article}
+\documentclass[12pt]{amsart}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{float}
-\usepackage[margin=1in]{geometry}
+\usepackage{geometry}
 \usepackage{hyperref}
@@
 \usepackage{mathtools}
+\usepackage{array}
 \addbibresource{bibliography.bib}
 \usepackage{hyperref,thmtools}
+\linespread{1.5}
 
@@
 The modelling of temporal networks is an important task in many real world applications including symptom interactions for mental health, epidemiology, and protein interactions \cite{jordan2020current,contreras2020temporal,lucas2021inferring,jin2009identifying,masuda2013predicting}.
-Temporal networks can be seen as dynamical systems: that is a system in which we have points, in our case nodes in a network, whose states, the edges connecting them, that vary dependent in time.
-Discovering the underlying equations governing these dynamical systems proves challenging, because changes in network structure are typically observed in the form of discrete jumps from one state to another, for example an edge between two nodes not being observed at the first timestep then appearing at the next.
+Temporal networks can be seen as dynamical systems: that is, a system in which we have points, in our case nodes in a network, whose states, the edges connecting them, vary dependent in time.
+Discovering the underlying equations governing these dynamical systems proves challenging, because changes in network structure are typically observed in the form of discrete jumps from one state to another, that is, an edge may exist between two nodes at one timestep then dissapear at the next.
+There cannot be an edge that has half decayed.
 Here, we proposes a hybrid statistical and deep learning framework that allows us to model temporal networks as continous-time dynamical systems, discover a fitting set of differential equations describing it, and, exploiting that discovery, predict the time evolution of a network.
@@
 We observe this behaviour in temporal networks; nodes' connections within the network can influence the formation and decay of edges between other nodes, for example the phenonmenon of preferential attatchment observed in \cite{newman2001clustering,capocci2006preferential}.
-With this in mind we might wish to draw on the rich mathematical literature of differential equation modelling.
+With this observation in mind we might wish to draw on the rich mathematical literature of differential equation modelling.
 
 In the common representation of networks as binary-valued adjacency matrices, the events recorded in a temporal sequence of networks correspond to topological events, such as the appearence or the disappearance of link.
-Because of the discrete nature of events, directly modelling the temporal networks as dynamical systems would require to handle discrete jumps.
+Because of the discrete nature of events, directly modelling the temporal networks as dynamical systems would require the model to handle discrete jumps.
 The topological nature of temporal networks, and the discontinuous character of their temporal evolution, make it challenging to use differential equations techniques.
 
-Here, we overcome the discretness problem by interpreting networks as Random Dot Product Graphs; a well established statistical model for complex networks, that embeds nodes in a low-dimensional metric space\cite{athreya2017statistical}.
+Here, we overcome the discretness problem by interpreting networks as Random Dot Product Graphs, a well established statistical model for complex networks, that embeds nodes in a low-dimensional metric space\cite{athreya2017statistical}.
 In this way we translate the hard problem of modelling discrete events in the space of networks to the easier problem of modelling continous change in the embedding space.
@@
 For this reason, we did not yet attempt to benchmark our model against other classic temporal network prediction methods.
-As it is completely general, we believe that the framework we are introducing can be usefully applied to areas of medicine, especially protein interaction networks; population dynamics for network ecology; and social network modelling.
+As it is completely general, we believe that the framework we are introducing can be usefully applied to areas of medicine, especially protein interaction networks; population dynamics for network ecology; and social network modelling[citation].
 In particular, we discuss how specific domain knowledge relative to the prediction scenario can be taken into account, moving from NNDEs to Universal Differential Equations.
@@
     We are given a sequence of graphs, and our goal is to predict the next graph in the sequence.
-To do this we read each graph as a Random Dot Product Graph (RDPG); a visual representation of this can be seen in \autoref{framework illustration}.
+To do this we read each graph as a Random Dot Product Graph (RDPG); a visual representation of this process can be seen in \autoref{framework illustration}.
 To obtain the RDPG, we take each network observation \autoref{method nets} and represent them in the form of an adjacency matrix \autoref{method adjacency}.
 We then use a truncated singular value decomposition to reduce the dimensionality of our adjacency matrices[ref].
-The rows of the output of the SVD can then be viewed as vector points in a d-dimensional space[ref], where d is the number of singular values we take for our SVD.
+This truncation introduces some loss, but can dramatically reduce the size of our problem [cite].
+XXXX It should be noted that when we plot our models, we compare them to this embedding and do not take into account this truncation loss.XXXX The rows of the output of the SVD can then be viewed as vector points in a d-dimensional space[ref], where d is the number of singular values we take for our SVD.
 In this space nodes that are similar, ie, nodes have many common neighbours, will be mapped to similar points in the space.
@@
 Altenatively we can use Procrustes alignmet[cite package] to align the matrices after they have been generated.\\
-    The approximation  given by this formula can be interpreted as a graph where the entry $(i,j)$ of the matrix are the probability that an edge exists from $i \rightarrow j$.This approach creates a Random Dot Product Graph\cite{athreya2017statistical}, a class of Latent Position Models \cite{hoff2002latent}.
+    The approximation  given by this formula can be interpreted as a graph where the entry $(i,j)$ of the matrix is the probability that an edge exists from $i \rightarrow j$.This approach creates a Random Dot Product Graph\cite{athreya2017statistical}, a class of Latent Position Models \cite{hoff2002latent}.
 Once we have this embedding of points, we look to model the trajectories of each point.
@@
     % Symbolic Regression Explaination
-    With our trained NODE, we have a black box that approximates the system that governs the movement of Twitter users.
+    With our trained NODE, we have a black box that approximates the system that governs the movement of the target node in the embedded space.
 To make this more interpretable we then look to approximate this black box into a combination of known functions using symbolic regression[citation (use the one from symreg package)].
@@
                 \begin{subfigure}[p]{0.3\textwidth}
-                    \includegraphics[width=\linewidth]{/home/stirling/thesis/Conference Submission/Plots/Test Only/2communities/2communities \i.png}
+                    \includegraphics[width=\linewidth]{./Plots/Test Only/2communities/2communities \i.png}
                     \caption{t=\i}
@@
 
-        In this case we see the symbolic regression overshoot the location of the target node and move far ahead of its location by the end of the training data.
-In contrast, the neural network moves away from the target node at first, then maintain that distance throughout the training data.
-This system was set up and trained multiple times, and each time we saw the symbolic regression model behave more erratically than the neural network model predictions.\\
+        In this case we see the neural network in one timestep jumps to around (-1.75, 0.4) where it remains until the end of the training data.
+In contrast, the symbolic regression remains relatively close to the true target node until the last time step when the symbolic regression moves away from the target node.\\
 
-        It is interesting to see the symbolic regression model perform so much more poorly than the neural network model in this system.
+        % It is interesting to see the symbolic regression model perform so much more poorly than the neural network model in this system.
 When we view the training section of the data, we see that there is a downward curve in the neural network predictions towards the end of the training data.
@@
                 \begin{subfigure}[p]{0.3\textwidth}
-                    \includegraphics[width=\linewidth]{/home/stirling/thesis/Conference Submission/Plots/Test Only/longTail/longTail \i.png}
+                    \includegraphics[width=\linewidth]{./Plots/Test Only/longTail/longTail \i.png}
                     \caption{t=\i}
@@
             }
-            \caption{3 Community test series.
+            \caption{Long Tail test series.
 This series shows the comparison of the neural network model, the symbolic regression model trained on the neural network model, and the true solution of the long tail system.}
@@
         In fig \autoref{longtail series} we see the true embedding of the target node jump from one arm to the other at each timestep.
-It is clear that neither the the symbolic regression model nor the neural network model capture this movement, but the symbolic regression model does not move away from the data as quickly as the neural network model does.
-
-        In contrast to this, the symbolic regression model remains close to the true target node throughout the test data.
+It is clear that neither the the symbolic regression model nor the neural network model capture this movement.
+We also see that the symbolic regression model maintains a relatively stable position when compared to the neural network model.
 
@@
                 \begin{subfigure}[p]{0.3\textwidth}
-                    \includegraphics[width=\linewidth]{/home/stirling/thesis/Conference Submission/Plots/Test Only/3community/3community \i.png}
+                    \includegraphics[width=\linewidth]{./Plots/Test Only/3community/3community \i.png}
                     \caption{t=\i}
@@
             }
-            \caption{Long tail test series.
+            \caption{3 community test series.
 This series shows the comparison of the neural network model, the symbolic regression model trained on the neural network model, and the true solution of the 3 community system.}
@@
 
-        In the neural network only model, we see the prediction follow the true target node very closely at first.
+        % In the neural network only model, we see the prediction follow the true target node very closely at first.
 We then see the node drift further and further from the true target node.
@@
 
-        This was by far the largest improvement between the neural network and the symbolic regression.
+        In the neural network model, we see the prediction remain at close to its initial location for the duration of the test. This seems to indicate an attractor in the model.
+
+        In contrast, we see that the symbolic regression model quickly moves ahead of the true location where it remains for the duration of the test.
+
+        % This was by far the largest improvement between the neural network and the symbolic regression.
 This could be because this system had the least difference between the training predictions and the true position of the target node.
@@
 
+        \subsection{Network Prediction}
+        \begin{figure}
+            \begin{center}
+                \begin{tabular}{| m{0.25\textwidth} | m{0.25\textwidth} | m{0.25\textwidth} | m{0.25\textwidth} |}
+                 \hline
+                 Sequence & Embedding Mean Loss & Neural Network Prediction Mean Loss & Symbolic Regression Prediction Mean Loss\\ 
+                 \hline
+                 \hline
+                 2 Community & cell5 & cell6 & c\\ 
+                 \hline 
+                 Long tail & cell8 & cell9 & c \\ 
+                 \hline 
+                 3 Community & cell8 & cell9 & c \\ 
+                 \hline 
+                \end{tabular}
+                \end{center}
+                \caption{my caption}
+        \end{figure}
+        \subsection{Summary}
         We see a large difference in the training predictions between the 2 and 3 community systems.
@@
 The movement of the target node in the embedding was very similar between the two systems, and so the difference seems to be that the 2 community has symmetrical inputs.
+
+        These were trained on a relatively small neural network (one hidden layer of 64 nodes), when training this small network one of the issues we encountered was that the weights would become stuck in local minima.
+To manage this we found that simulate annaeling was helpful.
+When training on a larger network (4 hidden layers (64,8,8,8)) this does not seem to be as much of a problem.
     \end{subsection}
@@
 \begin{section}{Conclusion}
-    Not sure what to write for this\\
-    Using symbolic regression to approximate the neural network output seems to increase the stability of the extrapolation. This is most pronounced 
+    In this paper, we proposed a novel framework for modelling temporal networks.
+We then tested this framework on three types of small, synthetic network sequences.
+Throughout these tests the neural network performed XXXXXXX, with the XXXXXX sequence being especially notable due to XXXXX.
+These results were likely because XXXXX.
+In contrast, when we used symbolic regression to approximate the neural network model, we saw that XXXXX.
 \end{section}

### 2023-04-06 ThesisDoc/MainDoc.tex
Started on the lit review

\documentclass[12pt]{article}

\usepackage[
backend=biber,
style=nature,
sorting=ynt
]{biblatex}
\usepackage{svg}
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}

\addbibresource{bibliography.bib}

\begin{document}
\begin{titlepage}
   \vspace*{\stretch{1.0}}
   \begin{center}
      \Large\textbf{My Thesis}\\
      \large\textit{Connor Smith}
   \end{center}
   \vspace*{\stretch{2.0}}
\end{titlepage}
\section{Abstract}
About 200-300 words long\\

\section{Introduction}
%\cite{metaInfo}
A bit of background about the topic.
Some information about the current knowledge.
The aim of your research (the gap in knowledge that prompted you to write the thesis).
    \subsection{Terminology?}

\section{Literature Review}
    \subsection{Traditional Online Social Network Modelling}
        There has been a lot of research into what governs how edges are formed in an online social network. Some examples of what affects edge formation are a nodes' "age", how much time has passed since it first made an edge; it's edge creation rate is highest shortly after joining and decreases over time. The majority of edge creation in the early stages of a network is driven by new nodes arriving in the network, however this decreases significantly as the network matures. Edges formation follows preferential attachment, but this strength decreases over time as the network expands \cite{zhao2012multi}. Research also indicates that, while preferential attachment (a node is most likely to form an edge with the highest in-degree) can be used to model edge formation in online social networks, it alone does not seem to account for the low number of hops that empirical data suggests edges usually form along. \cite{garg2009evolution} suggest that preferential attachment with node distance as a tie breaker results in a distribution of node distances close to what was seen empirically from  their data.\\

        A potential for improvement in this research [\cite{garg2009evolution}, \cite{zhao2012multi}] is that they did not model the decay of edges (to the best of my knowledge) and they used a friendship/follow as their edge, which, while may be meaningful in the short term, I don't think is always meaningful after a given amount of time. [find source] A person may add a friend and never speak to them again (hence we use conversations together), this has limitations where a person can't always choose who they talk to, but it might provide a more granular (definition?) snapshot of interactions between users.\\
    \subsection{UDEs and NODEs}
      \subsubsection{Theory}
         UDEs are a combination of a known, structural component of a system, and a universal approximator, often a neural network.[Find reference]
         Given the flexibility of neural networks, the use of UDEs is natural when modelling a process that is not well understood [On Neural ODEs]
         \\
         Largely, the SciML ecosystem has been optimised for flexibility and efficiency with respect to models available 
         and training performance. Given there does not seem to be any other ecosystem with this feature, it seemed like 
         an obvious choice. ~~~What makes it good (Examples from \cite{SciML_C_Rak})  \\

        \subsubsection{Applications [Caution only glanced at these papers]}
        Whilst there has been much interest in implementing UDEs and neural ODEs, much of this work has been focussed on phisics informed neural network PINNs \cite{karniadakis2021physics}, \cite{GAO2021110079}, \cite{krishnapriyan2021characterizing}, \cite{roehrl2020modeling}, and on improving modelling of fluids \cite{mahmoudabadbozchelou2021data} \cite{nguyen2022physics}. There has also been a considerable amount of research into converting these discrete step neural networks into continuous depth neural networks, sometimes also referred to as neural ODEs \cite{massaroli2020dissecting} \cite{poli2019graph} \cite{NEURIPS2020_c9f2f917}. Along side this, and given UDEs have gained popularity in the last few years, there have been a number of studies exploring their usefulness in modeling the effect of restrictions due to COVID-19 on the virus' spread \cite{Dandekar2020.04.03.20052084}. Although there has been a large amount of research into the usefulness of these types of models, to the best of this author's knowledge they have never been applied to the problem of predicting temporal social networks. This seems to be a natural fit for UDEs and neural ODEs, given we know relatively little about the processes that govern the evolution of online social networks, and the vast amounts of data that the providers of these services collect, data that can be used to train our neural networks.\\

         Start by illustrating that there is a wide range of applications (Reasonably briefly for not relevant), but little research into UDEs aplicability for modeling how temporal networks behaveb
    \subsection{Dynamical Systems}

    \subsection{Symbolic Regression}
        Story is that there is a large search space of potential symbolic equations so most research has been looking to optimise this search.

        Applications are increadibly varied, as this process is useful for getting interpretable equations from data (with limitations from \cite{kidger2022neural}).

        \cite{kidger2022neural} also demonstrates how to use this with NODEs and their usefulness.

        Examples of implementations include discovering equations governing the movement of simple harmonic and chaotic double pendula from data \cite{schmidt2009distilling}(for the double pendulum searching took between 30-40 hours but when some knowledge of the system was added the time went to 7-8 hours), found underlying differential equations directly from time series data\cite{bongard2007automated}.

        As well neumerous algorithms exist, with one of the most prominent being genetic programming XXXX research XXXX

    \subsection{Temporal Networks}
        Wide range of applications (in conference submission)

        challenging problem to model ()

\section{Methods}

    \subsection{Embedding Our Network, Singular Value Decomposition}
    We used a singular value decomposition of each matrix to embed our network in a low dimensional space.\
    \[
    A = U\Sigma V'
    \]
    Where $\Sigma_{ii} = \sigma_i$ and $\sigma_i > sigma_{i+1}$ and each $\sigma_i$ is a non-negative square root of the matrices $AA', \space A'A$. $U$ is a matrix made from the orthonormalised eigenvectors of $AA'$ associated with $\sigma_i$, and $V$ is a matrix made from the orthonormalised eigenvectors of $A'A$ associated with $\sigma_i$. Each row $i$ of $U$ and $V$ represents the in and out position of node $i$ respectively. This can be truncated at an arbitrary number of eigenpairs to form a low dimentional approximation to $A$.
    \[
     A \approx \hat U \hat \Sigma \hat V'
    \]\\
    Where $\hat U, \hat \Sigma, \hat V$ are the first $d$ columns of $U, \Sigma, V$ \cite{golub1971singular}. $\hat U \sqrt{\hat \Sigma}$ is still associated with the in edges of our nodes, and $\sqrt{\hat \Sigma} \hat V' $ is still associated with the out edges of our nodes, but now we have simplified our system whilst keeping as much information as possible due to our descending order of singular values. These two matrices form our $d$ dimensional embedding.\\

    The approximation given by this formula can be interpreted as a graph where the entry $(i,j)$ of the matrix are the probability that an edge exists from $i \rightarrow j$.This approach creates a random dot product graph, a class of Latent Position Models \cite{hoff2002latent}. Finding the embedding is not trivial; we need to find the eigenpairs of each of $AA'$ and $A'A$. Because of the computational complexity we use the SVD function in Arpack.jl to approximate each matrix. This then changes the problem of discovering edge formation and destruction into learning a dynamical system.\\
    It is important to note that the SVD is not unique. The distances between points will be the same for every embedding, but the orientation may be different, and so, if the SVD of each time step is not alligned, learning will be effectively impossible [<- show this]. Since our approximation method is an iterative approach, to align each SVD, we can simply pick the same initial vector guess for each [probably worth getting a reference].

    Once we have this embedding of points, we look to model the trajectories of each point. That is, with some input data, point location, distance to neighbours, etc, we want to model the ODE of each point. To do this we make use of the SciML ecosystem of packages in the Julia programming language \cite{SciML_C_Rak}. To explore which architectures perform best for this system we then test various types. ~~~~~~~~~~~~~~~~~~~~~~~~

    With our trained NODE, we have a black box that approximates the system that governs the movement of Twitter users. To make this more interpretable we then look to decompose this into linear combinations of known functions using SINDY. For this process we need to define a search space of functions which the algorithm will use to find the best approximation to our NODE with.

    % We then decide on the number of singular values to take (number of dimensions of our embedding), observing \cite{Runghen2021}, we use [method here including plots]  
    % - Take a time interval of our data and form an undirected network of interactions.
    % - This is not useful for modelling
    % - We embed the network into a low dimensional space where each node becomes a point and nodes that are strongly related become points that are close together. 
    % - This is done using a singular value decomposition (SVD).
    % - 
    % Similar method as Rogini but user Julia's Arpack SVD, not R's \cite{Runghen2021}
    % -->> Estimate adequate dimension using some criteria. \cite{Runghen2021} has references to the criteria they use.

    Initially, we decided the best course of action would be to implement a toy example graph as a proof of concept.
    This would allow us to check that it is indeed possible to use neural networks to model the progession of temporal networks.
    It would also allow us to compare and contrast the use of a "known" function in our model, which will be combined with the 
    neural network to model the evolution of the system over time.

    [On Neural Ordinary Differential Equations ch. 2] Potential for starting with a portion of data to minimise getting stuck in 
    local minima.
    \subsection{Testing Different Things}
        Before we begin training our model on the whole data set, we first perform a series of comparisons of different model setups on a subset of our data (1 node 0 knn, 15 nodes 5 knn, 50 nodes 20 knn). Each of these comparisons will be run for ?20? epochs and a ttraining data size of 25 weeks. We will compare both the accuracy and the training time, to develope a model that is likely to perform well on the whole data set. The base model we will be comparing against will have no proposed known component, will have 1 NN with ?2? hidden layers of width 16 each, with an activation function of ?tanh?. The results of this model are
        \begin{table}[]
            \centering
            \begin{tabular}{c|c|c}
                 & training loss & computation time \\
                 \hline
                 super small &  \\
                 small & \\
                 medium &
            \end{tabular}
            \caption{Caption}
            \label{tab:my_label}
        \end{table}

    \subsection{Proposed Known Components}
        \subsubsection{Everything Towards Zero} 
        \subsubsection{Including Time Component}
    \subsection{Comparison of Methods on Deterministic Toy Graphs}
        \subsubsection{Toy Graph}
            Toy Graph 1\\

            Toy Graph 2\\
                Our second toy network was created from a known vector field defined by
                \begin{align}
                    \frac{dx}{dt} &= (x^2+y^2-\frac14)y\\
                    \frac{dy}{dt} &= -(x^2+y^2-\frac14)x
                \end{align}
                With 4 initial points $(x,y)=(0.5,0.5), (0.125, -0.125), (-0.5, 0.0), (-0.5, -0.5)$. One minus the euclidean distance between point $i$ and $j$ is the entry $(i,j)$ in our associated adjacency matrix and corresponds to the probability of an edge existing between these two nodes. Having a network defined by such a system allows us to easily see whether our network (when run through SINDY) is recovering the correct dynamics of the movement of edges between nodes.

            Explain how the graph is defined and moves over time
        \subsubsection{Tweaks to Method}
            \subsubsection{Aligned vs Unaligned Embeddings}
                %\includesvg[scale=0.5]{plot_aligned_vs_unaligned(draft)}
                How does model accuracy, training time , etc change when the embedding is aligned compared to unaligned? Does alignment method matter?
            \subsubsection{Training on Embedded Data vsThe True Graph}
                Does training the model using the embedded data to calculate loss change the test loss of the model compared to us using the true network matrix?
            \subsubsection{One Neural Network Compared to One For In Edges and One For Out Edges}
            %\includesvg[scale=0.4]{Draft1NNvs2NN}
                Does test error change if we have one NN for the whole graph compared to one for the L and one for the R embeddings? Does it have much impact on computing time? Keep total number of parameters the same (maybe ask Giulio)?
            \subsubsection{Random Noise}
                If we introduce a stochastic component, how does the model cope?
            \subsubsection{Different Dimension Embeddings}
                As we vary the number of dimensions we embed, how does accuracy and computation time change?
            \subsubsection{Training Loss Against Embedding Loss}
                Does the information captured in the SVD embedding correlate with the accuracy of the NN?
            \subsubsection{SINDY}
                If we include a SINDY step, does this improve the accuracy of our model at times far from the training data?
            \subsubsection{trying to predict self loops vs not}
                If we ignore the models prediction of self loops, does this improve the accuracy for the rest of the model?
            \subsection{Including "Known" Differential Equation Component}
                How does the inclusion of the known component effect the accuracy and training time of the model.
                From \cite{garg2009evolution}
                Factors that have an impact on edge generation:

    \subsection{Including Other Information}
        Within the literature, there is evidence of the rate at which a new node creates edges depending on when it was first created, hence it may be worth including this, and other information, (for example the communities a user is in) as an input for the NN.
    \subsection{Variation in the known component}
        \cite{SciML_C_Rak} Demonstrates that if we have a differential equation of the form

        \begin{align}
            \dot x &= f_1(x,y)+g_1(x,y) \\
            \dot y &= f_2(x,y)+g_2(x,y)
        \end{align}

        ${g_1, \space g_2}$ can be replaced with neural networks $U_1(\theta, x, y), \space U_2(\theta, x, y)$. These neural networks can be trained, and using some type of sparse identification (SINDY), the original $g_1, \space g_2$ can be recovered. This example was given using the Lotka\-Volterra equations in which we knew that $f_1, f_2$ were exactly correct. Given we know very little about the systems of differential equations that govern social networks, we wish to briefly explore what is recovered when the known functions $f_1, \space f_2$ are perturbed to $\hat f_1, \space \hat f_2$. 
\section{Thesis Results}
\subsection{Exploratory Analysis}
- A brief overview of the data following the methodology of \cite{zhao2012multi} and \cite{garg2009evolution}. (Might need to find source code?)
\section{Discussion}

\section{Conclusion}

\printbibliography
\end{document}

### 2023-05-15 Code/PlottingCode/plotSltn.jl
sanoetuh

@@ -3,7 +3,7 @@ using ColorSchemes
 include("../_Modular Functions/loadGlobalConstants.jl")
 
 include("../_Modular Functions/pca.jl")
-global_consts("longTail", (182,2))
+global_consts("3community", (212,2))
 
 include("symreg.jl")
 
@@ -27,6 +27,7 @@ using DelimitedFiles
 
 
 sltn = readdlm("./Code/Solutions/$net_name big net test only.csv", ',')
+mid = convert(Int, dims[1]/2)
 
 for i in 1:length(t_data)-datasize
     pts = t_data[i+datasize]'#get_embedding([sltn_sym_reg[:,i]'; t_data[i+datasize]], sltn[:,i])
@@ -53,22 +54,22 @@ function net_pred_loss(pt, tstep)
     R = t_data[tstep][:,mid+2:end]
 
     
-    pred = round.(pt'*R)
+    pred = pt'*R
     # 
-    return sum(abs, pred.-true_struct'),pred
+    return sum(abs, pred.-true_struct'),pred,true_struct
 end
 
-tstep = datasize+15
+tstep = datasize+5
 sltn_sym = sltn_sym_reg[:,tstep-datasize]
 sltn_nn = sltn[:,tstep-datasize]
 sltn_true = t_data[datasize+1][:,1]
 
-tests = [sltn_sym, sltn_nn, sltn_true]
+tests = [sltn_true, sltn_nn, sltn_sym]
 p  = net_pred_loss.(tests,tstep)
 
 L = t_data[tstep][:,1:mid]
 R = t_data[tstep][:,mid+1:end]
 
 L'*R
-
-printall(p[1][2])
+(p[1][1], p[2][1], p[3][1])
+printall(p[1][3])

### 2023-05-15 Code/PlottingCode/symreg.jl

@@ -9,12 +9,12 @@ grad_sltn = sltn[:,2:end].-sltn[:,1:end-1]
 
 test_range = eachindex(1.0:0.01:Float64(datasize))
 
-# trace = scatter(x=sltn[1,:],y=sltn[2,:], mode="markers", name="sltn from start")
-# trace2 =  scatter(x=[t_data[i][1,1] for i in 1:datasize],y=[t_data[i][2,1] for i in 1:datasize], mode="markers", name="train")
-# trace3 =  scatter(x=[t_data[i+datasize][1,1] for i in 1:length(t_data)-datasize],y=[t_data[i+datasize][2,1] for i in 1:length(t_data)-datasize], mode="markers", name="test")
-# trace4 =  scatter(x=sltnt[1,1:end],y=sltnt[2,1:end], mode="markers", name="sltn from test")
+trace = scatter(x=sltn[1,:],y=sltn[2,:], mode="markers", name="sltn from start")
+trace2 =  scatter(x=[t_data[i][1,1] for i in 1:datasize],y=[t_data[i][2,1] for i in 1:datasize], mode="markers", name="train")
+trace3 =  scatter(x=[t_data[i+datasize][1,1] for i in 1:length(t_data)-datasize],y=[t_data[i+datasize][2,1] for i in 1:length(t_data)-datasize], mode="markers", name="test")
+trace4 =  scatter(x=sltnt[1,1:end],y=sltnt[2,1:end], mode="markers", name="sltn from test")
 
-# plot([trace, trace2, trace3, trace4])
+plot([trace, trace2, trace3, trace4])
 
 train_data = withoutNode(t_data,1)
 length(train_data)
@@ -51,9 +51,9 @@ dominatings = [
     calculate_pareto_frontier(Float64.(data), grad_sltn[i,:], halls[i], options)
     for i in 1:dims[2]
 ]
-
+dominatings[1]
 eqns = [
-    dominatings[i][1].tree
+    dominatings[i][end].tree
     for i in 1:dims[2]
 ]
 

### 2023-05-15 Conference Submission/DraftDoc.tex
aoeuaoeu

@@
 backend=biber,
-style=nature,
+style=numeric,
+maxbibnames=99,
 sorting=ynt
@@
 
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{remark*}[theorem]{Remark}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{sublemma}{}[theorem]
-\newtheorem{conjecture}[theorem]{Conjecture}
-
 % Override ugly default link
@@
 \begin{section}{Introduction}
-The modelling of temporal networks is an important task in many real world applications including symptom interactions for mental health, epidemiology, and protein interactions \cite{jordan2020current,contreras2020temporal,lucas2021inferring,jin2009identifying,masuda2013predicting}.
-Temporal networks can be seen as dynamical systems: that is, a system in which we have points, in our case nodes in a network, whose states, the edges connecting them, vary dependent in time.
-Discovering the underlying equations governing these dynamical systems proves challenging, because changes in network structure are typically observed in the form of discrete jumps from one state to another, that is, an edge may exist between two nodes at one timestep then dissapear at the next.
-There cannot be an edge that has half decayed.
-Here, we proposes a hybrid statistical and deep learning framework that allows us to model temporal networks as continous-time dynamical systems, discover a fitting set of differential equations describing it, and, exploiting that discovery, predict the time evolution of a network.
+    The modelling of temporal networks is an important task in many real world applications including symptom interactions for mental health \cite{jordan2020current,contreras2020temporal}, epidemiology \cite{masuda2013predicting}, and protein interactions \cite{lucas2021inferring,jin2009identifying}.
+    Temporal networks can be seen as dynamical systems: that is a system in which we have points, in our case nodes in a network, whose states, the edges connecting them, that vary dependent in time.
+    Discovering the underlying equations governing these dynamical systems proves challenging, because changes in network structure are typically observed in the form of discrete jumps from one state to another, for example an edge between two nodes not being observed at the first time step then appearing at the next.
+    Here, we propose a hybrid statistical and deep learning framework that allows us to model temporal networks as continuous-time dynamical systems, discover a fitting set of differential equations describing it, and, exploiting that discovery, predict the time evolution of a network.
 
     Differential equations are useful for modelling systems where the state of one variable can effect the trajectories of other variables.
-We observe this behaviour in temporal networks; nodes' connections within the network can influence the formation and decay of edges between other nodes, for example the phenonmenon of preferential attatchment observed in \cite{newman2001clustering,capocci2006preferential}.
-With this observation in mind we might wish to draw on the rich mathematical literature of differential equation modelling.
+We observe this behavior in temporal networks; nodes' connections within the network can influence the formation and decay of edges between other nodes, for example the phenomenon of preferential attachment observed in \cite{newman2001clustering,capocci2006preferential}, where a node is more lively to gain the connections the more connections it has.
+With this in mind we might wish to draw on the rich mathematical literature of differential equation modelling.
 
-In the common representation of networks as binary-valued adjacency matrices, the events recorded in a temporal sequence of networks correspond to topological events, such as the appearence or the disappearance of link.
-Because of the discrete nature of events, directly modelling the temporal networks as dynamical systems would require the model to handle discrete jumps.
+    In the common representation of networks as binary-valued adjacency matrices, the events recorded in a temporal sequence of networks correspond to topological events, such as the appearance or the disappearance of link.
+    Because of the discrete nature of events, directly modelling the temporal networks as dynamical systems would require us to handle discrete jumps.
     The topological nature of temporal networks, and the discontinuous character of their temporal evolution, make it challenging to use differential equations techniques.
 
-Here, we overcome the discretness problem by interpreting networks as Random Dot Product Graphs, a well established statistical model for complex networks, that embeds nodes in a low-dimensional metric space\cite{athreya2017statistical}.
-In this way we translate the hard problem of modelling discrete events in the space of networks to the easier problem of modelling continous change in the embedding space.
-Then, we define and use systems of Neural Network Differential Equations (NNDE) to approximate the time evolution of the embedding space, and symbolic regression techniques to discover the functional form of the fitted NNDEs.
-These functional forms are interpretable (as they read as classic differential equations) and allow to predict forward in time the evolution of the temporal networks.
+    Here, we overcome the discreteness problem by interpreting networks as Random Dot Product Graphs; a well established statistical model for complex networks, that embeds nodes in a continuous, low-dimensional metric space by using a truncated singular value decomposition\cite{athreya2017statistical}.
+In this way we translate the hard problem of modelling discrete events in the space of networks to the easier problem of modelling continuous change in the embedding space.
+We then define and use systems of Neural Network Differential Equations (NNDE)\cite{SciML_C_Rak} to approximate the time evolution of the embedding space, and symbolic regression techniques to discover the functional form of the fitted NNDEs.
+These functional forms are interpretable (as they read as classic differential equations) and allow us to predict forward in time the evolution of the temporal networks.
 
-In this manuscript, we prove that the temporal network prediction problem can be successfully re-interpreted as a dynamical system modelling problem.
-In particular, we apply our proposed framework to three small example temporal networks with the hope of exploring the limitations and strengths of the proposed framework.
+    In this manuscript, we prove that the temporal network prediction problem can be successfully re-interpreted as a dynamical system modelling problem by taking the singular value decomposition of a sequence of adjacency matrices and training a NNDE to model an approximation to the underlying differential equation.
+We then go on to create a symbolic equation of this approximation.
+
+    We apply our proposed framework to three small example temporal networks with the hope of exploring the limitations and strengths of the proposed framework. 
     The framework we are introducing is extremely flexible, and our research regarding the optimal structure of the Neural Networks used for the NNDEs is just started.
@@
     For this reason, we did not yet attempt to benchmark our model against other classic temporal network prediction methods.
-As it is completely general, we believe that the framework we are introducing can be usefully applied to areas of medicine, especially protein interaction networks; population dynamics for network ecology; and social network modelling[citation].
+    As it is completely general, we believe that the framework we are introducing can be usefully applied to areas of medicine, especially protein interaction networks; population dynamics for network ecology; and social network modelling.
 In particular, we discuss how specific domain knowledge relative to the prediction scenario can be taken into account, moving from NNDEs to Universal Differential Equations.
-
 \end{section}
@@
 \begin{section}{Methodology}
+
         We are given a sequence of graphs, and our goal is to predict the next graph in the sequence.
-To do this we read each graph as a Random Dot Product Graph (RDPG); a visual representation of this process can be seen in \autoref{framework illustration}.
-To obtain the RDPG, we take each network observation \autoref{method nets} and represent them in the form of an adjacency matrix \autoref{method adjacency}.
-We then use a truncated singular value decomposition to reduce the dimensionality of our adjacency matrices[ref].
-This truncation introduces some loss, but can dramatically reduce the size of our problem [cite].
-XXXX It should be noted that when we plot our models, we compare them to this embedding and do not take into account this truncation loss.XXXX The rows of the output of the SVD can then be viewed as vector points in a d-dimensional space[ref], where d is the number of singular values we take for our SVD.
-In this space nodes that are similar, ie, nodes have many common neighbours, will be mapped to similar points in the space.
+To achieve this, we reinterpret each graph as a sequence of points in a latent space; that is, a space in which similar vertices (ones with many of the same neighbours) are mapped to a similar point in space.
+We then Train a Neural Network Differential Equation (NNDE) to approximate the rate of change of the points in this latent space.
+With this numerical equation we can then use symbolic regression techniques to find a functional equation that matches the numerical equation.
+Using this process we discover an interpretable function that governs the evolution of a differential equation.
+
         \begin{figure}
@@
                 \end{tabular}
-        \caption{Sequence of sparce adjacency matrices associated with the networks in \autoref{method nets}.}
+                \caption{Sequence of sparse adjacency matrices associated with the networks in \autoref{method nets}.}
                 \label{method adjacency}
@@
 
-    We used a Singular Value Decomposition of each adjacency matrix to embed our network in a low dimensional space.
-To execute the SVD\cite{golub1971singular} we use the Julia package [cite].
-This package uses implicitly restarted Lanczos iterations\cite{lehoucq1996deflation} to approximate the eigen vectors and singular values of each of our adjacency matrices.
-From the "svds" function, we obtain two matrices, $L$ and $R$ where:\\
+        \subsection{Singular Value Decomposition and Random Dot Product Graphs}
+            \label{svd}
+            In this section we discuss the Singular Value Decomposition (SVD) of a matrix, and its usefulness in creating Random Dot Product Graphs (RDPG).
+
+            We define the matrix $A$ to be a real $m \times n$ with $n \le m$. $A$ can be expressed as \cite{forsythe1967computer}:
             \begin{align}
-        L&=\hat L \sqrt{\hat \Sigma }\\
-        R &= \hat R \sqrt{\hat \Sigma }\\
-        A &\approx \hat L \hat \Sigma \hat R'\\
-        &\approx LR'
+                A&=L\Sigma R'
             \end{align}
-    $L,\hat L, R, \hat R$ are each real valued $n\times d$ matrices, where the columns of $\hat L$ and $\hat R$ are the first $d$ eigenvectors of $AA'$ and $A'A$ respectively ordered by the size of their associated singular values.
-$\hat \Sigma$ is a $d\times d$ diagonal matrix whose entries are the singular values associated with each eigenvector.
-\\
+            Where $L, R$ are real valued, orthonormal matrices.
+The columns of $L$ consist of the $n$ largest eigenvectors of $AA'$ and the columns $R$ consist of the eigenvectors of $A'A$.
+$\Sigma$ is a diagonal matrix whose entries are the square root of the positive eigenvalues of $A'A$ in decreasing order.
+
+            In order to reduce the problem size, we can truncate the $L,R,\Sigma$ to the first $d$ columns to yield, $\hat L, \hat R, \hat \Sigma$ such that:
+
+            \begin{align}
+                A &\approx \hat L \hat \Sigma \hat R' \\
+                \hat A &= \hat L \hat \Sigma \hat R'
+                \label{approx}
+            \end{align}
+
+            The approximation of $A$ is defined as $\hat A$ and is given by \autoref{approx} can be interpreted as a graph where the entry $(i,j)$ of the matrix is the probability that an edge exists from $i \rightarrow j$.
+This approximation of $A$ is known as an RDPG.
+
             It is important to note that the SVD is not unique.
-The distances between points will be the same for every embedding, but the orientation may be different, and so, if the SVD of each time step is not alligned, learning will be effectively impossible [<- show this].
-Since our approximation method is an iterative approach, to align each SVD, we can simply pick the same initial vector guess for each [probably worth getting a reference]; this will cause the outputs of the Arpack function to each be aligned with eachother XXX with some requirements of the matrix/initial vec?XXX.
-Altenatively we can use Procrustes alignmet[cite package] to align the matrices after they have been generated.\\
-    The approximation  given by this formula can be interpreted as a graph where the entry $(i,j)$ of the matrix is the probability that an edge exists from $i \rightarrow j$.This approach creates a Random Dot Product Graph\cite{athreya2017statistical}, a class of Latent Position Models \cite{hoff2002latent}.
-Once we have this embedding of points, we look to model the trajectories of each point.
-That is, with some input data, point location, distance to neighbours, etc, we want to model the ODE of each point.
-To do this we make use of the SciML ecosystem of packages in the Julia programming language \cite{SciML_C_Rak}.\\
+The distances between points will be the same for every embedding, but the orientation may be different, and so, if the SVD of each time step is not aligned, learning will be effectively impossible as we will essentially be trying to model random noise.
+Here, we can use Procrustes alignment XXX cite package XXX to align the matrices after they have been generated.
 
-    % IN THE THESIS MAYBE
-    % This can be truncated at an arbitrary number of eigenpairs to form a low dimentional approximation to $A$.
-    %     \[
-    %     A \approx \hat U \hat \Sigma \hat V'
-    %     \]\\
-    % Where $\hat U, \hat \Sigma, \hat V$ are the first $d$ columns of $U, \Sigma, V$ \cite{golub1971singular}.
-$\hat U \sqrt{\hat \Sigma}$ is still associated with the in edges of our nodes, and $\sqrt{\hat \Sigma} \hat V' $ is still associated with the out edges of our nodes, but now we have simplified our system whilst keeping as much information as possible due to our descending order of singular values.
-These two matrices form our $d$ dimensional embedding.\\
+            The SVD gives is an RDPG\cite{athreya2017statistical}.
+The SVD can be considered to give a latent space representation of the matrix\cite{hoff2002latent}.
+That is, the rows of the matrices $L,R$ can be viewed as vector points in a $d$-dimensional space, where $d$ is the number of singular values we take for our SVD truncation.
+In this space similar nodes in the network are mapped to similar points.
+A visual representation of this process can be seen in \autoref{framework illustration}.
+
+            When obtaining the RDPGs for our temporal network, we take each network observation \autoref{method nets} and represent them in the form of an adjacency matrix \autoref{method adjacency}.
+We then use a truncated singular value decomposition to reduce the dimensionality of our adjacency matrices\cite{golub1971singular}.
+This truncation introduces some loss, but can dramatically reduce the size of our problem.
+\Citeauthor{Runghen2021}\cite{Runghen2021} effectively employ this method to reduce a problem involving over 130,000 visitors to a 6 dimensional latent space, whilst preserving 70\% of the information.
+
+            To execute the SVD we use the ARPACK Julia package \cite{lehoucq1998arpack}.
+This package uses an iterative approach to approximate the eigenvectors and singular values of each of our adjacency matrices\cite{lehoucq1996deflation}.
+
+    \subsection{Neural Network Differential Equation}
+        Once we have the SVD embedding of points, we look to model the trajectories of a target point.
+That is, with some input data, point location, distance to neighbours, etc, we want to model the differential equation that governs the movement of a point.
+Notably this method can be used to model multiple points by simply changing the node being predicted and trained on.
+
+        Our problem can be defined as:
+        \begin{align}
+            A_{t+1} = f(A(t),t)
+        \end{align}
+        Where $A_t$ is the adjacency matrix of the temporal network at time $t$.
+By using the SVD to obtain the approximation $\hat A_t$, which can evolve continuously, we can reinterpret our problem as:
+
+        \begin{align}
+            \frac{d\hat A}{dt} &= g(\hat A(t), t)
+        \end{align}
+
+        In this thesis, as a proof of concept, we focus on a modelling the change in structure of a single node, referred to as the target node $u$. In this case, the form of the problem becomes:
+
+        \begin{align}
+            \frac{du}{dt} &= g(u(t), t)
+        \end{align}
+
+        Because we are only modelling the movement of a single node, we assume that we have access to the rest of the network structure at every time step for the prediction.
+This would likely not be the case in a real world application, but will allow us to observe some of the strengths and weaknesses of this framework in a controlled setting.
+If we wanted to predict the whole network we would extrapolate out every point and use the dot product of each point to predict the edges.
+
+        Here we train a neural network to approximate the function $g(u(t),t)=NN(u(t),t,\theta)$. Where $\theta$ is the parameters of the neural network.
+
+        To obtain this differential equation we make use of the SciML ecosystem of packages in the Julia programming language \cite{SciML_C_Rak}.
 
@@
 The target node is the node that we are looking to model the movement of and stays the same throughout each of the temporal networks.
-    \begin{align}
-        %\centering
-        \mathbb{P}(i\rightarrow j)&\coloneqq L_i \cdot R_j\\
-        \mathbb{P}(\hat{i}\rightarrow j)&\coloneqq L_{\hat{i}} \cdot R_j
-    \end{align}
-    Where $(i,j)$ are nodes in the network and $\hat{i}$ is another node at the same timestep to $i$. This implies that the distance between these two nodes with respect to node $j$ is given by
-    \begin{equation}
-        \begin{gathered}
-            %\centering
-            ||\mathbb{P}(i\rightarrow j)-\mathbb{P}(\hat{i}\rightarrow j)||_2 = 
-            ||L_i \cdot R_j-L_{\hat{i}} \cdot R_j||_2\\
-            =||(L_i -L_{\hat{i}}) \cdot R_j||_2
-        \end{gathered}
-    \end{equation}
-    If we look at the expectation of this, we see
-    \begin{equation}
-        \begin{gathered}
-            %\centering
-            \mathbb{E}_j(||(L_i -L_{\hat{i}}) \cdot R_j||_2) = ||L_i -L_{\hat{i}} \cdot \frac{1}{k}\sum_{j\ne i}R_j||_2
-        \end{gathered}
-    \end{equation}
-    Where $k$ is the number of neighbours we chose for the neural network input. Because the distance between points is discribed by the euclidean distance, we use this as our loss metric.
+        % \begin{align}
+    %     %\centering
+    %     \mathbb{P}(i\rightarrow j)&\coloneqq L_i \cdot R_j\\
+    %     \mathbb{P}(\hat{i}\rightarrow j)&\coloneqq L_{\hat{i}} \cdot R_j
+    % \end{align}
+    % Where $(i,j)$ are nodes in the network and $\hat{i}$ is another node at the same timestep to $i$. This implies that the distance between these two nodes with respect to node $j$ is given by
+    % \begin{equation}
+    %     \begin{gathered}
+    %         %\centering
+    %         ||\mathbb{P}(i\rightarrow j)-\mathbb{P}(\hat{i}\rightarrow j)||_2 = 
+    %         ||L_i \cdot R_j-L_{\hat{i}} \cdot R_j||_2\\
+    %         =||(L_i -L_{\hat{i}}) \cdot R_j||_2
+    %     \end{gathered}
+    % \end{equation}
+    % If we look at the expectation of this, we see
+    % \begin{equation}
+    %     \begin{gathered}
+    %         %\centering
+    %         \mathbb{E}_j(||(L_i -L_{\hat{i}}) \cdot R_j||_2) = ||(L_i -L_{\hat{i}}) \cdot \frac{1}{k}\sum_{j\ne i}R_j||_2
+    %     \end{gathered}
+    % \end{equation}
+    % Where $k$ is the number of neighbours we chose for the neural network input. Because the distance between points is described by the euclidean distance, we use this as our loss metric.
 
     % Symbolic Regression Explaination
+    \subsection{Symbolic Regression}
         With our trained NODE, we have a black box that approximates the system that governs the movement of the target node in the embedded space.
-To make this more interpretable we then look to approximate this black box into a combination of known functions using symbolic regression[citation (use the one from symreg package)].
-For this process we need to define a set of functions which the algorithm will use to generate a tree of functions to find the best approximation to our NODE with.
-When using this method we usually are required to make two assumptions: that we have paired observations of $y(t), \frac{dy}{dt}$, and that the tree of expressions we will need is shallow.
+To make this more interpretable we then look to approximate this black box into a combination of known functions using symbolic regression\cite{pysr}.
+
+        Symbolic regression is a type of regression analysis that searches a space of equations to find an expression that matches data.
+We use the genetic programming algorithm found in \cite{pysr}.
+The process for which can be seen in \autoref{symbreg}.
+
+        \begin{figure}
+            \centering
+            \resizebox{\width}{!}{\input{SynthDataDiagrams/symbreg.tex}}
+            \caption{Illustration of the genetic programming symbolic regression process.}
+            \label{symbreg}
+        \end{figure}
+
+        The fitness of a candidate function is determined by comparing the predicted value to the given data, as well as the derivatives of the candidate equations to numerically found partial derivatives of the data variable.
+
+        For this process we need to define a set of functions which the algorithm will use to generate a tree of functions to find the best approximation to our NNDE with.
+When using this method we are usually required to make two assumptions: that we have paired observations of $y(t), \frac{dy}{dt}$, and that the tree of expressions we will need is shallow.
 We will train the symbolic regression on the predictions of the neural network.
 By doing this, we can remove these assumptions\cite{kidger2022neural}.
+
+    \subsection{Reconstructing the Temporal Network}
+        To recover a final prediction, the point vector of the target node with the matrix $R'$, this gives a vector of probabilities of connections between the target node and the rest of the network.
+As the results can be interpreted as a probability, the most likely graph is given by setting any entry with a value of $0.5$ or higher to one (predict that the edge exists), and setting any entry with a value of less than $0.5$ to zero (predict that an edge does not exist).
 \end{section}
@@
 \begin{section}{Data}
-
     In this paper we simulate three temporal sequences of undirected graphs.
 For each sequence we will be modelling the node in red, we will refer to this as the target node.
-For each sequence we train the model on the first 20 timesteps and compare the predictions for the next 15 timesteps.
-For clarity, each diagram \autoref{2community train series} \autoref{longTail train series} \autoref{3community train series} has been simplified and illustrates the movement of the target node in each sequence.\\
+For each sequence we train the model on the first 25 time steps and compare the predictions for the next 15 time steps.
+For clarity, each diagram \autoref{2community train series} \autoref{longTail train series} \autoref{3community train series} has been simplified and illustrates the movement of the target node in each sequence.
 
+    \subsection{Two Community System}
         The 2 community network has communities of size 40 and 50, each of which are fully connected.
 The target node is initially fully connected to the 50 node community.
-In our simplified diagram \autoref{2community train series, a} that is represented by the five node community.
+In our simplified diagram \autoref{2community train series, a} the 50 node community is represented by the 5 fully connected nodes, while the 40 node community is represented by the 4 node component.
 At each time step one edge is removed between the target node and the larger community and replaced with an edge between the target node and the smaller community \autoref{2community train series, b}.
-This process is then continued \autoref{2community train series, c} for thirty five timesteps to generate our training and test data.
+This process is then continued \autoref{2community train series, c} for thirty-five time steps to generate our training and test data.
+Once we have this data in the form of a sequence of adjacency matrices, we find the singular value decomposition using the framework described in \autoref{svd}.
 
@@
                 \resizebox{.6\width}{!}{\input{SynthDataDiagrams/2community1.tex}}
-            \caption{Simplification of the 2 Community network at $t=1$.}
+                \caption{$t=1$}
                 \label{2community train series, a}
@@
                 \resizebox{.6\width}{!}{\input{SynthDataDiagrams/2community2.tex}}
-            \caption{Simplification of the 2 Community network at $t=2$.}
+                \caption{$t=2$}
                 \label{2community train series, b}
@@
                 \resizebox{.6\width}{!}{\input{SynthDataDiagrams/2community3.tex}}
-            \caption{Simplification of the 2 Community network at $t=3$.}
+                \caption{$t=3$}
                 \label{2community train series, c}
             \end{subfigure}
-        \caption{First 3 time steps of synthetic 2 community network.}
+            \caption{First 3 time steps of the simplified, synthetic 2 community network.
+The red node represents the target node that we are aiming to model.
+The 4 node and 5 node fully connected components represent the 40 and 50 node communities of the sequence respectively.
+At each time step, an edge from the target node to the larger community is replaced with and edge from the target node to the smaller community.}
             \label{2community train series}
         \end{figure}
+        The 2 community temporal network was selected to test whether this framework can be used to model a node changing communities in systems where there are no other processes occurring.
+Notably, the movement in the two community system is difficult for the neural network to learn because opposite sets of inputs need to result in the same output.
+In a simplified version of this system with only the nearest node as input, the input for the model begins as the position of the larger community at roughly $(0,-1)$ \autoref{2community series 1}.
+This input needs to move the target towards the top left.
+However, as the sequence progresses, the nearest neighbours will be the small community at roughly $(-1,0)$, which also needs to move the target node towards the top left.
 
-    In the long tail network \autoref{longTail train series}, we have a long chain with fifty nodes and a fully connected component with forty nodes at one end of the chain.
+    \subsection{Long Tail System}
+        In the long tail network \autoref{longTail train series}, we have a long chain with 50 nodes and a fully connected component with forty nodes at one end of the chain.
 This is used to orient the embedding and model.
-The target node starts attatched to the node that is attatched to this large componet \autoref{longTail train series, a}.
+The SVD does not take into account the index of the individual node in the adjacency matrix; it only distinguishes based on their distance to each other.
+Because of this a chain of nodes, even when aligned, could be flipped when it is embedded.
+That is, between one time step and the next the first node in the chain could be aligned with the last node.
+With a large, connected group at one end however, that group will always be aligned with itself and so the rest of the chain will also be aligned properly.
+The target node starts attached to the node that is attached to this large component \autoref{longTail train series, a}.
 At each time step the target node move one node further down the tail \autoref{longTail train series, b}.
@@
                 \resizebox{.6\width}{!}{\input{SynthDataDiagrams/longTail1.tex}}
-            \caption{Simplification of the long tail network at $t=1$.}
+                \caption{$t=1$}
                 \label{longTail train series, a}
@@
                 \resizebox{.6\width}{!}{\input{SynthDataDiagrams/longTail2.tex}}
-            \caption{Simplification of the long tail network at $t=2$.}
+                \caption{$t=2$}
                 \label{longTail train series, b}
@@
                 \resizebox{.6\width}{!}{\input{SynthDataDiagrams/longTail3.tex}}
-            \caption{Simplification of the long tail network at $t=3$.}
+                \caption{$t=3$}
                 \label{longTail train series, c}
             \end{subfigure}\\
-        \caption{First 3 time steps of synthetic long tail network.}
+            \caption{First 3 time steps of the simplified, synthetic long tail network.
+The red node represents the target node that we are aiming to model.
+The fully connected, 5 node component represents a 50 node community at the end of the long tail.
+At each time step the target node moves one step further along the chain, away from the large community.}
             \label{longTail train series}
@@
 
+        The long tail network was selected because the SVD performs poorly on highly diagonal matrices; that is matrices with long chains.
+The long tail problem is difficult for the embedding because a large portion of the network is along the off diagonals; meaning that, to get an accurate embedding, the dimension of the embedding would need to be close to the length of the tail.
+As such we wish to see how the framework performs when it is presented with a system that the SVD cannot capture.
+
+    \subsection{Three community System}
     We also simulate a sequence with three communities.
 The communities have sizes 40, 35, 30 and have 25, 24, and 23 edges to the target node respectively.
-In \autoref{3community train series} the communities have been simplified to have sizes of five, four, and 3.
+In \autoref{3community train series} the communities have been simplified to have sizes of 5, 4, and 3.
 The target node starts connected to all of these communities with each community having a different number of edges \autoref{3community train series, a}.
-The community with the fewest edges between the target node will have one edge removed at each timestep \autoref{3community train series, b}, and this process is repeated to create the required number of timesteps \autoref{3community train series, c}.
+The community with the fewest edges between the target node will have one edge removed at each time step \autoref{3community train series, b}, and this process is repeated to create the required number of time steps \autoref{3community train series, c}.
     \begin{figure}[H]
@@
             \resizebox{.6\width}{!}{\input{SynthDataDiagrams/3community1.tex}}
-            \caption{Simplification of the 3 Community network at $t=1$.}
+            \caption{$t=1$}
             \label{3community train series, a}
@@
             \resizebox{.6\width}{!}{\input{SynthDataDiagrams/3community2.tex}}
-            \caption{Simplification of the 3 Community network at $t=2$.}
+            \caption{$t=2$}
             \label{3community train series, b}            
@@
             \resizebox{.6\width}{!}{\input{SynthDataDiagrams/3community3.tex}}
-            \caption{Simplification of the 3 Community network at $t=3$.}
+            \caption{$t=3$}
             \label{3community train series, c}
         \end{subfigure}
-        \caption{First 3 time steps of synthetic 3 community network.}
+        \caption{First 3 time steps of the simplified, synthetic 3 community networks.
+The red node represents the target node which we aim to model.
+The 3, 4, and 5 node components represent the 30, 35, and 40 node communities respectively.
+At each time step the one edge is removed between the target node and the community it has the fewest connections with.}
         \label{3community train series}
     \end{figure}
-    The 2 community temporal network was selected to illustrate that this process can be used to model a node changing communities in ideal conditions, and the long tail network was selected because we wanted to present these models with a range of problems.
-The two community problem is difficult for the neural network to learn because the same set of distances as input need to result in different outputs.
-The long tail problem is difficult for the embedding because a large portion of the network is along the off diagonals; meaning that, to get an accurate embedding, the dimension of the embedding would need to be close to the length of the tail.
-The three community problem should be the easiest to solve because it has been dileberately constructed to avoid the problems the other two models face.
+
+    The three community was chosen as a best case scenario system to model.
+It has been constructed to avoid the challenges that are posed by the 2 community and long tail systems.
+That is, because in this system the target node is moving away from its least similar community, not moving from one community to another, it is not required to overcome the issue of symmetrical input.
+And because there are no long tails in this system, the SVD is able to capture a lot of the system with a low dimensional.
 
@@
 \begin{section}{Results and Discussion}
-    For each of theses systems, we took embedded the temporal network in two dimensions at each time step.
+    \subsection{Network Prediction}
+    To compare our models, we look at the loss of the predictions. This includes the loss from the SVD.
+
+    To find the approximation of the edges of node $i$, $_tA_{i,\cdot}$. We use: 
+    \begin{align}
+        _tA_{i,\cdot} &\approxeq (\bar p) _t\hat A
+    \end{align}
+    Where $\bar p$ is the location of the node $i$ in the embedding at time $t$.
+
+    To find calculate the loss of our prediction at time $t$, we use:
+    \begin{align}
+        L = ||_tA_{i,\cdot} - (\bar p) _t\hat A||_1
+    \end{align}
+
+    When we do this for the SVD, NN, and symbolic regression, we get \autoref{loss_table}.
+    \begin{figure}
+        \begin{center}
+            \begin{tabular}{| m{0.17\textwidth} | m{0.25\textwidth} | m{0.25\textwidth} | m{0.25\textwidth} |}
+                \hline
+                Sequence & Embedding Loss & Neural Network Prediction Loss & Symbolic Regression Prediction Loss\\ 
+                \hline
+                \hline
+                2 Community & 41.67 & 47.91 & 35.11\\ 
+                \hline 
+                Long Tail & 2.408 & 1.193 & 2.524 \\ 
+                \hline 
+                3 Community & 35.43 & 35.50 & 35.57 \\ 
+                \hline 
+            \end{tabular}
+            \end{center}
+            \caption{A summary of the mean loss of each prediction at the fifth time step.
+The embedding loss comes from the true target node and loss is only introduced by the SVD.
+The neural network and symbolic prediction loss comes from the RDPG being reconstructed but with the position of the target node replaced with the location of the respective prediction.
+Loss is calculated as the total number of incorrectly predicted edges.
+That is an edge not being present when it should as well as the reverse.}
+            \label{loss_table}
+    \end{figure}
+
+    The loss of one system should not be compared with another.
+That is the 2 community losses should not be compared to the long tail.
+This is because the long tail system will only ever have one edge to predict, whereas the 2 community will have 50 edges that need to be predicted.
+
+    Instead, we may compare predictions within the same system.
+However, we do not see much difference between these predictions, and so we plot our predictions at each time step to further understand the behavior of our framework.
+
+    For each of these systems, we took embedded the temporal network in two dimensions at each time step.
 The temporal embeddings were then divided into a training set of 20 and a testing set of 15.
@@
 As such, we see the target node move towards the second community.
+
     \begin{subsection}{2 Community}
@@
                 \begin{subfigure}[p]{0.3\textwidth}
-                    \includegraphics[width=\linewidth]{./Plots/Test Only/2communities/2communities \i.png}
+                    \includegraphics[width=\linewidth]{../Code/Plots/Test Only/2communities/2communities \i.png}
                     \caption{t=\i}
+                    \label{2community series \i}
                 \end{subfigure}\quad
@@
         \end{figure}
+        We see the neural network model quickly jumps to around $(-0.5,-0.5)$ where it sits for the entire simulation.
+This happened across many training periods; either a few time steps after the training period or right at the end of it, the neural network model moved towards a stable point where it remained for the test period.
 
-        In this case we see the neural network in one timestep jumps to around (-1.75, 0.4) where it remains until the end of the training data.
-In contrast, the symbolic regression remains relatively close to the true target node until the last time step when the symbolic regression moves away from the target node.\\
+        In contrast, the symbolic regression predicted the location of the target node very well at the beginning of the test period, but after about 5 steps starts to drift away.
+
+        The poor predictive behaviour of the neural network especially may be attributed to this being a symmetrical problem.
+That is the same set of distances as input into the neural network, the target node needs to move away from its nearest neighbours in the first half, then move towards its nearest neighbours in the second half.
+Potential ways of breaking this symmetry may be to include information of the previous time step, or to include the absolute position of the target node as input into the neural network.
+
+        Notably, using the small neural network model to train the symbolic regression gave much better predictions than the large neural network\ref{2community series large neural network}.
 
@@
 This downward curve may be because the problem that we are trying to solve is symmetrical.
-That is the same set of distances as input into the neural network, the target node needs to move away from its nearest neighbours in the first half, then move towards its nearest neighbours in the second half.
-Potential ways of breaking this symmetry may be to include information of the previous timestep, or to include the absolute position of the target node as input into the neural network.
+That is
     \end{subsection}
@@
                 \begin{subfigure}[p]{0.3\textwidth}
-                    \includegraphics[width=\linewidth]{./Plots/Test Only/longTail/longTail \i.png}
+                    \includegraphics[width=\linewidth]{../Code/Plots/Test Only/longTail/longTail \i.png}
                     \caption{t=\i}
+                    \label{longtail series \i}
                 \end{subfigure}\quad
@@
         \end{figure}
-        In fig \autoref{longtail series} we see the true embedding of the target node jump from one arm to the other at each timestep.
-It is clear that neither the the symbolic regression model nor the neural network model capture this movement.
+        In fig \autoref{longtail series} we see the true embedding of the target node jump from one arm to the other at each time step.
+It is clear that neither the symbolic regression model nor the neural network model capture this movement.
 We also see that the symbolic regression model maintains a relatively stable position when compared to the neural network model.
@@
 One reason for this may again be an issue of symmetrical input.
-The distances from the k nearest neighbours to the target node do not seem to change much as the target node jumps from one arm to the other, but the neural network somehow needs to learn to jump left then right at alternating timesteps.
+The distances from the k nearest neighbours to the target node do not seem to change much as the target node jumps from one arm to the other, but the neural network somehow needs to learn to jump left then right at alternating time steps.
 The solutions to this would be the same as for the two community system.
@@
 
-    \begin{subsection}{Three Community (Please Review)}
+    \begin{subsection}{Three Community}
         \begin{figure}
@@
                 \begin{subfigure}[p]{0.3\textwidth}
-                    \includegraphics[width=\linewidth]{./Plots/Test Only/3community/3community \i.png}
+                    \includegraphics[width=\linewidth]{../Code/Plots/Test Only/3community/3community \i.png}
                     \caption{t=\i}
+                    \label{3community series \i}
                 \end{subfigure}\quad
@@
 
+        For the first ten time steps, we see similar behaviour between the neural network model and the neural network model.
+However, around the eleventh time step, the symbolic regression model begins to diverge from the neural network.
+The symbolic regression moves back towards the target node towards the end.
+This could indicate that the symbolic regression is a somewhat more robust model when extrapolating, but more testing should be done to corroborate this.
+
+        Notably the symbolic regression trained on the large neural network performed extremely well, while the predictions of the large neural network model itself did not seem to make any significant improvement\ref{3community series large neural network}.
+This may indicate that...XXXXX
         % In the neural network only model, we see the prediction follow the true target node very closely at first.
@@
 
-        \subsection{Network Prediction}
-        \begin{figure}
-            \begin{center}
-                \begin{tabular}{| m{0.25\textwidth} | m{0.25\textwidth} | m{0.25\textwidth} | m{0.25\textwidth} |}
-                 \hline
-                 Sequence & Embedding Mean Loss & Neural Network Prediction Mean Loss & Symbolic Regression Prediction Mean Loss\\ 
-                 \hline
-                 \hline
-                 2 Community & cell5 & cell6 & c\\ 
-                 \hline 
-                 Long tail & cell8 & cell9 & c \\ 
-                 \hline 
-                 3 Community & cell8 & cell9 & c \\ 
-                 \hline 
-                \end{tabular}
-                \end{center}
-                \caption{my caption}
-        \end{figure}
         \subsection{Summary}
@@
         These were trained on a relatively small neural network (one hidden layer of 64 nodes), when training this small network one of the issues we encountered was that the weights would become stuck in local minima.
-To manage this we found that simulate annaeling was helpful.
+To manage this we found that simulate annealing was helpful.
 When training on a larger network (4 hidden layers (64,8,8,8)) this does not seem to be as much of a problem.
@@
 We then tested this framework on three types of small, synthetic network sequences.
-Throughout these tests the neural network performed XXXXXXX, with the XXXXXX sequence being especially notable due to XXXXX.
-These results were likely because XXXXX.
-In contrast, when we used symbolic regression to approximate the neural network model, we saw that XXXXX.
+Throughout these tests the neural network performed generally more poorly than the symbolic regression model, with the large three community sequence being especially notable due to th symbolic regression remaining so close to the target node throughout the test period.
 \end{section}

### 2023-05-16 Conference Submission/DraftDoc.tex
dhtn

@@
 
-\begin{section}{Introduction}
-    The modelling of temporal networks is an important task in many real world applications including symptom interactions for mental health \cite{jordan2020current,contreras2020temporal}, epidemiology \cite{masuda2013predicting}, and protein interactions \cite{lucas2021inferring,jin2009identifying}.
-    Temporal networks can be seen as dynamical systems: that is a system in which we have points, in our case nodes in a network, whose states, the edges connecting them, that vary dependent in time.
-    Discovering the underlying equations governing these dynamical systems proves challenging, because changes in network structure are typically observed in the form of discrete jumps from one state to another, for example an edge between two nodes not being observed at the first time step then appearing at the next.
-    Here, we propose a hybrid statistical and deep learning framework that allows us to model temporal networks as continuous-time dynamical systems, discover a fitting set of differential equations describing it, and, exploiting that discovery, predict the time evolution of a network.
+% \begin{section}{Introduction}
+%     The modelling of temporal networks is an important task in many real world applications including symptom interactions for mental health \cite{jordan2020current,contreras2020temporal}, epidemiology \cite{masuda2013predicting}, and protein interactions \cite{lucas2021inferring,jin2009identifying}.
+%     Temporal networks can be seen as dynamical systems: that is a system in which we have points, in our case nodes in a network, whose states, the edges connecting them, that vary dependent in time.
+%     Discovering the underlying equations governing these dynamical systems proves challenging, because changes in network structure are typically observed in the form of discrete jumps from one state to another, for example an edge between two nodes not being observed at the first time step then appearing at the next.
+%     Here, we propose a hybrid statistical and deep learning framework that allows us to model temporal networks as continuous-time dynamical systems, discover a fitting set of differential equations describing it, and, exploiting that discovery, predict the time evolution of a network.
 
-    Differential equations are useful for modelling systems where the state of one variable can effect the trajectories of other variables.
+%     Differential equations are useful for modelling systems where the state of one variable can effect the trajectories of other variables.
 We observe this behavior in temporal networks; nodes' connections within the network can influence the formation and decay of edges between other nodes, for example the phenomenon of preferential attachment observed in \cite{newman2001clustering,capocci2006preferential}, where a node is more lively to gain the connections the more connections it has.
@@
 
-    In the common representation of networks as binary-valued adjacency matrices, the events recorded in a temporal sequence of networks correspond to topological events, such as the appearance or the disappearance of link.
-    Because of the discrete nature of events, directly modelling the temporal networks as dynamical systems would require us to handle discrete jumps.
-    The topological nature of temporal networks, and the discontinuous character of their temporal evolution, make it challenging to use differential equations techniques.
+%     In the common representation of networks as binary-valued adjacency matrices, the events recorded in a temporal sequence of networks correspond to topological events, such as the appearance or the disappearance of link.
+%     Because of the discrete nature of events, directly modelling the temporal networks as dynamical systems would require us to handle discrete jumps.
+%     The topological nature of temporal networks, and the discontinuous character of their temporal evolution, make it challenging to use differential equations techniques.
 
-    Here, we overcome the discreteness problem by interpreting networks as Random Dot Product Graphs; a well established statistical model for complex networks, that embeds nodes in a continuous, low-dimensional metric space by using a truncated singular value decomposition\cite{athreya2017statistical}.
+%     Here, we overcome the discreteness problem by interpreting networks as Random Dot Product Graphs; a well established statistical model for complex networks, that embeds nodes in a continuous, low-dimensional metric space by using a truncated singular value decomposition\cite{athreya2017statistical}.
 In this way we translate the hard problem of modelling discrete events in the space of networks to the easier problem of modelling continuous change in the embedding space.
@@
 
-    In this manuscript, we prove that the temporal network prediction problem can be successfully re-interpreted as a dynamical system modelling problem by taking the singular value decomposition of a sequence of adjacency matrices and training a NNDE to model an approximation to the underlying differential equation.
+%     In this manuscript, we prove that the temporal network prediction problem can be successfully re-interpreted as a dynamical system modelling problem by taking the singular value decomposition of a sequence of adjacency matrices and training a NNDE to model an approximation to the underlying differential equation.
 We then go on to create a symbolic equation of this approximation.
 
-    We apply our proposed framework to three small example temporal networks with the hope of exploring the limitations and strengths of the proposed framework. 
-    The framework we are introducing is extremely flexible, and our research regarding the optimal structure of the Neural Networks used for the NNDEs is just started.
-    We are confident that future research can identify more fitting Neural Network structures than the simple one adopted here.
-    For this reason, we did not yet attempt to benchmark our model against other classic temporal network prediction methods.
-    As it is completely general, we believe that the framework we are introducing can be usefully applied to areas of medicine, especially protein interaction networks; population dynamics for network ecology; and social network modelling.
+%     We apply our proposed framework to three small example temporal networks with the hope of exploring the limitations and strengths of the proposed framework. 
+%     The framework we are introducing is extremely flexible, and our research regarding the optimal structure of the Neural Networks used for the NNDEs is just started.
+%     We are confident that future research can identify more fitting Neural Network structures than the simple one adopted here.
+%     For this reason, we did not yet attempt to benchmark our model against other classic temporal network prediction methods.
+%     As it is completely general, we believe that the framework we are introducing can be usefully applied to areas of medicine, especially protein interaction networks; population dynamics for network ecology; and social network modelling.
 In particular, we discuss how specific domain knowledge relative to the prediction scenario can be taken into account, moving from NNDEs to Universal Differential Equations.
-\end{section}
+% \end{section}
 
-\begin{section}{Methodology}
+% \begin{section}{Methodology}
 
-        We are given a sequence of graphs, and our goal is to predict the next graph in the sequence.
+%         We are given a sequence of graphs, and our goal is to predict the next graph in the sequence.
 To achieve this, we reinterpret each graph as a sequence of points in a latent space; that is, a space in which similar vertices (ones with many of the same neighbours) are mapped to a similar point in space.
@@
 
-        \begin{figure}
-            \centering
-            \begin{subfigure}[c]{1\textwidth}
-                \begin{tabular}{llll}
-                \begin{subfigure}[c]{0.25\textwidth}
-                    \centering
-                    \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology1.tex}}
-                    \label{method net, a}
-                \end{subfigure}
-                &
-                \centering
-                \begin{subfigure}[c]{0.25\textwidth}
-                    \centering
-                    \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology2.tex}}
-                    \label{method net, b}
-                \end{subfigure}
-                &
-                $\cdots$
-                &
-                \centering
-                \begin{subfigure}[c]{0.25\textwidth}
-                    \centering
-                    \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology3.tex}}
-                    \label{method net, c}
-                \end{subfigure}
+%         \begin{figure}
+%             \centering
+%             \begin{subfigure}[c]{1\textwidth}
+%                 \begin{tabular}{llll}
+%                 \begin{subfigure}[c]{0.25\textwidth}
+%                     \centering
+%                     \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology1.tex}}
+%                     \label{method net, a}
+%                 \end{subfigure}
+%                 &
+%                 \centering
+%                 \begin{subfigure}[c]{0.25\textwidth}
+%                     \centering
+%                     \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology2.tex}}
+%                     \label{method net, b}
+%                 \end{subfigure}
+%                 &
+%                 $\cdots$
+%                 &
+%                 \centering
+%                 \begin{subfigure}[c]{0.25\textwidth}
+%                     \centering
+%                     \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology3.tex}}
+%                     \label{method net, c}
+%                 \end{subfigure}
 
-                \end{tabular}
-                \caption{Example sequence of networks.}
-                \label{method nets}
+%                 \end{tabular}
+%                 \caption{Example sequence of networks.}
+%                 \label{method nets}
 
-            \end{subfigure}
-            \begin{subfigure}[c]{1\textwidth}
-                \begin{tabular}{llll}
-                    $\begin{bmatrix}
-                        \cdot & 1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
-                        1 & \cdot & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
-                        1 & 1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot\\
-                        1 & \cdot & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
-                        \cdot & \cdot & 1 & \cdot & \cdot & 1 & 1 & \cdot\\
-                        \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & \cdot\\
-                        \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & 1\\
-                        \cdot & \cdot & \cdot & \cdot & \cdot & \cdot & 1 & \cdot
-                    \end{bmatrix}$
-                    &
-                    $\begin{bmatrix}
-                        \cdot & 1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
-                        1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
-                        1 & 1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot\\
-                        1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
-                        \cdot & \cdot & 1 & \cdot & \cdot & 1 & 1 & \cdot\\
-                        \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & 1\\
-                        \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & 1\\
-                        \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot
-                    \end{bmatrix}$
-                    &
-                    $\cdots$
-                    &
-                    $\begin{bmatrix}
-                        \cdot & 1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
-                        1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
-                        1 & 1 & \cdot & 1 & \cdot & \cdot & \cdot & \cdot\\
-                        1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
-                        \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot\\
-                        \cdot & \cdot & \cdot & \cdot & 1 & \cdot & 1 & 1\\
-                        \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot & 1\\
-                        \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot
-                    \end{bmatrix}$
+%             \end{subfigure}
+%             \begin{subfigure}[c]{1\textwidth}
+%                 \begin{tabular}{llll}
+%                     $\begin{bmatrix}
+%                         \cdot & 1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
+%                         1 & \cdot & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
+%                         1 & 1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot\\
+%                         1 & \cdot & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
+%                         \cdot & \cdot & 1 & \cdot & \cdot & 1 & 1 & \cdot\\
+%                         \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & \cdot\\
+%                         \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & 1\\
+%                         \cdot & \cdot & \cdot & \cdot & \cdot & \cdot & 1 & \cdot
+%                     \end{bmatrix}$
+%                     &
+%                     $\begin{bmatrix}
+%                         \cdot & 1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
+%                         1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
+%                         1 & 1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot\\
+%                         1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
+%                         \cdot & \cdot & 1 & \cdot & \cdot & 1 & 1 & \cdot\\
+%                         \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & 1\\
+%                         \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & 1\\
+%                         \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot
+%                     \end{bmatrix}$
+%                     &
+%                     $\cdots$
+%                     &
+%                     $\begin{bmatrix}
+%                         \cdot & 1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
+%                         1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
+%                         1 & 1 & \cdot & 1 & \cdot & \cdot & \cdot & \cdot\\
+%                         1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
+%                         \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot\\
+%                         \cdot & \cdot & \cdot & \cdot & 1 & \cdot & 1 & 1\\
+%                         \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot & 1\\
+%                         \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot
+%                     \end{bmatrix}$
 
-                \end{tabular}
-                \caption{Sequence of sparse adjacency matrices associated with the networks in \autoref{method nets}.}
-                \label{method adjacency}
-            \end{subfigure}
+%                 \end{tabular}
+%                 \caption{Sequence of sparse adjacency matrices associated with the networks in \autoref{method nets}.}
+%                 \label{method adjacency}
+%             \end{subfigure}
 
-            \begin{tabular}{llll}
+%             \begin{tabular}{llll}
 
-            \end{tabular}
+%             \end{tabular}
 
-            \caption{Visual illustration of the proposed framework.}
-            \label{framework illustration}
-        \end{figure}
+%             \caption{Visual illustration of the proposed framework.}
+%             \label{framework illustration}
+%         \end{figure}
 
-        \subsection{Singular Value Decomposition and Random Dot Product Graphs}
-            \label{svd}
-            In this section we discuss the Singular Value Decomposition (SVD) of a matrix, and its usefulness in creating Random Dot Product Graphs (RDPG).
+%         \subsection{Singular Value Decomposition and Random Dot Product Graphs}
+%             \label{svd}
+%             In this section we discuss the Singular Value Decomposition (SVD) of a matrix, and its usefulness in creating Random Dot Product Graphs (RDPG).
 
-            We define the matrix $A$ to be a real $m \times n$ with $n \le m$. $A$ can be expressed as \cite{forsythe1967computer}:
-            \begin{align}
-                A&=L\Sigma R'
-            \end{align}
-            Where $L, R$ are real valued, orthonormal matrices.
+%             We define the matrix $A$ to be a real $m \times n$ with $n \le m$. $A$ can be expressed as \cite{forsythe1967computer}:
+%             \begin{align}
+%                 A&=L\Sigma R'
+%             \end{align}
+%             Where $L, R$ are real valued, orthonormal matrices.
 The columns of $L$ consist of the $n$ largest eigenvectors of $AA'$ and the columns $R$ consist of the eigenvectors of $A'A$.
@@
 
-            In order to reduce the problem size, we can truncate the $L,R,\Sigma$ to the first $d$ columns to yield, $\hat L, \hat R, \hat \Sigma$ such that:
+%             In order to reduce the problem size, we can truncate the $L,R,\Sigma$ to the first $d$ columns to yield, $\hat L, \hat R, \hat \Sigma$ such that:
 
-            \begin{align}
-                A &\approx \hat L \hat \Sigma \hat R' \\
-                \hat A &= \hat L \hat \Sigma \hat R'
-                \label{approx}
-            \end{align}
+%             \begin{align}
+%                 A &\approx \hat L \hat \Sigma \hat R' \\
+%                 \hat A &= \hat L \hat \Sigma \hat R'
+%                 \label{approx}
+%             \end{align}
 
-            The approximation of $A$ is defined as $\hat A$ and is given by \autoref{approx} can be interpreted as a graph where the entry $(i,j)$ of the matrix is the probability that an edge exists from $i \rightarrow j$.
+%             The approximation of $A$ is defined as $\hat A$ and is given by \autoref{approx} can be interpreted as a graph where the entry $(i,j)$ of the matrix is the probability that an edge exists from $i \rightarrow j$.
 This approximation of $A$ is known as an RDPG.
 
-            It is important to note that the SVD is not unique.
+%             It is important to note that the SVD is not unique.
 The distances between points will be the same for every embedding, but the orientation may be different, and so, if the SVD of each time step is not aligned, learning will be effectively impossible as we will essentially be trying to model random noise.
@@
 
-            The SVD gives is an RDPG\cite{athreya2017statistical}.
+%             The SVD gives is an RDPG\cite{athreya2017statistical}.
 The SVD can be considered to give a latent space representation of the matrix\cite{hoff2002latent}.
@@
 
-            When obtaining the RDPGs for our temporal network, we take each network observation \autoref{method nets} and represent them in the form of an adjacency matrix \autoref{method adjacency}.
+%             When obtaining the RDPGs for our temporal network, we take each network observation \autoref{method nets} and represent them in the form of an adjacency matrix \autoref{method adjacency}.
 We then use a truncated singular value decomposition to reduce the dimensionality of our adjacency matrices\cite{golub1971singular}.
@@
 
-            To execute the SVD we use the ARPACK Julia package \cite{lehoucq1998arpack}.
+%             To execute the SVD we use the ARPACK Julia package \cite{lehoucq1998arpack}.
 This package uses an iterative approach to approximate the eigenvectors and singular values of each of our adjacency matrices\cite{lehoucq1996deflation}.
 
-    \subsection{Neural Network Differential Equation}
-        Once we have the SVD embedding of points, we look to model the trajectories of a target point.
+%     \subsection{Neural Network Differential Equation}
+%         Once we have the SVD embedding of points, we look to model the trajectories of a target point.
 That is, with some input data, point location, distance to neighbours, etc, we want to model the differential equation that governs the movement of a point.
@@
 
-        Our problem can be defined as:
-        \begin{align}
-            A_{t+1} = f(A(t),t)
-        \end{align}
-        Where $A_t$ is the adjacency matrix of the temporal network at time $t$.
+%         Our problem can be defined as:
+%         \begin{align}
+%             A_{t+1} = f(A(t),t)
+%         \end{align}
+%         Where $A_t$ is the adjacency matrix of the temporal network at time $t$.
 By using the SVD to obtain the approximation $\hat A_t$, which can evolve continuously, we can reinterpret our problem as:
 
-        \begin{align}
-            \frac{d\hat A}{dt} &= g(\hat A(t), t)
-        \end{align}
+%         \begin{align}
+%             \frac{d\hat A}{dt} &= g(\hat A(t), t)
+%         \end{align}
 
-        In this thesis, as a proof of concept, we focus on a modelling the change in structure of a single node, referred to as the target node $u$. In this case, the form of the problem becomes:
+%         In this thesis, as a proof of concept, we focus on a modelling the change in structure of a single node, referred to as the target node $u$. In this case, the form of the problem becomes:
 
-        \begin{align}
-            \frac{du}{dt} &= g(u(t), t)
-        \end{align}
+%         \begin{align}
+%             \frac{du}{dt} &= g(u(t), t)
+%         \end{align}
 
-        Because we are only modelling the movement of a single node, we assume that we have access to the rest of the network structure at every time step for the prediction.
+%         Because we are only modelling the movement of a single node, we assume that we have access to the rest of the network structure at every time step for the prediction.
 This would likely not be the case in a real world application, but will allow us to observe some of the strengths and weaknesses of this framework in a controlled setting.
@@
 
-        Here we train a neural network to approximate the function $g(u(t),t)=NN(u(t),t,\theta)$. Where $\theta$ is the parameters of the neural network.
+%         Here we train a neural network to approximate the function $g(u(t),t)=NN(u(t),t,\theta)$. Where $\theta$ is the parameters of the neural network.
 
-        To obtain this differential equation we make use of the SciML ecosystem of packages in the Julia programming language \cite{SciML_C_Rak}.
+%         To obtain this differential equation we make use of the SciML ecosystem of packages in the Julia programming language \cite{SciML_C_Rak}.
 
-        % KNN Explaination
-        As a way of limiting the complexity of our model, we limit the input of the neural network to the euclidean distances between the target node and its $k$ nearest neighbours.
+%         % KNN Explaination
+%         As a way of limiting the complexity of our model, we limit the input of the neural network to the euclidean distances between the target node and its $k$ nearest neighbours.
 The target node is the node that we are looking to model the movement of and stays the same throughout each of the temporal networks.
-        % \begin{align}
-    %     %\centering
-    %     \mathbb{P}(i\rightarrow j)&\coloneqq L_i \cdot R_j\\
-    %     \mathbb{P}(\hat{i}\rightarrow j)&\coloneqq L_{\hat{i}} \cdot R_j
-    % \end{align}
-    % Where $(i,j)$ are nodes in the network and $\hat{i}$ is another node at the same timestep to $i$. This implies that the distance between these two nodes with respect to node $j$ is given by
-    % \begin{equation}
-    %     \begin{gathered}
-    %         %\centering
-    %         ||\mathbb{P}(i\rightarrow j)-\mathbb{P}(\hat{i}\rightarrow j)||_2 = 
-    %         ||L_i \cdot R_j-L_{\hat{i}} \cdot R_j||_2\\
-    %         =||(L_i -L_{\hat{i}}) \cdot R_j||_2
-    %     \end{gathered}
-    % \end{equation}
-    % If we look at the expectation of this, we see
-    % \begin{equation}
-    %     \begin{gathered}
-    %         %\centering
-    %         \mathbb{E}_j(||(L_i -L_{\hat{i}}) \cdot R_j||_2) = ||(L_i -L_{\hat{i}}) \cdot \frac{1}{k}\sum_{j\ne i}R_j||_2
-    %     \end{gathered}
-    % \end{equation}
-    % Where $k$ is the number of neighbours we chose for the neural network input. Because the distance between points is described by the euclidean distance, we use this as our loss metric.
+%         % \begin{align}
+%     %     %\centering
+%     %     \mathbb{P}(i\rightarrow j)&\coloneqq L_i \cdot R_j\\
+%     %     \mathbb{P}(\hat{i}\rightarrow j)&\coloneqq L_{\hat{i}} \cdot R_j
+%     % \end{align}
+%     % Where $(i,j)$ are nodes in the network and $\hat{i}$ is another node at the same timestep to $i$. This implies that the distance between these two nodes with respect to node $j$ is given by
+%     % \begin{equation}
+%     %     \begin{gathered}
+%     %         %\centering
+%     %         ||\mathbb{P}(i\rightarrow j)-\mathbb{P}(\hat{i}\rightarrow j)||_2 = 
+%     %         ||L_i \cdot R_j-L_{\hat{i}} \cdot R_j||_2\\
+%     %         =||(L_i -L_{\hat{i}}) \cdot R_j||_2
+%     %     \end{gathered}
+%     % \end{equation}
+%     % If we look at the expectation of this, we see
+%     % \begin{equation}
+%     %     \begin{gathered}
+%     %         %\centering
+%     %         \mathbb{E}_j(||(L_i -L_{\hat{i}}) \cdot R_j||_2) = ||(L_i -L_{\hat{i}}) \cdot \frac{1}{k}\sum_{j\ne i}R_j||_2
+%     %     \end{gathered}
+%     % \end{equation}
+%     % Where $k$ is the number of neighbours we chose for the neural network input. Because the distance between points is described by the euclidean distance, we use this as our loss metric.
 
-    % Symbolic Regression Explaination
-    \subsection{Symbolic Regression}
-        With our trained NODE, we have a black box that approximates the system that governs the movement of the target node in the embedded space.
+%     % Symbolic Regression Explaination
+%     \subsection{Symbolic Regression}
+%         With our trained NODE, we have a black box that approximates the system that governs the movement of the target node in the embedded space.
 To make this more interpretable we then look to approximate this black box into a combination of known functions using symbolic regression\cite{pysr}.
 
-        Symbolic regression is a type of regression analysis that searches a space of equations to find an expression that matches data.
+%         Symbolic regression is a type of regression analysis that searches a space of equations to find an expression that matches data.
 We use the genetic programming algorithm found in \cite{pysr}.
@@
 
-        \begin{figure}
-            \centering
-            \resizebox{\width}{!}{\input{SynthDataDiagrams/symbreg.tex}}
-            \caption{Illustration of the genetic programming symbolic regression process.}
-            \label{symbreg}
-        \end{figure}
+%         \begin{figure}
+%             \centering
+%             \resizebox{\width}{!}{\input{SynthDataDiagrams/symbreg.tex}}
+%             \caption{Illustration of the genetic programming symbolic regression process.}
+%             \label{symbreg}
+%         \end{figure}
 
-        The fitness of a candidate function is determined by comparing the predicted value to the given data, as well as the derivatives of the candidate equations to numerically found partial derivatives of the data variable.
+%         The fitness of a candidate function is determined by comparing the predicted value to the given data, as well as the derivatives of the candidate equations to numerically found partial derivatives of the data variable.
 
-        For this process we need to define a set of functions which the algorithm will use to generate a tree of functions to find the best approximation to our NNDE with.
+%         For this process we need to define a set of functions which the algorithm will use to generate a tree of functions to find the best approximation to our NNDE with.
 When using this method we are usually required to make two assumptions: that we have paired observations of $y(t), \frac{dy}{dt}$, and that the tree of expressions we will need is shallow.
@@
 
-    \subsection{Reconstructing the Temporal Network}
-        To recover a final prediction, the point vector of the target node with the matrix $R'$, this gives a vector of probabilities of connections between the target node and the rest of the network.
+%     \subsection{Reconstructing the Temporal Network}
+%         To recover a final prediction, the point vector of the target node with the matrix $R'$, this gives a vector of probabilities of connections between the target node and the rest of the network.
 As the results can be interpreted as a probability, the most likely graph is given by setting any entry with a value of $0.5$ or higher to one (predict that the edge exists), and setting any entry with a value of less than $0.5$ to zero (predict that an edge does not exist).
-\end{section}
+% \end{section}
 
-\begin{section}{Data}
-    In this paper we simulate three temporal sequences of undirected graphs.
+% \begin{section}{Data}
+%     In this paper we simulate three temporal sequences of undirected graphs.
 For each sequence we will be modelling the node in red, we will refer to this as the target node.
@@
 
-    \subsection{Two Community System}
-        The 2 community network has communities of size 40 and 50, each of which are fully connected.
+%     \subsection{Two Community System}
+%         The 2 community network has communities of size 40 and 50, each of which are fully connected.
 The target node is initially fully connected to the 50 node community.
@@
 
-        Figures obtained from \cite{Emma2023}.
-        \begin{figure}[H]
-            \centering
-            \centering
-            \begin{subfigure}[c]{0.3\textwidth}
-                \centering
-                \resizebox{.6\width}{!}{\input{SynthDataDiagrams/2community1.tex}}
-                \caption{$t=1$}
-                \label{2community train series, a}
-            \end{subfigure}
-            \hfill
-            \centering
-            \begin{subfigure}[c]{0.3\textwidth}
-                \centering
-                \resizebox{.6\width}{!}{\input{SynthDataDiagrams/2community2.tex}}
-                \caption{$t=2$}
-                \label{2community train series, b}
-            \end{subfigure}
-            \hfill
-            \centering
-            \begin{subfigure}[c]{0.3\textwidth}
-                \centering
-                \resizebox{.6\width}{!}{\input{SynthDataDiagrams/2community3.tex}}
-                \caption{$t=3$}
-                \label{2community train series, c}
-            \end{subfigure}
-            \caption{First 3 time steps of the simplified, synthetic 2 community network.
+%         Figures obtained from \cite{Emma2023}.
+%         \begin{figure}[H]
+%             \centering
+%             \centering
+%             \begin{subfigure}[c]{0.3\textwidth}
+%                 \centering
+%                 \resizebox{.6\width}{!}{\input{SynthDataDiagrams/2community1.tex}}
+%                 \caption{$t=1$}
+%                 \label{2community train series, a}
+%             \end{subfigure}
+%             \hfill
+%             \centering
+%             \begin{subfigure}[c]{0.3\textwidth}
+%                 \centering
+%                 \resizebox{.6\width}{!}{\input{SynthDataDiagrams/2community2.tex}}
+%                 \caption{$t=2$}
+%                 \label{2community train series, b}
+%             \end{subfigure}
+%             \hfill
+%             \centering
+%             \begin{subfigure}[c]{0.3\textwidth}
+%                 \centering
+%                 \resizebox{.6\width}{!}{\input{SynthDataDiagrams/2community3.tex}}
+%                 \caption{$t=3$}
+%                 \label{2community train series, c}
+%             \end{subfigure}
+%             \caption{First 3 time steps of the simplified, synthetic 2 community network.
 The red node represents the target node that we are aiming to model.
@@
 At each time step, an edge from the target node to the larger community is replaced with and edge from the target node to the smaller community.}
-            \label{2community train series}
-        \end{figure}
-        The 2 community temporal network was selected to test whether this framework can be used to model a node changing communities in systems where there are no other processes occurring.
+%             \label{2community train series}
+%         \end{figure}
+%         The 2 community temporal network was selected to test whether this framework can be used to model a node changing communities in systems where there are no other processes occurring.
 Notably, the movement in the two community system is difficult for the neural network to learn because opposite sets of inputs need to result in the same output.
@@
 
-    \subsection{Long Tail System}
-        In the long tail network \autoref{longTail train series}, we have a long chain with 50 nodes and a fully connected component with forty nodes at one end of the chain.
+%     \subsection{Long Tail System}
+%         In the long tail network \autoref{longTail train series}, we have a long chain with 50 nodes and a fully connected component with forty nodes at one end of the chain.
 This is used to orient the embedding and model.
@@
 Again, this is repeated to generate the training and test data \autoref{longTail train series, c}.
-        \begin{figure}[H]
-            \centering
-            \begin{subfigure}[c]{0.3\textwidth}
-                \centering
-                \resizebox{.6\width}{!}{\input{SynthDataDiagrams/longTail1.tex}}
-                \caption{$t=1$}
-                \label{longTail train series, a}
-            \end{subfigure}
-            \hfill
-            \centering
-            \begin{subfigure}[c]{0.3\textwidth}
-                \centering
-                \resizebox{.6\width}{!}{\input{SynthDataDiagrams/longTail2.tex}}
-                \caption{$t=2$}
-                \label{longTail train series, b}
-            \end{subfigure}
-            \hfill
-            \centering
-            \begin{subfigure}[c]{0.3\textwidth}
-                \centering
-                \resizebox{.6\width}{!}{\input{SynthDataDiagrams/longTail3.tex}}
-                \caption{$t=3$}
-                \label{longTail train series, c}
-            \end{subfigure}\\
-            \caption{First 3 time steps of the simplified, synthetic long tail network.
+%         \begin{figure}[H]
+%             \centering
+%             \begin{subfigure}[c]{0.3\textwidth}
+%                 \centering
+%                 \resizebox{.6\width}{!}{\input{SynthDataDiagrams/longTail1.tex}}
+%                 \caption{$t=1$}
+%                 \label{longTail train series, a}
+%             \end{subfigure}
+%             \hfill
+%             \centering
+%             \begin{subfigure}[c]{0.3\textwidth}
+%                 \centering
+%                 \resizebox{.6\width}{!}{\input{SynthDataDiagrams/longTail2.tex}}
+%                 \caption{$t=2$}
+%                 \label{longTail train series, b}
+%             \end{subfigure}
+%             \hfill
+%             \centering
+%             \begin{subfigure}[c]{0.3\textwidth}
+%                 \centering
+%                 \resizebox{.6\width}{!}{\input{SynthDataDiagrams/longTail3.tex}}
+%                 \caption{$t=3$}
+%                 \label{longTail train series, c}
+%             \end{subfigure}\\
+%             \caption{First 3 time steps of the simplified, synthetic long tail network.
 The red node represents the target node that we are aiming to model.
@@
 At each time step the target node moves one step further along the chain, away from the large community.}
-            \label{longTail train series}
-        \end{figure}
+%             \label{longTail train series}
+%         \end{figure}
 
-        The long tail network was selected because the SVD performs poorly on highly diagonal matrices; that is matrices with long chains.
+%         The long tail network was selected because the SVD performs poorly on highly diagonal matrices; that is matrices with long chains.
 The long tail problem is difficult for the embedding because a large portion of the network is along the off diagonals; meaning that, to get an accurate embedding, the dimension of the embedding would need to be close to the length of the tail.
@@
 
-    \subsection{Three community System}
-    We also simulate a sequence with three communities.
+%     \subsection{Three community System}
+%     We also simulate a sequence with three communities.
 The communities have sizes 40, 35, 30 and have 25, 24, and 23 edges to the target node respectively.
@@
 The community with the fewest edges between the target node will have one edge removed at each time step \autoref{3community train series, b}, and this process is repeated to create the required number of time steps \autoref{3community train series, c}.
-    \begin{figure}[H]
-        \centering
-        \centering
-        \begin{subfigure}[c]{0.3\textwidth}
-            \centering
-            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/3community1.tex}}
-            \caption{$t=1$}
-            \label{3community train series, a}
-        \end{subfigure}
-        \hfill
-        \centering
-        \begin{subfigure}[c]{0.3\textwidth}
-            \centering
-            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/3community2.tex}}
-            \caption{$t=2$}
-            \label{3community train series, b}            
-        \end{subfigure}
-        \hfill
-        \centering
-        \begin{subfigure}[c]{0.3\textwidth}
-            \centering
-            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/3community3.tex}}
-            \caption{$t=3$}
-            \label{3community train series, c}
-        \end{subfigure}
-        \caption{First 3 time steps of the simplified, synthetic 3 community networks.
+%     \begin{figure}[H]
+%         \centering
+%         \centering
+%         \begin{subfigure}[c]{0.3\textwidth}
+%             \centering
+%             \resizebox{.6\width}{!}{\input{SynthDataDiagrams/3community1.tex}}
+%             \caption{$t=1$}
+%             \label{3community train series, a}
+%         \end{subfigure}
+%         \hfill
+%         \centering
+%         \begin{subfigure}[c]{0.3\textwidth}
+%             \centering
+%             \resizebox{.6\width}{!}{\input{SynthDataDiagrams/3community2.tex}}
+%             \caption{$t=2$}
+%             \label{3community train series, b}            
+%         \end{subfigure}
+%         \hfill
+%         \centering
+%         \begin{subfigure}[c]{0.3\textwidth}
+%             \centering
+%             \resizebox{.6\width}{!}{\input{SynthDataDiagrams/3community3.tex}}
+%             \caption{$t=3$}
+%             \label{3community train series, c}
+%         \end{subfigure}
+%         \caption{First 3 time steps of the simplified, synthetic 3 community networks.
 The red node represents the target node which we aim to model.
@@
 At each time step the one edge is removed between the target node and the community it has the fewest connections with.}
-        \label{3community train series}
-    \end{figure}
+%         \label{3community train series}
+%     \end{figure}
 
-    The three community was chosen as a best case scenario system to model.
+%     The three community was chosen as a best case scenario system to model.
 It has been constructed to avoid the challenges that are posed by the 2 community and long tail systems.
@@
 
-\end{section}
+% \end{section}
 
@@
                 \begin{subfigure}[p]{0.3\textwidth}
-                    \includegraphics[width=\linewidth]{../Code/Plots/Test Only/2communities/2communities \i.png}
+                    \includegraphics[width=\linewidth]{../Code/Plots/Test Only/2communities/2communities \i \space small net.png}
                     \caption{t=\i}
@@
                 \begin{subfigure}[p]{0.3\textwidth}
-                    \includegraphics[width=\linewidth]{../Code/Plots/Test Only/longTail/longTail \i.png}
+                    \includegraphics[width=\linewidth]{../Code/Plots/Test Only/longTail/longTail \i \space small net.png}
                     \caption{t=\i}
@@
                 \begin{subfigure}[p]{0.3\textwidth}
-                    \includegraphics[width=\linewidth]{../Code/Plots/Test Only/3community/3community \i.png}
+                    \includegraphics[width=\linewidth]{../Code/Plots/Test Only/3community/3community \i \space small net.png}
                     \caption{t=\i}

### 2023-06-05 Code/1NN vs 2NN/1NN with for loop.jl
2 dimensional predictions

@@ -1,5 +1,10 @@
 using CSV, DataFrames, LinearAlgebra, Revise, CUDA
 using DifferentialEquations, Lux, SciMLSensitivity, ComponentArrays
+using Optimization, OptimizationOptimisers, OptimizationOptimJL, Optimisers
+using Random
+using Zygote
+import DiffEqFlux: NeuralODE
+
 # CUDA.allowscalar(false)
 # User needs to provide:
 #   u0
@@ -11,18 +16,14 @@ using DifferentialEquations, Lux, SciMLSensitivity, ComponentArrays
 
 # Things that are important:
 # embedding dim, initial vec for SVD, amount of data
-
+CUDA.allowscalar(false)
 include("../_Modular Functions/helperFunctions.jl")
 include("../_Modular Functions/loadGlobalConstants.jl")
 include("../_Modular Functions/constructNN.jl")
 include("../_Modular Functions/NODEproblem.jl")
-include("../_Modular Functions/reconstructRDPG.jl")
 
 global_consts("longTail", (182,2))
-
-#u1::Array{Float32, 1} = Array{Float32, 1}(undef, output_data_length)
-
-
+device = Lux.cpu
 rng = Random.default_rng()
 nn = Lux.Chain(x -> x,
       Lux.Dense(input_data_length, 64, tanh),
@@ -30,61 +31,70 @@ nn = Lux.Chain(x -> x,
       Lux.Dense(8, 8, tanh),
       Lux.Dense(8, output_data_length))
 
-p, st = Lux.setup(rng, nn)
+p, st = Lux.setup(rng, nn) 
+p = p |> ComponentArray |> device
+st = st |> device
 
-p = p |> ComponentArray #|> Lux.gpu
-# st = st |> Lux.gpu
-
-
-function dudt_pred(u,p,t) 
-
+function dudt_pred(u,p,t)
+  
   M = train_data[t]
-
-  subtract_func(m) = m-u
-  direction_vecs = [subtract_func(m) for m in eachcol(M)]
-
+  subtract_func(m) = m.-u
+  direction_vecs = subtract_func.(eachrow(M))
   û = vcat(partialsort(direction_vecs,1:k, by=x->sum(abs2, x))...)
-  nn(û, p, st)
+  nn(û, p, st)[1]
 end
 
-dudt_pred_(u,p,t) = dudt_pred(u,p,t)[1]
 
[…]

### 2023-06-05 Code/1NN vs 2NN/2NN with for loop .jl

@@ -1,113 +1,0 @@
-using CSV, DataFrames, LinearAlgebra
-using PlotlyJS
-include("../../_Modular Functions/loadMITGraphFlat.jl")
-# User needs to provide:
-#   u0
-#   datasize
-#   tspan
-#   ode_data
-#   input_data_length (length of one input vector)
-#   output_data_length
-EPOCHS = 5
-const datasize = 10
-const dims=(2952,6)   
-
-
-true_data, time_graphs = loadMITGraphFlat();
-true_data = round.(true_data, digits=10);
-
-LR = [reshape(true_data[:,i], (dims[1],dims[2])) for i in 1:size(true_data)[2]]
-true_dataL = hcat([reshape(lr[1:Int(dims[1]/2),:], Int(dims[1]/2)*dims[2]) for lr in LR]...)
-true_dataR = hcat([reshape(lr[1+Int(dims[1]/2):end,:], Int(dims[1]/2)*dims[2]) for lr in LR]...)
-
-
-include("../../_Modular Functions/helperFunctions.jl")
-
-ode_dataL = true_dataL[:,1:datasize]
-ode_dataR = true_dataR[:,1:datasize]
-
-
-tspan = (0.0f0, 1.0f0)
-tsteps = range(tspan[1], tspan[2], length = 2)
-const k = 7
-
-input_data_length = dims[2] + k
-output_data_length = dims[2]
-
-# Process Data
-
-# u0::Array{Float64, 1} = Array{Float64, 1}(undef, input_data_length) # Distance of point at ̲0 is always set to 0 to prevent instability
-u1::Array{Float64, 1} = Array{Float64, 1}(undef, output_data_length)
-
-
-include("../../_Modular Functions/constructNN.jl")
-include("../../_Modular Functions/NODEproblem.jl")
-include("../../_Modular Functions/trainNN.jl")
-include("../../_Modular Functions/reconstructRDPG.jl")
-
-prob_neuralodeL, pL, st = constructNN();
-prob_neuralodeR, pR, st = constructNN();
-
-optprobL = NODEproblem(pL);
-optprobR = NODEproblem(pR);
-
-function predict_neuralode(θ, pnode = prob_neuralodeL)
-    Array(solve(pnode, p=θ, save_everystep=false, reltol=1e-5))
-end
-
-resultL::AbstractVector = []
-for e in 1:EPOCHS
-    println("Epoch: ", e)
-
-    for i in 1:datasize
[…]

### 2023-06-05 Code/1NN vs 2NN/test.jl

@@ -1,61 +1,0 @@
-using Lux, Optimization, OptimizationOptimisers, Zygote, OrdinaryDiffEq, 
-      Plots, CUDA, SciMLSensitivity, Random, ComponentArrays
-import DiffEqFlux: NeuralODE 
-
-CUDA.allowscalar(false) # Makes sure no slow operations are occuring
-
-#rng for Lux.setup
-rng = Random.default_rng()
-# Generate Data
-u0 = Float32[2.0; 0.0]
-datasize = 30
-tspan = (0.0f0, 1.5f0)
-tsteps = range(tspan[1], tspan[2], length = datasize)
-function trueODEfunc(du, u, p, t)
-    true_A = [-0.1 2.0; -2.0 -0.1]
-    du .= ((u.^3)'true_A)'
-end
-prob_trueode = ODEProblem(trueODEfunc, u0, tspan)
-# Make the data into a GPU-based array if the user has a GPU
-ode_data = gpu(solve(prob_trueode, Tsit5(), saveat = tsteps))
-
-
-dudt2 = Chain(x -> x.^3, Dense(2, 50, tanh), Dense(50, 2))
-u0 = Float32[2.0; 0.0] |> gpu
-p, st = Lux.setup(rng, dudt2) 
-p = p |> ComponentArray |> gpu
-st = st |> gpu
-
-prob_neuralode = NeuralODE(dudt2, tspan, Tsit5(), saveat = tsteps)
-
-function predict_neuralode(p)
-  gpu(first(prob_neuralode(u0,p,st)))
-end
-function loss_neuralode(p)
-    pred = predict_neuralode(p)
-    loss = sum(abs2, ode_data .- pred)
-    return loss, pred
-end
-# Callback function to observe training
-list_plots = []
-iter = 0
-callback = function (p, l, pred; doplot = false)
-  global list_plots, iter
-  if iter == 0
-    list_plots = []
-  end
-  iter += 1
-  display(l)
-  # plot current prediction against data
-  plt = scatter(tsteps, Array(ode_data[1,:]), label = "data")
-  scatter!(plt, tsteps, Array(pred[1,:]), label = "prediction")
-  push!(list_plots, plt)
-  if doplot
-    display(plot(plt))
-  end
-  return false
-end
-
-adtype = Optimization.AutoZygote()
-optf = Optimization.OptimizationFunction((x,p)->loss_neuralode(x), adtype)
-optprob = Optimization.OptimizationProblem(optf, p)

### 2023-06-05 Code/PlottingCode/eqnSearch.jl

@@ -1,0 +1,18 @@
+function numbersToParameters(eqn)
+
+end
+
+
+using Symbolics
+@syms p x[1:45] e(X, p)
+arguments.(eqns[1])[1]=p
+p=2
+x40=1
+x20=1
+
+e = eqns[1]
+Symbolics.diff2term(Symbolics.value(eqns[1]))
+
+func = eval(build_function(e, x, p))
+func(x, p)
+e(4,4)

### 2023-06-05 Code/PlottingCode/getSymbRegEqn.jl

@@ -1,0 +1,22 @@
+using SymbolicRegression
+
+function getSymbRegEqn(data, sltn, options)
+    
+    halls = [
+        EquationSearch(
+        data, sltn[i,:], niterations=40, options=options,
+        parallelism=:multithreading
+        )
+        for i in 1:dims[2]
+    ]
+
+
+    dominatings = [
+        calculate_pareto_frontier(Float64.(data), sltn[i,:], halls[i], options)
+        for i in 1:dims[2]
+    ]
+    dominatings
+
+end
+
+

### 2023-06-05 Code/PlottingCode/plotSltn.jl

@@ -1,12 +1,13 @@
 using PlotlyJS
 using ColorSchemes
+using Lux
 include("../_Modular Functions/loadGlobalConstants.jl")
 
 include("../_Modular Functions/pca.jl")
-global_consts("longTail", (182,2))
+global_consts("2communities", (182,2))
 
 include("symreg.jl")
-
+p1, p2 = (1,2)
 
 
 
@@ -27,21 +28,22 @@ using DelimitedFiles
 
 
 sltn = readdlm("./Code/Solutions/$net_name big net test only.csv", ',')
-mid = convert(Int, dims[1]/2)
+
+t_data[1][:AL]
 
 for i in 1:length(t_data)-datasize
-    pts = t_data[i+datasize]'#get_embedding([sltn_sym_reg[:,i]'; t_data[i+datasize]], sltn[:,i])
-    mid = convert(Int, dims[1]/2)
-    traces0 = PlotlyJS.scatter(x=[sltn[1,i]], y=[sltn[2,i]], mode="markers", name="Neural Network Pred", marker_size=12)
-    traces1 = PlotlyJS.scatter(x=[sltn_sym_reg[1,i]], y=[sltn_sym_reg[2,i]], mode="markers", name="Symbolic Regression Pred", marker_size=12)
-    traces2 = PlotlyJS.scatter(x=[pts[1,1]], y=[pts[1,2]], mode="markers", name="Target Node", marker_size=12)
+    pts = t_data[i+datasize][:AL]#get_embedding([sltn_sym_reg[:,i]'; t_data[i+datasize]], sltn[:,i])
     
-    traces3 = PlotlyJS.scatter(x=pts[2:mid,1], y=pts[1:mid,2], mode="markers", name="Data")
+    traces0 = PlotlyJS.scatter(x=[sltn[p1,i]], y=[sltn[p2,i]], mode="markers", name="Neural Network Pred", marker_size=12)
+    traces1 = PlotlyJS.scatter(x=[sltn_sym_reg[p1,i]], y=[sltn_sym_reg[p2,i]], mode="markers", name="Symbolic Regression Pred", marker_size=12)
+    traces2 = PlotlyJS.scatter(x=[pts[1,p1]], y=[pts[1,p2]], mode="markers", name="Target Node", marker_size=12)
+    
[…]

### 2023-06-05 Code/PlottingCode/symreg.jl

@@ -1,29 +1,36 @@
-using SymbolicRegression
+
 using SymbolicUtils
 using DelimitedFiles
+using DataDrivenDiffEq
+using ModelingToolkit
+using OrdinaryDiffEq
+using DataDrivenSparse
+using LinearAlgebra
+
 include("../_Modular Functions/helperFunctions.jl")
+include("getSymbRegEqn.jl")
 
 sltn = readdlm("./Code/Solutions/$net_name big net.csv", ',')
 sltnt = readdlm("./Code/Solutions/$net_name big net test only.csv", ',')
 grad_sltn = sltn[:,2:end].-sltn[:,1:end-1]
 
+
+
 test_range = eachindex(1.0:0.01:Float64(datasize))
 
-trace = scatter(x=sltn[1,:],y=sltn[2,:], mode="markers", name="sltn from start")
-trace2 =  scatter(x=[t_data[i][1,1] for i in 1:datasize],y=[t_data[i][2,1] for i in 1:datasize], mode="markers", name="train")
-trace3 =  scatter(x=[t_data[i+datasize][1,1] for i in 1:length(t_data)-datasize],y=[t_data[i+datasize][2,1] for i in 1:length(t_data)-datasize], mode="markers", name="test")
-trace4 =  scatter(x=sltnt[1,1:end],y=sltnt[2,1:end], mode="markers", name="sltn from test")
-
-plot([trace, trace2, trace3, trace4])
 
 train_data = withoutNode(t_data,1)
 length(train_data)
+
+
+
+
 
 function dists(u,t)
     M = train_data[t]
     
     subtract_func(m) = m-u
-    direction_vecs = [subtract_func(m) for m in eachcol(M)]
+    direction_vecs = [subtract_func(m) for m in eachrow(M)]
 
     û = vcat(partialsort(direction_vecs,1:k, by=x->sum(abs2, x))...)
 
@@ -33,65 +40,120 @@ iter_sltn = [sltn[:,i] for i in 1:size(sltn)[2]]
 data = dists.(iter_sltn, 1.0:0.01:Float64(datasize))
 data = hcat(data...)
 
+# true_sltn = targetNode(t_data,1).AL[1,:,1:datasize]
+# true_iter_sltn = [true_sltn[:,i] for i in 1:size(true_sltn)[2]]
[…]

### 2023-06-05 Code/PlottingCode/visualiseTraining.jl

@@ -1,0 +1,18 @@
+using SymbolicRegression
+using SymbolicUtils
+using DelimitedFiles
+include("../_Modular Functions/helperFunctions.jl")
+
+sltn = readdlm("./Code/Solutions/$net_name big net.csv", ',')
+sltnt = readdlm("./Code/Solutions/$net_name big net test only.csv", ',')
+grad_sltn = sltn[:,2:end].-sltn[:,1:end-1]
+
+test_range = eachindex(1.0:0.01:Float64(datasize))
+p1, p2 = (1,2)
+
+trace = PlotlyJS.scatter(x=sltn[p1,:],y=sltn[p2,:], mode="markers", name="sltn from start")
+trace2 =  PlotlyJS.scatter(x=[t_data[i,:AL][1,p1] for i in 1:datasize],y=[t_data[i,:AL][1,p2] for i in 1:datasize], mode="markers", name="train")
+trace3 =  PlotlyJS.scatter(x=[t_data[i+datasize,:AL][1,p1] for i in 1:length(t_data)-datasize],y=[t_data[i+datasize,:AL][1,p2] for i in 1:length(t_data)-datasize], mode="markers", name="test")
+trace4 =  PlotlyJS.scatter(x=sltnt[p1,1:end],y=sltnt[p2,1:end], mode="markers", name="sltn from test")
+
+PlotlyJS.plot([trace, trace2, trace3, trace4])

### 2023-06-05 Code/_Modular Functions/NODEproblem.jl

@@ -9,13 +9,14 @@ using Lux, DiffEqFlux, DifferentialEquations, Optimization, OptimizationOptimJL,
 #   output_data_length
 
 
-function predict_neuralode(θ)
-  Array(solve(prob_neuralode, Tsit5(), saveat = tsteps, p=θ))#|>Lux.gpu
+function predict_neuralode(θ)  
+  solve(prob_neuralode, Tsit5(), saveat = tsteps, p=θ)|>device
 end
 
 function loss_neuralode(θ)
     pred = predict_neuralode(θ)
-    loss = sum((pred-TNode_data.A[:,1,:]).^2)
+    
+    loss = sum((pred-TNode_data.AL[1,:,:]).^2)
     return loss
 end
 
@@ -24,7 +25,7 @@ callback = function(θ, l)
   #t = t+1
   #M = reshape(ode_data[:,t], (dims[1],dims[2]))
   display(l)
-  global temp_res = θ
+  # global temp_res = θ
   return false
 end
 

### 2023-06-05 Code/_Modular Functions/constructNN.jl

@@ -1,6 +1,5 @@
 using Lux, Random
 
-include("convertToDistances.jl")
 include("helperFunctions.jl")
 
 

### 2023-06-05 Code/_Modular Functions/convertToDistances.jl

@@ -1,6 +1,0 @@
-using LinearAlgebra, Distances
-
-function convertToDistances(p1::AbstractVector, p2::AbstractVector, distance_metric=cosine_dist)::Float64
-    distance_metric(p1,p2)
-end
-

### 2023-06-05 Code/_Modular Functions/createFullSltn.jl

@@ -1,46 +1,22 @@
 
-function createFullSltn(data, prob_neuralode, result)
-    prediction = []
-    for i in 1:size(data)[2]
-        point_preds = []
-        M = reshape(data[:,i], (dims[1],dims[2]))
-        for v in 1:1
-            u0 = includeKNNdists(M[v,:], M[vcat(1:mid.!=v, zeros(Bool, mid)...),:])
-            pnode = remake(prob_neuralode, u0=u0)
+# function createFullSltn(data, prob_neuralode, result)
+#     prediction = []
+#     for i in 1:size(data)[2]
+#         point_preds = []
+#         M = reshape(data[:,i], (dims[1],dims[2]))
+#         for v in 1:1
+#             u0 = includeKNNdists(M[v,:], M[vcat(1:mid.!=v, zeros(Bool, mid)...),:])
+#             pnode = remake(prob_neuralode, u0=u0)
 
 
-            pred = predict_neuralode(result.u; pnode)[1:dims[2],2]
-            push!(point_preds, pred)
-        end
-        p = hcat(point_preds...)
-        push!(prediction, copy(p))
-    end
+#             pred = predict_neuralode(result.u; pnode)[1:dims[2],2]
+#             push!(point_preds, pred)
+#         end
+#         p = hcat(point_preds...)
+#         push!(prediction, copy(p))
+#     end
 
-    return prediction
-end
-
-
-
-# function loss(true_data, prob_neuralode, result)
-#     p = createFullSln(true_data,prob_neuralode, result);
-#     true_pts = [reshape(true_data[:,i], (dims...)) for i in 1:size(true_data)[2]];
-#     return [sum(abs, regenerateNetwork(p[i-1]').-regenerateNetwork(true_pts[i])) for i in 2:size(true_data)[2]]
+#     return prediction
 # end
-
-# function loss(prob_neuralode, result)
-#     p = createFullSln(true_data,prob_neuralode, result);
-#     return [sum(abs, regenerateNetwork(p[i-1]').-time_graphs[i]) for i in 2:size(true_data)[2]]
-# end
-
-# function create_loss_plot(true_data, prob_neuralode, name="")
-#     l1 = loss.([true_data], [prob_neuralode], res)
-#     # l2 = loss.(prob_neuralode, res)
-#     xs=1:size(true_data)[2]
[…]

### 2023-06-05 Code/_Modular Functions/helperFunctions.jl

@@ -3,7 +3,6 @@ using Graphs
 using DifferentialEquations
 using DiffEqFlux
 using OrdinaryDiffEq
-using Flux
 using Optim
 using SymbolicRegression
 using LinearAlgebra
@@ -24,80 +23,46 @@ end
 
 # Function that takes take vertex embedding, one vertex and returns all distances between that vertex and the k closest vertices
 
-function vertex_distances(M, k)
-    distances = []  # preallocate sizes
-    vertex_norm_distances = []
+# function vertex_distances(M, k)
+#     distances = []  # preallocate sizes
+#     vertex_norm_distances = []
 
-    for i::Int8 in 1:n                                                 # find closest_vertices to v 
-        if i != v
-            distance = norm(M[:,v] - M[:,i], 1)
-            push!(vertex_norm_distances, (distance, i))
+#     for i::Int8 in 1:n                                                 # find closest_vertices to v 
+#         if i != v
+#             distance = norm(M[:,v] - M[:,i], 1)
+#             push!(vertex_norm_distances, (distance, i))
     
-        end 
-    end
+#         end 
+#     end
 
-    closest_vertices_to_v = partialsort(vertex_norm_distances,1:k, by=x->x[1])
+#     closest_vertices_to_v = partialsort(vertex_norm_distances,1:k, by=x->x[1])
 
-    for i in 1:length(closest_vertices_to_v)
-        vertex_index = closest_vertices_to_v[i][2]           
-        for j in 1:size(M)[1]                                          # iterating over all columns in matrix
-            push!(distances, M[j, v] - M[j,vertex_index])
-        end
-    end
+#     for i in 1:length(closest_vertices_to_v)
+#         vertex_index = closest_vertices_to_v[i][2]           
+#         for j in 1:size(M)[1]                                          # iterating over all columns in matrix
+#             push!(distances, M[j, v] - M[j,vertex_index])
+#         end
+#     end
 
-    return closest_vertices_to_v
-end
+#     return closest_vertices_to_v
+# end
 
 
-function vertex_distances_2(M::Matrix, v::T, k::Integer, distance_metric=cosine_dist) where {T<:AbstractArray}
-    cosine_distances = zeros(Float64, size(M)[1])
[…]

### 2023-06-05 Code/_Modular Functions/load2ComGraphFlat.jl

@@ -40,7 +40,7 @@ function loadManualAligned()
 
     n, d = dims
 
-    time_graphs = []
+    time_graphs = Vector{Matrix}(undef, 0)
     for i in 1:length(names)
         temp = CSV.read(string(path, "/step", i, ".csv"), DataFrame, header=false)
         push!(time_graphs, Matrix(temp[:,:]))

### 2023-06-05 Code/_Modular Functions/loadGlobalConstants.jl

@@ -2,28 +2,29 @@ using Revise
 include("load2ComGraphFlat.jl")
 include("../structs/TemporalEmbedding.jl")
 
-function global_consts(n, d)
+function global_consts(n, d; device=Lux.cpu)
     global dims=d #|> Lux.gpu
     global net_name = n
 
 
     global true_data, time_graphs = load2ComGraphFlat(true);
-
-    global t_data = TemporalNetworkEmbedding(true_data,dims[1],dims[2])
+    t_graphs = [Float32.(t) for t in time_graphs]
+    global t_data = TemporalNetworkEmbedding(t_graphs,dims[2])
 
 
     global datasize = 25
-    global train_data = withoutNode(t_data[1:datasize],1) #|> Lux.gpu
+    global train_data = withoutNode(t_data[1:datasize],1) |> device
     global test_data = withoutNode(t_data[1+datasize:end],1)
-    global tspan = (1.0, Float64(datasize))#|> Lux.gpu
-    global tsteps = range(tspan[1], tspan[2], length = datasize)#|> Lux.gpu 
+    global tspan = (Float32(1.0), Float32(datasize))|> device
+    global tsteps = range(tspan[1], tspan[2], length = datasize)|> device
     global k = 15
 
     global input_data_length = k*dims[2]
     global output_data_length = dims[2]
-    global u0 = vec(targetNode(t_data,1)[1])#|> Lux.gpu
+    global u0 = vec(targetNode(t_data,1)[1][:AL])|> device
     return nothing
 end
+
 
 #targetNode(t_data,1)[1]
 # TNode_data = targetNode(t_data,1)

### 2023-06-05 Code/_Modular Functions/loadMITGraphFlat.jl

@@ -1,50 +1,0 @@
-using CSV, DataFrames, LinearAlgebra, Graphs, Tables
-include("../_Modular Functions/helperFunctions.jl")
-
-function loadMITGraphFlat(dims)
-    path = "./Thesis/Code/Graph Series/MIT1"
-    names = readdir(path)
-
-    n, d = dims
-
-    time_graphs = []
-    for i in 1:length(names)
-        temp = CSV.read(string(path, "/time ", i, ".csv"), DataFrame)
-        push!(time_graphs, Matrix(temp[:,:]))
-    end
-
-    true_data = zeros(Float16, d*n, length(names))
-
-    
-
-    for i in 1:length(names)
-        L, R = do_the_rdpg(time_graphs[i], convert(Int, d))
-        true_data[:,i] = reshape([L; R], d*n)
-
-    end
-    return true_data, time_graphs
-end
-
-function loadMITGraphFlat()
-    path = "./Thesis/Code/Graph Series/MIT1"
-    names = readdir(path)
-
-    n, d = dims
-
-    time_graphs = []
-    for i in 1:length(names)
-        temp = CSV.read(string(path, "/time ", i, ".csv"), DataFrame)
-        push!(time_graphs, Matrix(temp[:,:]))
-    end
-
-    true_data = zeros(Float16, d*n, length(names))
-
-    
-
-    for i in 1:length(names)
-        L, R = do_the_rdpg(time_graphs[i], convert(Int, d))
-        true_data[:,i] = reshape([L; R], d*n)
-
-    end
-    return true_data, time_graphs
-end

### 2023-06-05 Code/_Modular Functions/loadRotatingGraphFlat.jl

@@ -1,25 +1,0 @@
-using CSV, DataFrames, LinearAlgebra, Graphs
-include("../_Modular Functions/helperFunctions.jl")
-
-function loadRotatingGraphFlat()
-    path = "./Code/Graph Series/Rotating Edge Graph"
-    names = readdir(path)
-
-    n, d = dims
-
-    time_graphs = []
-    for i in 1:length(names)
-        push!(time_graphs, adjacency_matrix(loadgraph(string(path, "/toy_graph_", i, ".lg"))))
-    end
-
-    true_data = zeros(Float64, d*n, length(names))
-
-    
-
-    for i in 1:length(names)
-        L, R = do_the_rdpg(time_graphs[i], convert(Int64, d))
-        true_data[:,i] = reshape([L; R], d*n)
-
-    end
-    return true_data, time_graphs
-end

### 2023-06-05 Code/_Modular Functions/reconstructRDPG.jl

@@ -1,8 +1,0 @@
-using LinearAlgebra
-function reconstructRDPG(data)
-    # Takes a (2n, d, datasize) tensor and outputs a (n,n,datasize) tensor were
-    # (:,:,i) is RDPG at time i
-    split = Int(dims[1]/2)
-    mult(A) = A[1:split,:]*A[split+1:end,:]'
-    mapslices(mult, data, dims=(1,2))
-end

### 2023-06-05 Code/_Modular Functions/regenerateNetwork.jl

@@ -1,12 +1,0 @@
-using LinearAlgebra
-
-function regenerateNetwork(A)
-    B = reshape(A, (dims[1], dims[2]))
-    mid = convert(Int, dims[1]/2)
-    L = B[1:mid,:]
-    R = B[mid+1:end,:]
-    pred_net = L*R'
-
-    pred_net=pred_net.>0.5
-    return pred_net
-end

### 2023-06-05 Code/_Modular Functions/trainNN.jl

@@ -1,10 +1,0 @@
-
-
-function train(optprob)
-    result_neuralode = Optimization.solve(optprob,
-    ADAM(0.005),
-    callback = callback,
-    maxiters = 100)
-
-    return result_neuralode
-end

### 2023-06-05 Code/structs/TemporalEmbedding.jl

@@ -1,3 +1,5 @@
+using DotProductGraphs
+using Arpack
 """
     TemporalNetworkEmbedding
     A: The raw embedding array dims = [d*n, :]
@@ -7,27 +9,64 @@
 """
 
 struct TemporalNetworkEmbedding
-    A::AbstractArray
+    AL::AbstractArray
+    AR::AbstractArray
     n::Int
     d::Int
 end
 
-@inline function Base.getindex(X::TemporalNetworkEmbedding, t::T) where {T<:AbstractFloat} 
-    X.A[:,:,Int(floor(t))]*(1-t).+X.A[:,:,Int(ceil(t))]*(t) # uses linear interpolation between indices
+@inline function Base.getindex(X::TemporalNetworkEmbedding, t::T, side::Symbol=:AL) where {T<:AbstractFloat} 
+    X[Int(floor(t))][side]*(1-(t-floor(t))).+X[Int(ceil(t))][side]*(t-floor(t)) # uses linear interpolation between indices
 end
 # Base.getindex(X::TemporalNetworkEmbedding, t::T) where {T<:AbstractFloat} = reshape(X.A[:,Int(floor(t))], (X.n,X.d)) # this uses the floor of a float index
-Base.getindex(X::TemporalNetworkEmbedding, t::T) where {T<:Int} = X.A[:,:,t]
+Base.getindex(X::TemporalNetworkEmbedding, t::T) where {T<:Int} = Dict(:AL => X.AL[:,:,t], :AR => X.AR[:,:,t])
+
+Base.getindex(X::TemporalNetworkEmbedding, t::T, side::Symbol) where {T<:Int} = X[t][side]
 
 
-Base.getindex(X::TemporalNetworkEmbedding, t::UnitRange{Int64})=TemporalNetworkEmbedding(X.A[:,:,t], X.n, X.d)
-Base.lastindex(X::TemporalNetworkEmbedding) = size(X.A)[3]
+
+Base.getindex(X::TemporalNetworkEmbedding, t::UnitRange{Int64})=TemporalNetworkEmbedding(X.AL[:,:,t],X.AR[:,:,t], X.n, X.d)
+Base.lastindex(X::TemporalNetworkEmbedding) = size(X.AL)[3]
 not(t::Bool)=!t
-withoutNode(X::TemporalNetworkEmbedding, t::Int) = TemporalNetworkEmbedding(X.A[:,not.(in.(1:X.n, [t])),:], X.n-1, X.d)
[…]

### 2023-06-05 Code/structs/TemporalNetwork.jl

@@ -1,0 +1,3 @@
+struct TemporalNetwork
+    A::AbstractArray
+end

### 2023-06-05 Code/structs/constructRDPG.jl

@@ -1,0 +1,16 @@
+using LinearAlgebra
+
+function constructRDPG(TempNet::TemporalNetworkEmbedding; tsteps=false)
+    # p ∈ s, n, t
+    # pR' = a
+    # round(a)
+    if typeof(tsteps)==Bool
+        tsteps = 1:length(TempNet)
+    end
+
+
+    Ls = [TempNet[t][:AL] for t in tsteps]
+    Rs = [TempNet[t][:AR]' for t in tsteps]
+
+    rdpg = Ls.*Rs
+end

### 2023-06-05 Code/structs/nearestNeighbours.jl

@@ -1,0 +1,12 @@
+function nearestNeighbours(u,t,TempNet, k;side::Symbol=:AL) 
+  """
+  Returns a tuple of the indeces of the neares nodes to u
+  """
+  M = TempNet[t][side]
+  subtract_func(m) = m-u
+  direction_vecs = [subtract_func(m) for m in eachrow(M)]
+  
+  v = collect(enumerate(direction_vecs))
+  println(v)
+  û = [v[1] for v in partialsort(v,1:k, by=x->sum(abs2, x[2]))]
+end

### 2023-06-05 Code/structs/test.jl

@@ -1,0 +1,14 @@
+using DotProductGraphs
+
+include("allignment.jl")
+include("nearestNeighbours.jl")
+include("constructRDPG.jl")
+include("TemporalEmbedding.jl")
+
+adj = [[0 1 1; 0 0 1; 1 0 0], [1 1 1; 0 1 1; 1 0 0], [0 1 1; 0 1 1; 1 1 0]]
+
+TemporalNetworkEmbedding(AL=[1 2; 3 4], AR=[5 6; 7 8], n=2, d=2)
+t = TemporalNetworkEmbedding(adj, 2)
+
+t.AL
+targetNode(t,3).AL

### 2023-06-05 Code/PlottingCode/plotSltn.jl
2d long tail plots

@@ -4,7 +4,7 @@ using Lux
 include("../_Modular Functions/loadGlobalConstants.jl")
 
 include("../_Modular Functions/pca.jl")
-global_consts("2communities", (182,2))
+global_consts("longTail", (182,2))
 
 include("symreg.jl")
 p1, p2 = (1,2)

### 2023-06-05 Conference Submission/DraftDoc.tex
Includes 2d long tail plots

--- 2023-05-15 Conference Submission/DraftDoc.tex
@@
 \begin{section}{Introduction}
+    Temporal networks are networks whose nodes and edges change in time. In this thesis we look to model temporal networks. That is, describe the temporal network using mathematical language. 
+    % Why temp nets are important
     The modelling of temporal networks is an important task in many real world applications including symptom interactions for mental health \cite{jordan2020current,contreras2020temporal}, epidemiology \cite{masuda2013predicting}, and protein interactions \cite{lucas2021inferring,jin2009identifying}.
-    Temporal networks can be seen as dynamical systems: that is a system in which we have points, in our case nodes in a network, whose states, the edges connecting them, that vary dependent in time.
-    Discovering the underlying equations governing these dynamical systems proves challenging, because changes in network structure are typically observed in the form of discrete jumps from one state to another, for example an edge between two nodes not being observed at the first time step then appearing at the next.
-    Here, we propose a hybrid statistical and deep learning framework that allows us to model temporal networks as continuous-time dynamical systems, discover a fitting set of differential equations describing it, and, exploiting that discovery, predict the time evolution of a network.
 
+    % Temp nets are dynam systs
+    Temporal networks can be seen as a system in which points, in our case nodes in a network, whose states, the edges connecting them, that vary dependent in time, a dynamical system.
+
+    % Hard to find dynam systs because of discrete events 
+    Discovering the underlying equations governing these dynamical systems proves challenging.
+That is because changes in network structure are typically observed in the form of discrete jumps from one state to another, for example an edge between two nodes not being observed at the first time step then being observed at the next.
+
+    % We are proposing a solution
+    In this thesis, we propose a hybrid statistical and deep learning framework.
+That is a framework in which a neural network is used to model probabilistic values of the temporal network.
+This framework allows us to model temporal networks as continuous-time dynamical systems, discover a fitting set of differential equations describing it, and, exploiting that discovery, predict the time evolution of a network.
+
+    % DEs are useful for modelling interacting states
     Differential equations are useful for modelling systems where the state of one variable can effect the trajectories of other variables.
-We observe this behavior in temporal networks; nodes' connections within the network can influence the formation and decay of edges between other nodes, for example the phenomenon of preferential attachment observed in \cite{newman2001clustering,capocci2006preferential}, where a node is more lively to gain the connections the more connections it has.
+
+    % Temp nets have interacting states 
+    We observe this behavior in temporal networks; nodes' connections within the network can influence the observation of edges between other nodes, for example the phenomenon observed in \cite{newman2001clustering,capocci2006preferential}, where a node is more likely to gain the connections the more connections it has (preferential attachment).
 With this in mind we might wish to draw on the rich mathematical literature of differential equation modelling.
 
-    In the common representation of networks as binary-valued adjacency matrices, the events recorded in a temporal sequence of networks correspond to topological events, such as the appearance or the disappearance of link.
+    % Temp net events are discrete
+    In the common representation of networks as binary-valued adjacency matrices, matrices where the observation, or lack thereof, of an edge is represented as a 1 or 0 respectively, the events recorded in a temporal sequence of networks correspond to the appearance or the disappearance of link.
+
+    % Difficult to model discrete events
     Because of the discrete nature of events, directly modelling the temporal networks as dynamical systems would require us to handle discrete jumps.
@@
 
-    Here, we overcome the discreteness problem by interpreting networks as Random Dot Product Graphs; a well established statistical model for complex networks, that embeds nodes in a continuous, low-dimensional metric space by using a truncated singular value decomposition\cite{athreya2017statistical}.
+    % We propose a solution
+    Here, we overcome the discreteness problem by interpreting networks as a well established statistical model for complex networks, that embeds nodes in a continuous, low-dimensional metric space by using a truncated singular value decomposition (Random Dot Product Graphs\cite{athreya2017statistical}).
 In this way we translate the hard problem of modelling discrete events in the space of networks to the easier problem of modelling continuous change in the embedding space.
+
+    % Our solution is interpretable because we use symb reg
     We then define and use systems of Neural Network Differential Equations (NNDE)\cite{SciML_C_Rak} to approximate the time evolution of the embedding space, and symbolic regression techniques to discover the functional form of the fitted NNDEs.
@@
 
-    In this manuscript, we prove that the temporal network prediction problem can be successfully re-interpreted as a dynamical system modelling problem by taking the singular value decomposition of a sequence of adjacency matrices and training a NNDE to model an approximation to the underlying differential equation.
+    % We propose a solution
+    In this manuscript, we show that the temporal network prediction problem can be successfully re-interpreted as a dynamical system modelling problem by taking the singular value decomposition of a sequence of adjacency matrices and training a NNDE to model an approximation to the underlying differential equation.
 We then go on to create a symbolic equation of this approximation.
 
+    % We will do some small tests on the proposed framework
     We apply our proposed framework to three small example temporal networks with the hope of exploring the limitations and strengths of the proposed framework.
+
+    % The framework can and should be tweaked to make it optimised
     The framework we are introducing is extremely flexible, and our research regarding the optimal structure of the Neural Networks used for the NNDEs is just started.
@@
     For this reason, we did not yet attempt to benchmark our model against other classic temporal network prediction methods.
+
+    % The framework can be applied to lots of fields
     As it is completely general, we believe that the framework we are introducing can be usefully applied to areas of medicine, especially protein interaction networks; population dynamics for network ecology; and social network modelling.
@@
 
+\begin{section}{Literature Review}
+
+    \subsection{Temporal Networks}
+        % Use of temp nets
+        Temporal networks are used to describe a series of interactions across time.
+        A temporal network $G$ is defined as:  
+        \begin{align}
+            G=\{ {_t} G=({_t} N, {_t} E)\} _{t \in 1\ldots T } 
+        \end{align}
+        $_t x \in {_t} N, {_t} e\in {_t} E$, where ${_t} x, {_t} e$ are nodes and edges at time $t$ respectively, and ${_t} N, {_t} E$ are the sets of nodes and edges at time $t$ respectively.
+        An example of this can be found in \autoref{method nets}.
+
+        %representations of temp nets as adj lists
+        This can be represented in many ways, for example as a series of interactions.
+The series of interactions is generally represented as a list of tuples containing the node that interacted and the time that the interaction took place.
+        \begin{align}
+            G=\{(i, j, t)|\space i,j\in {_t} N, (i\leftrightarrow j)\in {_t}E \}
+        \end{align}
+
+        % representation of temp nets as adj mats
+        A temporal network can also be represented as a sequence of adjacency matrices.
+In the representation of a series of adjacency matrices, the columns and rows of the matrix each refer to each of the nodes.
+In this way, if an edge exists between nodes $i$ and $j$, the entry $(i,j)$ of the adjacency matrix will be 1; if an edge does not exist the entry will be 0.
+        \begin{align}
+            _t G &= {_t} A\\
+            _t A_{ij} &=  
+            \left\{
+                \begin{array}{ll} 
+                1 & (i\leftrightarrow j)\in {_t} E\\
+                0 & otherwise
+                \end{array}
+            \right.
+        \end{align}
+        The row $_t A_{i\cdot}$ describes the outgoing edges of the node $i$, while the column $_t A_{\cdot j}$ describes the incoming edges of the node $j$.
+
+        % Uses of temp nets
+        Temporal networks are present in many areas of research interest, ranging from symptom interactions in mental health\cite{jordan2020current,contreras2020temporal}, to epidemiology\cite{masuda2013predicting}, protein interactions\cite{lucas2021inferring,jin2009identifying}, and social networks\cite{moinet2015burstiness,hanneke2010discrete}.
+
+        % Overview of modelling attempts
+        Generally attempts to model temporal networks either model the change in node state or the change in network structure.
+
+        The node state describes some information about that node:
+        \begin{align}
+            _t x &= (m_1,\ldots, m_p)
+        \end{align}
+        Where $m_i$ is some metadata about the node $_t x$.
+
+        An example of modelling the change in a node state could be the severity of a symptom at a given time, as in \Citeauthor{contreras2020temporal}\cite{contreras2020temporal}.
+Where the node $_t x$ represents the symptom and $m_1$ would represent the severity of that symptom.
+
+        Other effort focus on modelling the changing structure of the network as in \Citeauthor{sanna2021link}\cite{sanna2021link}, which looks to model $_t G$ as a whole.
+
+        % Intro contreras as attempt to model changes in nodes
+        \Citeauthor{contreras2020temporal}\cite{contreras2020temporal} model the change in node state over time while the structure of the network remains constant.
+\Citeauthor{contreras2020temporal} look at the severity of symptoms over time, i.e.
+the state of the nodes, as a temporal network where the network structure remains constant.
+
+        % Contreras methods
+        They use multilevel vector autoregression, a method that finds correlations between the current state of a variable and the states of variables at previous time steps \cite{singer2003applied}, to model how the current symptoms of people with paranoia might predict their future symptoms.
+These models were then used to create three networks that linked symptoms.
+
+        % Focal point of the paper is their temporal network
+        Of particular interest to this thesis is the temporal network created by having a fully connected network of all symptoms including self-loops, where a symptom connects to itself; this self loop comes about from a symptom being correlated with itself from one time step to the next.
+The edge weights represent the extent to which the severity of each symptom at time $(t)$ predicts the severity of itself and other symptoms at time $(t+1)$.
+
+        % Why this is the focal point
+        This framework keeps the overall structure of the network fixed throughout time and so is not particularly flexible, but is extremely human interpretable and can be used to extrapolate and predict into the future.
+
+        % intro to paper as attempt to model node state
+        In \cite{KARIMI20133476}, the \Citeauthor{KARIMI20133476} look to model the change in node state while the network structure changes.
+
+        % How network is represented
+        \Citeauthor{KARIMI20133476} represent their temporal network as a series of interactions (a list of tuples in the form $(i,j,t)$, where $i,j$ are the nodes interacting and $t$ is the time the at which the interaction occurred).
+
+        % what state the paper attempts to model
+        The authors use a model to predict when a node will change from state 0 to state 1, in practice this could represent whether a user of a social network believes a rumour, or an ecological patch being colonised.
+
+        % Model limitation
+        Notably, in their model the node never changes back; this is done to keep the model analytically tractable, but does limit its usefulness in some contexts.
+In this model an organism could not become locally extinct in an ecological patch for example.
+
+        % Methods to model node state
+        To model the change in a nodes' state, the model uses a sliding time window and if the fraction of interactions with nodes of state 1 within that time window exceeds a given threshold, the node switches to state 1 as well.
+
+        % Limitation of model
+        In this work I aim to present a model for predicting the state of a node in the future.
+Instead, \Citeauthor{KARIMI20133476} aim to present a tool for understanding the spread of ideas, viruses, etc.
+within a network.
+
+        % Intro to pasino et al as modelling structure of temp net
+        \Citeauthor{sanna2021link}\cite{sanna2021link} model the change in the structure of a temporal network.
+
+        % temp net representation
+        In this case the \Citeauthor{sanna2021link} represent the temporal network as a series of adjacency matrices, each matrix representing an observation of the changing network.
+
+        % Methods for embedding
+        The authors look to model the structure of edges by using a spectral embedding (SVD).
+A spectral embedding uses the eigenvectors of a network's adjacency matrix to find vectors that represent the nodes of the network.
+The spectral embedding transforms their temporal sequence into a sequence of observations of a latent space.
+
+        % What is a latent space
+        A latent space is a continuous space in which similar nodes (nodes with many of the same neighbours) are positioned near each other.
+In this space nodes are represented as points in a continuous, low dimensional space.
+Another feature of this latent space, is that the dot product of any two points in the space gives us the probability that the nodes related to those points are connected.
+
+        % methods for time series
+        With this series of embeddings, the authors employ a variety of time series techniques to predict the network structure at future time steps.
+
+    \subsection{UDEs and NNDEs}
+        % Justification for DEs being useful
+        In some temporal networks the state of a node might influence the evolution of its neighbours.
+For example, in social networks we often observe the power law distribution of edges, where the more neighbours a node has, the more likely they are to gain more neighbours\cite{zhao2012multi,garg2009evolution}.
+We also see that the state of symptoms (occurrence, severity, and distress), can influence the states of other symptoms in patients undergoing chemotherapy \cite{papachristou2019network,kalantari2022network}, and for mental health disorders \cite{contreras2020temporal}.
+As well as in ecological networks where the interactions of species are often represented as a network, and the populations of one species may influence the population growth of another \cite{elton2001animal,volterra1927variazioni}; that is, the state (in this case the population) of a species (node), may influence the movement of another species.
+
+        % DEs have lots of research
+        With the observation that nodes in real world temporal networks may influence others, differential equations or difference equations seem appropriate for modelling the evolution of nodes as there is a rich body of literature exploring these methods use in modelling interacting variables.
+
+        % The data we have is discrete, which is a problem for DEs
+        One of the issues that the differential equation method encounters is the prevalence of discrete jumps of edges forming and decaying.
+Because of this we may consider exploring the possibility of using difference equations.
+
+        % time is continuous so good to have our model be cont too
+        We note that the progression of the network is generally continuous even if the events happen as discrete jumps.
+Because of this, we may wish to preserve the continuous temporal progression in our model.
+
+        %This approach may overcome the problem of discrete observations, by defining a progression function that will only predict discrete formation or decay of edges\cite{hanneke2010discrete}.
+However, this imposes a significant limitation on the temporal granularity with which we can predict the state of the network.
+We would be limited to the granularity our data is collected at.
+This may be a problem if for example we had a series of weekly or monthly observations of networks we would not be able to predict interactions at each day.
+We can overcome both this limitation and the discrete jump limitation by using random dot product graphs.
+Interpolation may be possible in this case, but we would have no way of knowing if the interpolation had any basis in the real world.
+
+        % passino has discrete data but uses a method to view it as cont
+        Looking at the work of Passino et al.\cite{sanna2021link}, the authors use random dot produce graphs\cite{athreya2017statistical} to approximate a temporal network as a matrix of probabilities of an edge existing between two nodes.
+In contrast to edges, these probabilities can evolve continuously, and so we can use differential equations to generate probabilistic networks at any temporal resolution we require.
+That is, we will be able to model the changes in the probabilities of edges continuous and from this, generate a network at any time step.
+
+        %  we can use the same method we can view data as dynam sys and use DEs
+        Using the method in Passino et al.\cite{sanna2021link}, we can treat the sequence of embeddings as a dynamical system and then use differential equation modelling in a continuous space.
+That is, once we have found a latent space for each network.
+We know that each point in this space refers to a specific node in the network, and so, as the network changes, so too does the position of each of the points in the latent space.
+We then look to model this movement using differential equations.
+
+        % Can use a new NN structure to make this framework very general
+        Our aim for this framework to be as general as possible and note that there may not yet be enough domain knowledge to perform traditional differential equation modelling to the desired accuracy.
+For example in network ecology models can be useful, but not perfect XXX cite XXX.
+Hence, we might wish to build on these models rather than trying to create something entirely new.
+This can be achieved by using this partial domain knowledge using it to create a universal differential equation (UDE) \cite{SciML_C_Rak}.
+
+        \subsubsection{Theory}
+
+            % Overview of why UDEs are useful
+            Developed by \Citeauthor{SciML_C_Rak}\cite{SciML_C_Rak}, Universal Iifferential Equation (UDEs) are a novel neural network architecture that aims to take the best of both traditional neural differential equation modelling and of flexible machine learning approaches to modelling.
+
+            If we consider a comparison to an Ordinary Differential Equation (ODE), the ODE is written as:
+            \begin{align}
+                y(0) &= y_0 \\
+                \frac{dy}{dt}(t)&=f(t,y(t))
+            \end{align}
+
+            The UDE will incorporate some component of $f(t,y(t))\approx \hat f(t,y(t))$, and will learn the difference with a Neural Network (NN) such that:
+            \begin{align}
+                \label{UDE}
+                y(0) &= y_0 \\
+                \frac{dy}{dt}(t)&=\hat f(t,y(t))+NN(t,y(t), \theta)
+            \end{align}
+            Where $\theta$ is a vector of the parameters of the NN.
+            % Structure of UDE
+            UDEs combine domain knowledge in the form of a differential equation, with a neural network. This hybrid machine learning model is then trained on the observed data.
+
+            % Overview of why UDEs are useful
+            Combining the two allows for most of the movement in the data to be captured by the differential equation, which contains the domain knowledge.
+In this way the neural network will only need to learn a theoretically simpler equation, given that a part of the system has already been captured.
+
+            % Why this structure is useful
+            This then allows the neural network to be smaller, require fewer data, and be trained much faster than traditional neural network models.
+Given the flexibility of neural networks, the use of UDEs is natural when modelling a process that is not entirely understood\cite{kidger2022neural}.
+
+            % Software used for coding
+            There is an ecosystem of packages specifically designed for performing machine learning with UDEs.
+The ecosystem is called SciML or scientific machine learning\cite{SciML_C_Rak}.
+Largely, the SciML ecosystem has been optimised for flexibility and efficiency with respect to models available and training performance.
+Given there does not seem to be any other ecosystem with this feature, it seemed like
+            an obvious choice.
+
+        \subsubsection{Applications}
+            Whilst there has been much interest in implementing UDEs and neural ODEs, much of this work has been focussed on physics informed neural network and physics informed ordinary differential equations (PINNs and PINODEs) \cite{karniadakis2021physics,GAO2021110079,krishnapriyan2021characterizing,roehrl2020modeling}, and on improving modelling of fluids \cite{mahmoudabadbozchelou2021data,nguyen2022physics}.
+Alongside this, and given UDEs have gained popularity in the last few years, there have been a number of studies exploring their usefulness in modeling the effect of restrictions due to COVID-19 on the virus' spread \cite{Dandekar2020.04.03.20052084}.
+Although there has been a large amount of research into the usefulness of these types of models, to the best of this author's knowledge they have never been applied to the problem of predicting temporal networks.
+This seems to be a natural fit for UDEs and neural ODEs, given we may know relatively little about the processes that govern the evolution of temporal networks, and any information we do have can be incorporated into the model.
+
+    \subsection{Symbolic Regression}
+        % What is symbolic regression
+        Symbolic regression is a type of analysis that looks to find a relationship between input variables that describe the output variables.
+For symbolic regression, we define a set of equations that may be used to find this relationship.
+The algorithm then generates combinations of these equations to find an expression that matches the output variables.
+Because we define the set of potential equations, the resulting expression is interpretable by humans, as opposed to a NN for example.
+
+        % Why is symbolic regression useful
+        Having interpretable models that capture underlying relations is relevant to all fields of study, and so the applications of symbolic regression are incredibly varied.
+
+        % Where has symbolic regression been used 
+        Various methods of symbolic regression have been use in manufacturing systems, chemical systems, and tumor research\cite{can2011comparison,keith2021combining,yoshihara2013inferring}.
+As well research into improvements is still on going.
+
+        % How is this done
+        This can be achieved in many ways and remains active area of research. One of the most popular algorithms is genetic programming\cite{schmidt2009distilling}.
+
+        % How genetic programming works
+        Genetic programming involves constructing a search tree using a genetic algorithm to yield a potential equation, which may match the data as well as numerically calculated partial derivatives of each of the input variables.
+
+        % Why are the derivatives important
+        Comparing with these derivatives is useful as it helps to ensure that the produced function equations have some grounding in the real world process that generated the data.
+The search tree is then pruned by comparing the partial derivatives of the candidate equation, with partial derivatives calculated from data.
+This process is then iterated many times to generate a suitable equation.
+
+        % What symbolic regression aims to solve
+        The problem that symbolic regression aims to solve is to generate interpretable and ``meaningful'' equations from observed data.
+
+        % Examples of use of genetic programming
+        For example, both \Citeauthor{schmidt2009distilling,bongard2007automated} test their methods' capacity for obtaining a symbolic equation with physical simulation data, various pendula specifically.
+A ``meaningful'' equation in this case would be one that adheres to the laws of physics.
+
+        % Expalaination of schmidt
+        Examples of genetic programming include discovering equations governing the movement of simple harmonic and chaotic double pendula from data\cite{schmidt2009distilling}.
+In this paper the authors present an evolutionary algorithm to generate multiple candidate functions that approximate the partial derivatives of each variable that are calculated directly from the data.
+
+        % Intro to bongard
+        Another approach to symbolic regression can be found in \cite{bongard2007automated}.
+This paper proposes a method to find a symbolic equation that approximates a learned numerical equation rather than directly from data.
+
+        % How does this process work
+        The candidate equation is then tested against the numerical equation in such a way that the difference between the two predictions are maximised.
+The algorithm will generate new initial conditions to find behaviour exhibited by the numerical equation, for example a fixed point, that is not exhibited by the functional equation.
+When a difference is found, the functional equation is adjusted to also exhibit the behaviour of the numerical equation.
+
+        % Limitations of this process
+        Especially when using a neural network model as the numerical equation, it seems these process may not be useful if the initial conditions are outside the scope of the training data.
+
+        % Benefits of combining UDEs and symbolic regression
+        In very recent work, Kidger\cite{kidger2022neural}, demonstrates that, with UDEs, two of the assumptions necessary for symbolic regression can be overcome.
+Those are the necessity for paired observations and derivatives, as well as the assumption that the function can be expressed as a shallow tree of symbolic operations.
+We are modelling a differential equation, and so will have access to the derivatives of our numerical model at any point, as neural networks are easily differentiable.
+
+        % Usefulness of symbolic regression for nnde
+        In \Citeauthor{SciML_C_Rak}\cite{SciML_C_Rak}, the authors demonstrate that using symbolic regression, as opposed to just an NNDE, can improve the accuracy of extrapolating.
+One aspect of this improvement is having accurate numerical derivative to compare to.
+To ensure this, it is important that the data is sampled very frequently.
+This seems integral to the accuracy of the found equation.
+\end{section}
+
 \begin{section}{Methodology}
 
+        % Goal is to predict next time steps
         We are given a sequence of graphs, and our goal is to predict the next graph in the sequence.
+
+        % How we achieve this goal
         To achieve this, we reinterpret each graph as a sequence of points in a latent space; that is, a space in which similar vertices (ones with many of the same neighbours) are mapped to a similar point in space.
@@
             \label{svd}
+            % Over view of section
             In this section we discuss the Singular Value Decomposition (SVD) of a matrix, and its usefulness in creating Random Dot Product Graphs (RDPG).
 
+            % Definition of SVD
             We define the matrix $A$ to be a real $m \times n$ with $n \le m$. $A$ can be expressed as \cite{forsythe1967computer}:
             \begin{align}
-                A&=L\Sigma R'
+                A&=l\sqrt{\Sigma} \sqrt{\Sigma} r' \\
+                A&=L R'
             \end{align}
@@
 
-            In order to reduce the problem size, we can truncate the $L,R,\Sigma$ to the first $d$ columns to yield, $\hat L, \hat R, \hat \Sigma$ such that:
+            % How to reduce problem size
+            In order to reduce the problem size, we can truncate the $L,R$ to the first $d$ columns to yield, $\hat L, \hat R$ such that:
 
             \begin{align}
-                A &\approx \hat L \hat \Sigma \hat R' \\
-                \hat A &= \hat L \hat \Sigma \hat R'
+                A &\approx \hat L \hat R' \\
+                \hat A &= \hat L \hat R'
                 \label{approx}
@@
 
-            The approximation of $A$ is defined as $\hat A$ and is given by \autoref{approx} can be interpreted as a graph where the entry $(i,j)$ of the matrix is the probability that an edge exists from $i \rightarrow j$.
-This approximation of $A$ is known as an RDPG.
+            % Supposed to be how to interpret this as RDPG but is bad
+            The approximation of $A$ is defined as $\hat A$ and is given by \autoref{approx} can be interpreted as a graph where the entry $(i,j)$ of the matrix is the probability that an edge $(i \leftrightarrow j)$ exists.
+This approximation of $A$ is an RDPG\cite{athreya2017statistical}.
 
+            % Introduce problem of alignment
             It is important to note that the SVD is not unique.
 The distances between points will be the same for every embedding, but the orientation may be different, and so, if the SVD of each time step is not aligned, learning will be effectively impossible as we will essentially be trying to model random noise.
-Here, we can use Procrustes alignment XXX cite package XXX to align the matrices after they have been generated.
 
-            The SVD gives is an RDPG\cite{athreya2017statistical}.
+            % How to solve alignment problem
+            Here, we can use Procrustes alignment\cite{DotProductGraphs} to align the matrices after they have been generated.
+
+            % SVD can give a latent space embedding
             The SVD can be considered to give a latent space representation of the matrix\cite{hoff2002latent}.
-That is, the rows of the matrices $L,R$ can be viewed as vector points in a $d$-dimensional space, where $d$ is the number of singular values we take for our SVD truncation.
-In this space similar nodes in the network are mapped to similar points.
+That is, the rows of the matrices $\hat L,\hat R$ can be viewed as vector points in a $d$-dimensional space, where $d$ is the number of singular values we take for our SVD truncation.
+In this space similar nodes in the network are mapped to similar points in space.
 A visual representation of this process can be seen in \autoref{framework illustration}.
 
+            % Explicit process for how we process our data
             When obtaining the RDPGs for our temporal network, we take each network observation \autoref{method nets} and represent them in the form of an adjacency matrix \autoref{method adjacency}.
 We then use a truncated singular value decomposition to reduce the dimensionality of our adjacency matrices\cite{golub1971singular}.
+
+            % Introduce problem of loss from SVD
             This truncation introduces some loss, but can dramatically reduce the size of our problem.
@@
 
+            % What code we use
             To execute the SVD we use the ARPACK Julia package \cite{lehoucq1998arpack}.
@@
 That is, with some input data, point location, distance to neighbours, etc, we want to model the differential equation that governs the movement of a point.
+        % Modelling multiple points
         Notably this method can be used to model multiple points by simply changing the node being predicted and trained on.
 
-        Our problem can be defined as:
+        From \autoref{UDE} our problem can be represented as the UDE:
         \begin{align}
-            A_{t+1} = f(A(t),t)
+            \frac{d \hat A}{dt} &= \hat f(t,\hat A(t)) + NN(t, \hat A, \theta)
         \end{align}
-        Where $A_t$ is the adjacency matrix of the temporal network at time $t$.
-By using the SVD to obtain the approximation $\hat A_t$, which can evolve continuously, we can reinterpret our problem as:
+        The focus of this thesis is to understand the behaviour of the neural network when modelling temporal neural networks.
+Hence, we set $\hat f(t, \hat A(t))=0 \space \forall t$.
+With this, the problem becomes:
+        \begin{align}
+            \frac{d \hat A}{dt} &= NN(t, \hat A, \theta)
+        \end{align}
+        A special case of a UDE called a Neural Network Differential Equation(NNDE).
+
+        In this thesis, as a proof of concept, we focus on a modelling the change in structure of a single node, referred to as the target node $u$, where $u(t)={_t}\hat L_{1\cdot}$.
+To model $u$ we use the direction vectors from $u$ to its $k$ (15) nearest neighbours in $\hat L$.
+We define the function $K(\hat L(t), k)$ to find the direction vectors of the $k$ nearest neighbours to $u(t)$.
+We use the function $K$ to limit the complexity of our model.
 
         \begin{align}
-            \frac{d\hat A}{dt} &= g(\hat A(t), t)
-        \end{align}
-
-        In this thesis, as a proof of concept, we focus on a modelling the change in structure of a single node, referred to as the target node $u$. In this case, the form of the problem becomes:
-
-        \begin{align}
-            \frac{du}{dt} &= g(u(t), t)
+            \frac{du}{dt} &= NN(t, K(\hat L, k), \theta)
         \end{align}
@@
 
-        To obtain this differential equation we make use of the SciML ecosystem of packages in the Julia programming language \cite{SciML_C_Rak}.
-
-        % KNN Explaination
-        As a way of limiting the complexity of our model, we limit the input of the neural network to the euclidean distances between the target node and its $k$ nearest neighbours.
-The target node is the node that we are looking to model the movement of and stays the same throughout each of the temporal networks.
-        % \begin{align}
-    %     %\centering
-    %     \mathbb{P}(i\rightarrow j)&\coloneqq L_i \cdot R_j\\
-    %     \mathbb{P}(\hat{i}\rightarrow j)&\coloneqq L_{\hat{i}} \cdot R_j
-    % \end{align}
-    % Where $(i,j)$ are nodes in the network and $\hat{i}$ is another node at the same timestep to $i$. This implies that the distance between these two nodes with respect to node $j$ is given by
-    % \begin{equation}
-    %     \begin{gathered}
-    %         %\centering
-    %         ||\mathbb{P}(i\rightarrow j)-\mathbb{P}(\hat{i}\rightarrow j)||_2 = 
-    %         ||L_i \cdot R_j-L_{\hat{i}} \cdot R_j||_2\\
-    %         =||(L_i -L_{\hat{i}}) \cdot R_j||_2
-    %     \end{gathered}
-    % \end{equation}
-    % If we look at the expectation of this, we see
-    % \begin{equation}
-    %     \begin{gathered}
-    %         %\centering
-    %         \mathbb{E}_j(||(L_i -L_{\hat{i}}) \cdot R_j||_2) = ||(L_i -L_{\hat{i}}) \cdot \frac{1}{k}\sum_{j\ne i}R_j||_2
-    %     \end{gathered}
-    % \end{equation}
-    % Where $k$ is the number of neighbours we chose for the neural network input. Because the distance between points is described by the euclidean distance, we use this as our loss metric.
+        To obtain a suitable set of parameters $\theta$, we make use of the SciML ecosystem of packages in the Julia programming language\cite{SciML_C_Rak}.
 
     % Symbolic Regression Explaination
+
     \subsection{Symbolic Regression}
-        With our trained NODE, we have a black box that approximates the system that governs the movement of the target node in the embedded space.
-To make this more interpretable we then look to approximate this black box into a combination of known functions using symbolic regression\cite{pysr}.
+        With our trained NNDE, we have a black box that approximates the system that governs the movement of the target node in the embedded space.
+To make this more interpretable.
+We then look to approximate this black box into a combination of known functions using symbolic regression\cite{pysr}.
 
-        Symbolic regression is a type of regression analysis that searches a space of equations to find an expression that matches data.
-We use the genetic programming algorithm found in \cite{pysr}.
-The process for which can be seen in \autoref{symbreg}.
+        We use the genetic programming algorithm found in \cite{pysr}. The process for which can be seen in \autoref{symbreg}.
 
@@
         For this process we need to define a set of functions which the algorithm will use to generate a tree of functions to find the best approximation to our NNDE with.
-When using this method we are usually required to make two assumptions: that we have paired observations of $y(t), \frac{dy}{dt}$, and that the tree of expressions we will need is shallow.
+When using this method we are usually required to make two assumptions: that we have paired observations of $u(t), \frac{du}{dt}$, and that the tree of expressions we will need is shallow.
 We will train the symbolic regression on the predictions of the neural network.
@@
     \subsection{Reconstructing the Temporal Network}
-        To recover a final prediction, the point vector of the target node with the matrix $R'$, this gives a vector of probabilities of connections between the target node and the rest of the network.
+        To recover a final prediction of the edges of $u$, we multiply the point vector of $u$ with the matrix $R'$.
+This gives a vector of probabilities of connections between the target node and the rest of the network.
 As the results can be interpreted as a probability, the most likely graph is given by setting any entry with a value of $0.5$ or higher to one (predict that the edge exists), and setting any entry with a value of less than $0.5$ to zero (predict that an edge does not exist).
@@
 \begin{section}{Results and Discussion}
-    \subsection{Network Prediction}
-    To compare our models, we look at the loss of the predictions. This includes the loss from the SVD.
+    \subsection{Embedding Prediction}
+        For each of these systems, we took embedded the temporal network in two dimensions at each time step.
+The temporal embeddings were then divided into a training set of 20 and a testing set of 15.
+The output of the trained neural networks was then used to train a symbolic regression model that could use a simple set of addition, subtraction, division, and multiplication.
 
-    To find the approximation of the edges of node $i$, $_tA_{i,\cdot}$. We use: 
+        We predicted the evolution of the 2 community, long tail, and 3 community systems for 15 time steps after the training period using both a NNDE model and a symbolic regression model.
+
+        To compare our models, we look at the distance of the predictions to the embedding of the target node.
+Note that this does not include the loss from the SVD, which con be reduced by increasing the number of singular values taken in for the SVD.
+
+        To find the predicted probability of the edges of node $i$, $\mathbb{P}(i \leftrightarrow j:j\in V\smallsetminus \{i\})$, we use: 
         \begin{align}
-        _tA_{i,\cdot} &\approxeq (\bar p) _t\hat A
+            _tA_{i,\cdot} &\approxeq (\bar p) _t\hat R
         \end{align}
-    Where $\bar p$ is the location of the node $i$ in the embedding at time $t$.
+        Where $\bar p$ is the predicted location of the target node $i$ in the embedding at time $t$.
 
@@
         \begin{align}
-        L = ||_tA_{i,\cdot} - (\bar p) _t\hat A||_1
+            \bar j &= V \smallsetminus \{i\}  \\
+            L &= \frac{1}{||\bar j||}\sum{(_t\hat A_{i,\cdot} \hat R_{\cdot,\bar j} - (\bar p) _t\hat R_{\cdot,\bar j})^2}
         \end{align}
+        That is the mean squared error between the probabilities given by the true embedding and the prediction.
 
@@
             \begin{center}
-            \begin{tabular}{| m{0.17\textwidth} | m{0.25\textwidth} | m{0.25\textwidth} | m{0.25\textwidth} |}
+                \begin{tabular}{| m{0.17\textwidth} | m{0.25\textwidth} | m{0.25\textwidth} |}
                     \hline
-                Sequence & Embedding Loss & Neural Network Prediction Loss & Symbolic Regression Prediction Loss\\ 
+                    Sequence & Neural Network Prediction Loss & Symbolic Regression Prediction Loss\\ 
                     \hline
                     \hline
-                2 Community & 41.67 & 47.91 & 35.11\\ 
+                    2 Community & 5.784 & 10.16\\ 
                     \hline 
-                Long Tail & 2.408 & 1.193 & 2.524 \\ 
+                    Long Tail  & 3.858 & 0.057 \\ 
                     \hline 
-                3 Community & 35.43 & 35.50 & 35.57 \\ 
+                    3 Community & 6.597 & 2.047 \\ 
                     \hline 
@@
                 \end{center}
-            \caption{A summary of the mean loss of each prediction at the fifth time step.
-The embedding loss comes from the true target node and loss is only introduced by the SVD.
+                \caption{A summary of the mean loss of the predictions at the fifth to ninth time steps.
 The neural network and symbolic prediction loss comes from the RDPG being reconstructed but with the position of the target node replaced with the location of the respective prediction.
-Loss is calculated as the total number of incorrectly predicted edges.
-That is an edge not being present when it should as well as the reverse.}
+Loss is calculated as the mean squared error between the prediction predicted edge probability and the edge probability of the embedding.}
                 \label{loss_table}
         \end{figure}
+
+        As can be seen in \autoref{loss_table}, the symbolic regression model performed better for both the long tail system and the 3 community system.
+However, for the 2 community system the symbolic regression model performed notably worse.
 
@@
 
-    For each of these systems, we took embedded the temporal network in two dimensions at each time step.
-The temporal embeddings were then divided into a training set of 20 and a testing set of 15.
-The output of the trained neural networks was then used to train a symbolic regression model that could use a simple set of addition, subtraction, division, and multiplication.
-\\
-    In fig \autoref{2community series}, \autoref{longtail series},\autoref{3community series} the green points are the embedded coordinates of the node in each of the communities.
+    \subsection{Further Exploration}
+        In fig \autoref{2community series}, \autoref{longtail series},\autoref{3community series} the purple points are the embedded coordinates of the node in each of the communities.
 Each cluster is one separate community.
-The orange point is the true coordinate of the embedded target node at each time step.
-The blue point is our model prediction from the true target node at the first time step.
+The green point is the true coordinate of the embedded target node at each time step.
+The blue point is our neural network model prediction at each time step.
+The orange point is the symbolic regression prediction.
+
+        To illustrate how the changing structure of the network is represented in the embedding, we give a brief description of the movement of the target node throughout the 2 community system below.
+
         As the time progresses, we see the true node move from one community cluster to the other.
-This is expected from the embedding; the target node starts as very similar to the first community (as it has many connections with nodes in that community) and as time progresses, it gradually becomes less and less similar to the first community and more similar to the second (as the edges between the target node and the first community are replaced with edges to the second community).
-As such, we see the target node move towards the second community.
+This is because, at the beginning of the training phase, the target node starts as very similar to the first community (as it has many connections with nodes in that community) and as time progresses, it gradually becomes less and less similar to the first community and more similar to the second (as the edges between the target node and the first community are replaced with edges to the second community).
+Because the SVD embeds nodes with many of the same connections close to each other, we see the target node move towards the second community.
 
-    \begin{subsection}{2 Community}
+        \subsubsection{2 Community}
             \begin{figure}
-            \foreach \i in {1,...,15} {%
-                \begin{subfigure}[p]{0.3\textwidth}
-                    \includegraphics[width=\linewidth]{../Code/Plots/Test Only/2communities/2communities \i.png}
+                \foreach \i in {3,6,9,12,15} {%
+                    \begin{subfigure}[p]{0.4\textwidth}
+                        \includegraphics[width=\linewidth]{../Code/Plots/Test Only/2communities/2communities \i \space small net.png}
                         \caption{t=\i}
@@
 
-        In contrast, the symbolic regression predicted the location of the target node very well at the beginning of the test period, but after about 5 steps starts to drift away.
+            Similarly, the symbolic regression prediction remains close to the neural network prediction at the beginning of the test period, but towards the end of the test period begin to drift away.
 
-        The poor predictive behaviour of the neural network especially may be attributed to this being a symmetrical problem.
-That is the same set of distances as input into the neural network, the target node needs to move away from its nearest neighbours in the first half, then move towards its nearest neighbours in the second half.
+            The poor predictive behaviour of the models may be attributed to this being a symmetrical problem.
+That is, with the same set of distances as input into the model, the target node needs to move away from its nearest neighbours in the first half, then move towards its nearest neighbours in the second half.
+
             Potential ways of breaking this symmetry may be to include information of the previous time step, or to include the absolute position of the target node as input into the neural network.
 
-        Notably, using the small neural network model to train the symbolic regression gave much better predictions than the large neural network\ref{2community series large neural network}.
-
-        % It is interesting to see the symbolic regression model perform so much more poorly than the neural network model in this system.
-When we view the training section of the data, we see that there is a downward curve in the neural network predictions towards the end of the training data.
-It seems that the symbolic regression model picked this up and continued the downward trajectory throughout the test data.
-This downward curve may be because the problem that we are trying to solve is symmetrical.
-That is
-    \end{subsection}
-
-    \begin{subsection}{Long Tail}
+        \subsubsection{Long Tail}
             \begin{figure} 
-            \foreach \i in {1,...,15} {%
-                \begin{subfigure}[p]{0.3\textwidth}
-                    \includegraphics[width=\linewidth]{../Code/Plots/Test Only/longTail/longTail \i.png}
+                \foreach \i in {3,6,9,12,15} {%
+                    \begin{subfigure}[p]{0.4\textwidth}
+                        \includegraphics[width=\linewidth]{../Code/Plots/Test Only/longTail/longTail \i \space small net.png}
                         \caption{t=\i}
@@
 It is clear that neither the symbolic regression model nor the neural network model capture this movement.
-We also see that the symbolic regression model maintains a relatively stable position when compared to the neural network model.
+
+            However, the symbolic regression model maintains an appropriate distance from the origin oven if it does not follow the movement of the target node.
 
             We see that neither the neural network model capture the movement of the target node to any real extent.
-One reason for this may again be an issue of symmetrical input.
-The distances from the k nearest neighbours to the target node do not seem to change much as the target node jumps from one arm to the other, but the neural network somehow needs to learn to jump left then right at alternating time steps.
-The solutions to this would be the same as for the two community system.
-    \end{subsection}
+One reason for this may be that by the time the system progresses to the test section the number of nearest neighbours (k=15) means that the input for the model no longer includes the large community used to orient the system.
+Because of this, the model will essentially be given the same input at every time step, but will have to somehow produce the alternating behaviour of the target node.
+This again is an issue of symmetry.
 
-    \begin{subsection}{Three Community}
+            The solutions to symmetry in this problem would be the same as for the two community system.
+That is, to break the symmetry by including the absolute position of the target node as input for the model, or to have multiple time steps as input.
+
+            Another potential solution we might consider in this instance, could be increasing the number of nearest neighbours so that the model always has a reference point.
+That is, the model would have the position of the large community as input.
+This solution would not generalise well however, as, in general, we may not know how long a tail could be, and therefore how many nearest neighbours to include.
+
+        \subsubsection{Three Community}
             \begin{figure}
-            \foreach \i in {1,...,15} {%
-                \begin{subfigure}[p]{0.3\textwidth}
-                    \includegraphics[width=\linewidth]{../Code/Plots/Test Only/3community/3community \i.png}
+                \foreach \i in {3,6,9,12,15} {%
+                    \begin{subfigure}[p]{0.4\textwidth}
+                        \includegraphics[width=\linewidth]{../Code/Plots/Test Only/3community/3community \i \space small net.png}
                         \caption{t=\i}
@@
             \end{figure}
-        In fig \autoref{3community series} we again, as the edges between the community with the fewest edges are removed, we see the target node move away from it in the embedding and towards the other two clusters of points (communities).
+            In fig \autoref{3community series} we see both models move roughly in the same direction as the target node.
+The neural network however moves quickly ahead of the target node and, as it does, away from the precise direction of the target node.
 
-        For the first ten time steps, we see similar behaviour between the neural network model and the neural network model.
-However, around the eleventh time step, the symbolic regression model begins to diverge from the neural network.
-The symbolic regression moves back towards the target node towards the end.
-This could indicate that the symbolic regression is a somewhat more robust model when extrapolating, but more testing should be done to corroborate this.
+            In contrast, the symbolic regression model maintains a very small distance to the target node.
 
-        Notably the symbolic regression trained on the large neural network performed extremely well, while the predictions of the large neural network model itself did not seem to make any significant improvement\ref{3community series large neural network}.
-This may indicate that...XXXXX
-        % In the neural network only model, we see the prediction follow the true target node very closely at first.
-We then see the node drift further and further from the true target node.
-In contrast, the symbolic regression model remains much closer to the true position of the target node as the test data progresses.
-We see the symbolic regression move slightly ahead of the true location at first, but this distance remains relatively constant thereafter.
+            This system was constructed to avoid the symmetrical input of the other two systems.
+The models built for the 3 community system are by far the most accurate, with the symbolic regression model being particularly impressive.
 
-        In the neural network model, we see the prediction remain at close to its initial location for the duration of the test. This seems to indicate an attractor in the model.
-
-        In contrast, we see that the symbolic regression model quickly moves ahead of the true location where it remains for the duration of the test.
-
-        % This was by far the largest improvement between the neural network and the symbolic regression.
-This could be because this system had the least difference between the training predictions and the true position of the target node.
-At the end of the test data we see the true target node move towards the origin.
-This is because it now only has edges to one community and so at each timestep it removes one of these.
-If this had continued, the target node would have no edges.
-Nodes with no edges are mapped to the origin.
-When this happened, the symbolic regression model prediction began to move further from the true node.
+            This supports the notion that symbolic regression, when the training data is non-symmetrical, can give more robust predictive models than a NNDE alone.
 
@@
 
-        These were trained on a relatively small neural network (one hidden layer of 64 nodes), when training this small network one of the issues we encountered was that the weights would become stuck in local minima.
-To manage this we found that simulate annealing was helpful.
-When training on a larger network (4 hidden layers (64,8,8,8)) this does not seem to be as much of a problem.
-    \end{subsection}
+                These were trained on a relatively small neural network (4 hidden layers (64,8,8,8)).
 
@@
 
-\begin{section}{Conclusion}
-    In this paper, we proposed a novel framework for modelling temporal networks.
+\begin{section}{Code}
+    \subsection{Summary}
+    The idea of this code is to provide a foundation for a streamline research into temporal network modelling.
+To that end it is planned to be compatible with popular Julia packages such as Graphs, the SciML ecosystem, and EcologicalNetworks.
+    \subsection{Statement of Need}
+
+    \subsection{Package Methods}
+
+    \subsection{Comparable Methods and Related Work}
+    Teneto Python
+
+    packages("sna")  R
+    packages("tsna")
+    packages("ndtv")
+
+    EvolvingGraphs Julia
+
+    \subsection{Past and Ongoing Research}
+    Wrote code that is general
+
+    Made a structure (TemporalNetworkEmbedding)
+
+    Useful functions include nearestNeighbours, and constructRDPG.
+\end{section}
+% \begin{section}{Conclusion}
+%     In this paper, we proposed a novel framework for modelling temporal networks.
 We then tested this framework on three types of small, synthetic network sequences.
 Throughout these tests the neural network performed generally more poorly than the symbolic regression model, with the large three community sequence being especially notable due to th symbolic regression remaining so close to the target node throughout the test period.
-\end{section}
+% \end{section}
 

### 2023-06-06 Conference Submission/DraftDoc.tex
skeleton done

@@
 
+    Each model was trained on a neural network with 4 hidden layers (64,8,8,8).
+
     \subsection{Two Community System}
@@
 Notably, the movement in the two community system is difficult for the neural network to learn because opposite sets of inputs need to result in the same output.
-In a simplified version of this system with only the nearest node as input, the input for the model begins as the position of the larger community at roughly $(0,-1)$ \autoref{2community series 1}.
+In a simplified version of this system with only the nearest node as input, the input for the model begins as the position of the larger community at roughly $(0,-1)$ \autoref{2community series 3}.
 This input needs to move the target towards the top left.
@@
     \subsection{Long Tail System}
+        \label{longtaildata}
         In the long tail network \autoref{longTail train series}, we have a long chain with 50 nodes and a fully connected component with forty nodes at one end of the chain.
@@
 The temporal embeddings were then divided into a training set of 20 and a testing set of 15.
-The output of the trained neural networks was then used to train a symbolic regression model that could use a simple set of addition, subtraction, division, and multiplication.
+The output of the trained neural networks was then used to train a symbolic regression model that could use a simple set of addition, subtraction, and multiplication.
 
@@
                     \hline
-                    2 Community & 5.784 & 10.16\\ 
+                    2 Community & 0.224 & 0.145 \\ 
                     \hline 
-                    Long Tail  & 3.858 & 0.057 \\ 
+                    Long Tail  & 0.093 & 0.331 \\ 
                     \hline 
-                    3 Community & 6.597 & 2.047 \\ 
+                    3 Community & 43.064 & 2.768 \\ 
                     \hline 
@@
 
-        As can be seen in \autoref{loss_table}, the symbolic regression model performed better for both the long tail system and the 3 community system.
-However, for the 2 community system the symbolic regression model performed notably worse.
+        As can be seen in \autoref{loss_table}, the symbolic regression model performed better for both the 2 and 3 community system.
+However, for the long tail system the symbolic regression model performed notably worse.
 
@@
         Instead, we may compare predictions within the same system.
-However, we do not see much difference between these predictions, and so we plot our predictions at each time step to further understand the behavior of our framework.
+However, we do not necessarily get a good understanding of the behaviour of our models with just this summary.
+We plot our predictions at every third time step to further understand the behavior of the models generated by our framework.
 
@@
             \end{figure}
-            We see the neural network model quickly jumps to around $(-0.5,-0.5)$ where it sits for the entire simulation.
-This happened across many training periods; either a few time steps after the training period or right at the end of it, the neural network model moved towards a stable point where it remained for the test period.
+            We see both the neural network model and the symbolic regression models follow quite closely to the target node throughout the test process.
+As we saw in \autoref{loss_table}, the NN model performs slightly worse than the symbolic regression model.
+This improvement of symbolic regression was present throughout the test period.
 
-            Similarly, the symbolic regression prediction remains close to the neural network prediction at the beginning of the test period, but towards the end of the test period begin to drift away.
+            In spite of the simple movement of the target node, these close predictions were unexpected.
+When creating this system, we were looking to test how the model would perform with symmetrical input data.
+We hypothesised that this may be difficult for the NN model to learn, as it would need to learn to give the same output with opposite input.
 
-            The poor predictive behaviour of the models may be attributed to this being a symmetrical problem.
-That is, with the same set of distances as input into the model, the target node needs to move away from its nearest neighbours in the first half, then move towards its nearest neighbours in the second half.
-
-            Potential ways of breaking this symmetry may be to include information of the previous time step, or to include the absolute position of the target node as input into the neural network.
+            In this case however, it seems that predicting the movement of the target node was not affected by this symmetry.
 
@@
             \end{figure}
-            In fig \autoref{longtail series} we see the true embedding of the target node jump from one arm to the other at each time step.
+            In fig \autoref{longtail series} we see the true embedding of the target node move from one arm to the other between the time steps 9 and 12.
 It is clear that neither the symbolic regression model nor the neural network model capture this movement.
 
-            However, the symbolic regression model maintains an appropriate distance from the origin oven if it does not follow the movement of the target node.
+            From \autoref{loss_table}, we see that the NN model had a higher accuracy than the symbolic regression.
+However, the NN model does not follow the true node; instead it stays in relatively the same spot, as opposed to the symbolic regression model, which does move.
 
@@
 
-            The solutions to symmetry in this problem would be the same as for the two community system.
-That is, to break the symmetry by including the absolute position of the target node as input for the model, or to have multiple time steps as input.
+            The solutions to this symmetry in this problem would be to break the symmetry by including the absolute position of the target node as input for the model, or to have multiple time steps as input.
 
-            Another potential solution we might consider in this instance, could be increasing the number of nearest neighbours so that the model always has a reference point.
-That is, the model would have the position of the large community as input.
-This solution would not generalise well however, as, in general, we may not know how long a tail could be, and therefore how many nearest neighbours to include.
+            Another potential reason for the poor behavior could be that the embedding of the temporal network does not contain enough information to train a NNDE model.
+This is discussed in \autoref{longtaildata}.
 
@@
             \end{figure}
-            In fig \autoref{3community series} we see both models move roughly in the same direction as the target node.
-The neural network however moves quickly ahead of the target node and, as it does, away from the precise direction of the target node.
+            In fig \autoref{3community series} we see the symbolic regression model move in roughly the same direction as the target node.
+The NN model however, moves quickly towards the bottom left, away from the target node.
 
-            In contrast, the symbolic regression model maintains a very small distance to the target node.
+            In contrast, after the third time step, the symbolic regression model prediction maintains a relatively constant distance to the target node.
 
-            This system was constructed to avoid the symmetrical input of the other two systems.
-The models built for the 3 community system are by far the most accurate, with the symbolic regression model being particularly impressive.
+            This system was constructed to avoid the symmetrical input of the other two systems. Because of this, it is interesting to see the poor predictive performance of the NN model.
 
-            This supports the notion that symbolic regression, when the training data is non-symmetrical, can give more robust predictive models than a NNDE alone.
+            We see that the symbolic regression model significantly improved the predictions, which supports the notion that symbolic regression, can give more robust predictive models than a NNDE alone.
 
     \subsection{Summary}
-                We see a large difference in the training predictions between the 2 and 3 community systems.
-In the 2 community system, even in the training period, the predictions tended to wander and be less accurate.
-Whereas the 3 community training predictions remained very close to the true target node.
-The movement of the target node in the embedding was very similar between the two systems, and so the difference seems to be that the 2 community has symmetrical inputs.
-
-                These were trained on a relatively small neural network (4 hidden layers (64,8,8,8)).
+      In the 2 and 3 community systems, we see that symbolic regression improved the accuracy of the predictions across all time steps when compared to the NN model.
+This is especially prominent in the 3 community system.
+In the long tail system, where the symbolic regression model performed worse than the NN model, neither performed well, with the NN model remaining in relatively the same spot throughout the test period.
 
@@
 To that end it is planned to be compatible with popular Julia packages such as Graphs, the SciML ecosystem, and EcologicalNetworks.
+
+        The core of the code developed for this project is the TemporalNetworkEmbedding (TNE) structure.
+This structure was developed not only for me to be able to interface with data quickly and easily, but also so the SciML ecosystem could interface with it during training of the NN.
+In particular, the ability to index the TNE with a float was essential for the continuous time evolution of the UDEs and NNDEs to function.
+
     \subsection{Statement of Need}
+        Throughout this thesis, we have demonstrated that temporal networks are found in many different areas, that, on small networks, temporal progression of embedded nodes can be modelled with NNDEs, and that there are still problems to be overcome.
+
+        With this in mind, the code has been developed to:
+
+            1: Allow for interface with popular packages
+
+            2: Allow for further exploration of optimal network structures for deep learning
+
+            3: Provide opportunities for collaboration of experts from other fields
 
     \subsection{Package Methods}
+        In the package \cite{DotProductGraphs}, I created code for constructing:
+        % ADD NOTATION
+        The TemporalNetworkEmbedding structure.
+This structure stores the temporal network as tensors of the $\hat L, \hat R$ matrices.
+This structure has many methods for streamlining interactions with the TemporalNetworkEmbedding.
+These include indexing with integers and floats, where the floats will linearly interpolate between time steps.
+Other methods include viewing and or removing specific nodes from the network.
+
+        As well as constructRDPG, which takes a temporal network embedding and optionally the time steps of interest, and outputs the RDPG from the embedding.
+
+        I also added the nearestNeighbours method which takes a vector point in the dimension of the embedding, the time step, a TemporalNetworkEmbedding and the number of nearest neighbours required.
+The method then outputs the indices of the nearest nodes of the network to the vector in descending order.
 

### 2023-06-07 Conference Submission/DraftDoc.tex
eoeu

@@
 \begin{section}{Introduction}
-    Temporal networks are networks whose nodes and edges change in time. In this thesis we look to model temporal networks. That is, describe the temporal network using mathematical language. 
+    Temporal networks are networks whose nodes and edges change in time.
+In this thesis we look to model temporal networks.
+That is, describe the changing temporal network using mathematical language.
     % Why temp nets are important
@@
     % Temp nets are dynam systs
-    Temporal networks can be seen as a system in which points, in our case nodes in a network, whose states, the edges connecting them, that vary dependent in time, a dynamical system.
+    Temporal networks can be seen as a system in which points, in our case nodes in a network, whose states, the edges connecting them, vary dependent in time, a dynamical system.
 
@@
     Discovering the underlying equations governing these dynamical systems proves challenging.
-That is because changes in network structure are typically observed in the form of discrete jumps from one state to another, for example an edge between two nodes not being observed at the first time step then being observed at the next.
+That is because changes in network structure are typically observed in the form of discrete jumps from one state to another; for example an edge between two nodes not being observed at the first time step then being observed at the next.
 
@@
 That is a framework in which a neural network is used to model probabilistic values of the temporal network.
-This framework allows us to model temporal networks as continuous-time dynamical systems, discover a fitting set of differential equations describing it, and, exploiting that discovery, predict the time evolution of a network.
+This framework allows us to model temporal networks as continuous-time dynamical systems, discover a fitting set of differential equations describing it, and, exploiting that discovery, predict the time evolution of a temporal network.
 
@@
     Differential equations are useful for modelling systems where the state of one variable can effect the trajectories of other variables.
-
-    % Temp nets have interacting states 
 We observe this behavior in temporal networks; nodes' connections within the network can influence the observation of edges between other nodes, for example the phenomenon observed in \cite{newman2001clustering,capocci2006preferential}, where a node is more likely to gain the connections the more connections it has (preferential attachment).
@@
     % Temp net events are discrete
-    In the common representation of networks as binary-valued adjacency matrices, matrices where the observation, or lack thereof, of an edge is represented as a 1 or 0 respectively, the events recorded in a temporal sequence of networks correspond to the appearance or the disappearance of link.
+    In the common representation of networks as binary-valued adjacency matrices, matrices where the observation or lack thereof, of an edge is represented as a 1 or 0 respectively, the events recorded in a temporal sequence of networks correspond to the appearance or the disappearance of link.
 
@@
     Because of the discrete nature of events, directly modelling the temporal networks as dynamical systems would require us to handle discrete jumps.
-    The topological nature of temporal networks, and the discontinuous character of their temporal evolution, make it challenging to use differential equations techniques.
+The discontinuous character of their temporal evolution, make it challenging to use differential equations techniques.
 
     % We propose a solution
-    Here, we overcome the discreteness problem by interpreting networks as a well established statistical model for complex networks, that embeds nodes in a continuous, low-dimensional metric space by using a truncated singular value decomposition (Random Dot Product Graphs\cite{athreya2017statistical}).
+    Here, we overcome the discreteness problem by interpreting temporal networks as a well established statistical model for complex networks, which embeds nodes in a continuous, low-dimensional metric space by using a truncated singular value decomposition (Random Dot Product Graphs\cite{athreya2017statistical}).
 In this way we translate the hard problem of modelling discrete events in the space of networks to the easier problem of modelling continuous change in the embedding space.
@@
     % Our solution is interpretable because we use symb reg
-    We then define and use systems of Neural Network Differential Equations (NNDE)\cite{SciML_C_Rak} to approximate the time evolution of the embedding space, and symbolic regression techniques to discover the functional form of the fitted NNDEs.
+    We then define and use Neural Network Differential Equations (NNDE)\cite{SciML_C_Rak} to approximate the time evolution of the embedding space, and symbolic regression techniques to discover the functional form of the fitted NNDEs.
 These functional forms are interpretable (as they read as classic differential equations) and allow us to predict forward in time the evolution of the temporal networks.
@@
     In this manuscript, we show that the temporal network prediction problem can be successfully re-interpreted as a dynamical system modelling problem by taking the singular value decomposition of a sequence of adjacency matrices and training a NNDE to model an approximation to the underlying differential equation.
-We then go on to create a symbolic equation of this approximation.
+We then go on to create a functional equation of this approximation.
 
@@
     As it is completely general, we believe that the framework we are introducing can be usefully applied to areas of medicine, especially protein interaction networks; population dynamics for network ecology; and social network modelling.
-In particular, we discuss how specific domain knowledge relative to the prediction scenario can be taken into account, moving from NNDEs to Universal Differential Equations.
+In particular, we discuss how specific domain knowledge relative to the prediction scenario can be taken into account, moving from NNDEs to Universal Differential Equations (UDEs).
 \end{section}
@@
         % Use of temp nets
+        \subsubsection{Definitions}
         Temporal networks are used to describe a series of interactions across time.
@@
         This can be represented in many ways, for example as a series of interactions.
-The series of interactions is generally represented as a list of tuples containing the node that interacted and the time that the interaction took place.
+The series of interactions is generally represented as a list of tuples containing the nodes which interacted and the time that the interaction took place.
         \begin{align}
@@
 
-        % Uses of temp nets
+        \subsubsection{Applications}
         Temporal networks are present in many areas of research interest, ranging from symptom interactions in mental health\cite{jordan2020current,contreras2020temporal}, to epidemiology\cite{masuda2013predicting}, protein interactions\cite{lucas2021inferring,jin2009identifying}, and social networks\cite{moinet2015burstiness,hanneke2010discrete}.
@@
         An example of modelling the change in a node state could be the severity of a symptom at a given time, as in \Citeauthor{contreras2020temporal}\cite{contreras2020temporal}.
-Where the node $_t x$ represents the symptom and $m_1$ would represent the severity of that symptom.
-
-        Other effort focus on modelling the changing structure of the network as in \Citeauthor{sanna2021link}\cite{sanna2021link}, which looks to model $_t G$ as a whole.
+Where the node $_t x$ represents a given symptom and $m_1$ would represent the severity of that symptom.
 
@@
         \Citeauthor{contreras2020temporal}\cite{contreras2020temporal} model the change in node state over time while the structure of the network remains constant.
-\Citeauthor{contreras2020temporal} look at the severity of symptoms over time, i.e.
-the state of the nodes, as a temporal network where the network structure remains constant.
+The authors look at the severity of symptoms over time, i.e.
+the state of the nodes, where the nodes exist in a statically structured temporal network.
 
         % Contreras methods
-        They use multilevel vector autoregression, a method that finds correlations between the current state of a variable and the states of variables at previous time steps \cite{singer2003applied}, to model how the current symptoms of people with paranoia might predict their future symptoms.
+        \Citeauthor{contreras2020temporal} use multilevel vector autoregression, a method that finds correlations between the current state of a variable and the states of variables at previous time steps \cite{singer2003applied}, to model how the current symptoms of people with paranoia might predict their future symptoms.
 These models were then used to create three networks that linked symptoms.
@@
         % intro to paper as attempt to model node state
-        In \cite{KARIMI20133476}, the \Citeauthor{KARIMI20133476} look to model the change in node state while the network structure changes.
+        In \cite{KARIMI20133476}\cite{KARIMI20133476}, the \Citeauthor{KARIMI20133476} look to model the change in node state while the network structure changes.
 
@@
         % what state the paper attempts to model
-        The authors use a model to predict when a node will change from state 0 to state 1, in practice this could represent whether a user of a social network believes a rumour, or an ecological patch being colonised.
+        The authors use a model to predict when a node will change from state 0 to state 1, in practice this could represent whether a user of a social network believes a rumour, or whether an ecological patch has been colonised.
 
         % Model limitation
-        Notably, in their model the node never changes back; this is done to keep the model analytically tractable, but does limit its usefulness in some contexts.
+        Notably, in this model, the node never changes back; this is done to keep the model analytically tractable, but does limit its usefulness in some contexts.
 In this model an organism could not become locally extinct in an ecological patch for example.
@@
         % Limitation of model
-        In this work I aim to present a model for predicting the state of a node in the future.
+        In this work we aim to present a model for predicting the state of a node in the future.
 Instead, \Citeauthor{KARIMI20133476} aim to present a tool for understanding the spread of ideas, viruses, etc.
@@
 
-        % Intro to pasino et al as modelling structure of temp net
-        \Citeauthor{sanna2021link}\cite{sanna2021link} model the change in the structure of a temporal network.
+        Other efforts focus on modelling the changing structure of the network as in \Citeauthor{sanna2021link}\cite{sanna2021link}, which looks to model $_t G$ as a whole.
 
@@
 In this space nodes are represented as points in a continuous, low dimensional space.
-Another feature of this latent space, is that the dot product of any two points in the space gives us the probability that the nodes related to those points are connected.
+Another feature of this latent space, is that the dot product of any two points in the space gives us the probability that the nodes related to those points are connected, a Random Dot Product Graph (RDPG)\cite{athreya2017statistical}.
 
@@
         In some temporal networks the state of a node might influence the evolution of its neighbours.
-For example, in social networks we often observe the power law distribution of edges, where the more neighbours a node has, the more likely they are to gain more neighbours\cite{zhao2012multi,garg2009evolution}.
+For example, in social networks we often observe that the more neighbours a node has, the more likely they are to gain more neighbours, a power law distribution of edges\cite{zhao2012multi,garg2009evolution}.
 We also see that the state of symptoms (occurrence, severity, and distress), can influence the states of other symptoms in patients undergoing chemotherapy \cite{papachristou2019network,kalantari2022network}, and for mental health disorders \cite{contreras2020temporal}.
@@
         % DEs have lots of research
-        With the observation that nodes in real world temporal networks may influence others, differential equations or difference equations seem appropriate for modelling the evolution of nodes as there is a rich body of literature exploring these methods use in modelling interacting variables.
+        With the observation that nodes in real world temporal networks may influence others, differential equations or difference equations seem appropriate for modelling the evolution of nodes; there is a rich body of literature exploring these methods use in modelling interacting variables.
 
         % The data we have is discrete, which is a problem for DEs
-        One of the issues that the differential equation method encounters is the prevalence of discrete jumps of edges forming and decaying.
-Because of this we may consider exploring the possibility of using difference equations.
+        One of the issues that the differential equation method encounters is the prevalence of discrete jumps of edges being observed and then not being observed.
+Because of this, we may consider exploring the possibility of using difference equations.
 
         % time is continuous so good to have our model be cont too
-        We note that the progression of the network is generally continuous even if the events happen as discrete jumps.
-Because of this, we may wish to preserve the continuous temporal progression in our model.
+        We note that the progression of the network is generally continuous even if the events happen as discrete jumps. We may wish to preserve this continuous temporal progression in our model.
 
@@
         % passino has discrete data but uses a method to view it as cont
-        Looking at the work of Passino et al.\cite{sanna2021link}, the authors use random dot produce graphs\cite{athreya2017statistical} to approximate a temporal network as a matrix of probabilities of an edge existing between two nodes.
+        Looking at the work of \Citeauthor{sanna2021link}\cite{sanna2021link}, the authors use RDPGs to approximate a temporal network as a matrix of probabilities of an edge existing between two nodes.
 In contrast to edges, these probabilities can evolve continuously, and so we can use differential equations to generate probabilistic networks at any temporal resolution we require.
-That is, we will be able to model the changes in the probabilities of edges continuous and from this, generate a network at any time step.
+That is, we will be able to model the changes in the probabilities of edges continuously and from this, generate a network at any time step.
 
         %  we can use the same method we can view data as dynam sys and use DEs
-        Using the method in Passino et al.\cite{sanna2021link}, we can treat the sequence of embeddings as a dynamical system and then use differential equation modelling in a continuous space.
-That is, once we have found a latent space for each network.
-We know that each point in this space refers to a specific node in the network, and so, as the network changes, so too does the position of each of the points in the latent space.
+        Using the method in \Citeauthor{sanna2021link}\cite{sanna2021link}, we can treat the sequence of embeddings as a dynamical system and then use differential equation modelling in a continuous space.
+Once we have found a latent space for each network, we know that each point in this space refers to a specific node in the network, and so, as the network changes, so too does the position of each of the points in the latent space.
 We then look to model this movement using differential equations.
@@
         Our aim for this framework to be as general as possible and note that there may not yet be enough domain knowledge to perform traditional differential equation modelling to the desired accuracy.
-For example in network ecology models can be useful, but not perfect XXX cite XXX.
+For example in network ecology models can be useful, but not perfect.
 Hence, we might wish to build on these models rather than trying to create something entirely new.
-This can be achieved by using this partial domain knowledge using it to create a universal differential equation (UDE) \cite{SciML_C_Rak}.
+This can be achieved by using this partial domain knowledge using it to create a UDE\cite{SciML_C_Rak}.
 
@@
             % Overview of why UDEs are useful
-            Developed by \Citeauthor{SciML_C_Rak}\cite{SciML_C_Rak}, Universal Iifferential Equation (UDEs) are a novel neural network architecture that aims to take the best of both traditional neural differential equation modelling and of flexible machine learning approaches to modelling.
+            Developed by \Citeauthor{SciML_C_Rak}\cite{SciML_C_Rak}, UDEs are a novel neural network architecture that aims to take the best of both traditional neural differential equation modelling and of flexible machine learning approaches to modelling.
 
@@
             % Structure of UDE
-            UDEs combine domain knowledge in the form of a differential equation, with a neural network. This hybrid machine learning model is then trained on the observed data.
+            UDEs combine domain knowledge in the form of a differential equation, with a NN. This hybrid machine learning model is then trained on the observed data.
 
@@
             Combining the two allows for most of the movement in the data to be captured by the differential equation, which contains the domain knowledge.
-In this way the neural network will only need to learn a theoretically simpler equation, given that a part of the system has already been captured.
+In this way, the NN will only need to learn a theoretically simpler equation, given that a part of the system has already been captured.
 
             % Why this structure is useful
-            This then allows the neural network to be smaller, require fewer data, and be trained much faster than traditional neural network models.
-Given the flexibility of neural networks, the use of UDEs is natural when modelling a process that is not entirely understood\cite{kidger2022neural}.
+            This then allows the NN to be smaller, require fewer data, and be trained much faster than traditional NN models.
+Given the flexibility of NNs, the use of UDEs is natural when modelling a process that is not entirely understood\cite{kidger2022neural}.
+
+            Note that we can construct a special case of a UDE, an NNDE when $\hat f(t,y(t))=0$. This structure can be used when do not have any domain knowledge we wish to give the model.
 
@@
             There is an ecosystem of packages specifically designed for performing machine learning with UDEs.
-The ecosystem is called SciML or scientific machine learning\cite{SciML_C_Rak}.
+The ecosystem is called Scientific Machine Learning (SciML)\cite{SciML_C_Rak}.
 Largely, the SciML ecosystem has been optimised for flexibility and efficiency with respect to models available and training performance.
@@
         \subsubsection{Applications}
-            Whilst there has been much interest in implementing UDEs and neural ODEs, much of this work has been focussed on physics informed neural network and physics informed ordinary differential equations (PINNs and PINODEs) \cite{karniadakis2021physics,GAO2021110079,krishnapriyan2021characterizing,roehrl2020modeling}, and on improving modelling of fluids \cite{mahmoudabadbozchelou2021data,nguyen2022physics}.
-Alongside this, and given UDEs have gained popularity in the last few years, there have been a number of studies exploring their usefulness in modeling the effect of restrictions due to COVID-19 on the virus' spread \cite{Dandekar2020.04.03.20052084}.
+            Whilst there has been much interest in implementing UDEs and NNDEs, much of this work has been focussed on physics informed neural network and physics informed neural ordinary differential equations (PINNs and PINODEs) \cite{karniadakis2021physics,GAO2021110079,krishnapriyan2021characterizing,roehrl2020modeling}, and on improving modelling of fluids \cite{mahmoudabadbozchelou2021data,nguyen2022physics}.
+Alongside this, UDEs have gained popularity in the last few years, and there have been a number of studies exploring their usefulness in modeling the effect of restrictions due to COVID-19 on the virus' spread \cite{Dandekar2020.04.03.20052084}.
 Although there has been a large amount of research into the usefulness of these types of models, to the best of this author's knowledge they have never been applied to the problem of predicting temporal networks.
-This seems to be a natural fit for UDEs and neural ODEs, given we may know relatively little about the processes that govern the evolution of temporal networks, and any information we do have can be incorporated into the model.
+This seems to be a natural fit for UDEs and NNDEs, given we may know relatively little about the processes that govern the evolution of temporal networks, and any information we do have can be incorporated into the model.
 
@@
         % What is symbolic regression
-        Symbolic regression is a type of analysis that looks to find a relationship between input variables that describe the output variables.
-For symbolic regression, we define a set of equations that may be used to find this relationship.
+        Symbolic regression is a type of analysis that looks to take input variables and find a relationship between them that describes the output variables.
+For symbolic regression, we construct a set of mathematical operations that may be used to find this relationship.
 The algorithm then generates combinations of these equations to find an expression that matches the output variables.
-Because we define the set of potential equations, the resulting expression is interpretable by humans, as opposed to a NN for example.
+Because we construct the set of potential operations, the resulting expression is interpretable by humans (a functional equation), as opposed to a NN for example (a numeric equation).
 
@@
         % How is this done
-        This can be achieved in many ways and remains active area of research. One of the most popular algorithms is genetic programming\cite{schmidt2009distilling}.
+        Finding a suitable functional expression can be achieved in many ways and remains active area of research.
+One of the most popular algorithms is genetic programming\cite{schmidt2009distilling}.
 
         % How genetic programming works
-        Genetic programming involves constructing a search tree using a genetic algorithm to yield a potential equation, which may match the data as well as numerically calculated partial derivatives of each of the input variables.
+        Genetic programming involves constructing a search tree using an evolutionary algorithm to yield candidate equations.
+An evolutionary algorithm is an iterative process.
+It begins by randomly generating a set of candidate equations with operations from the given set of operations:
+        \begin{align}
+            Q_1=\{f_1,\dots,f_n\}
+        \end{align}
+        Each candidate function $f_i$ is tested and given a fitness score based on how well it performed. The higher a candidates' fitness, the more likely it is to be selected for the next iteration.
+
+        Suppose $f_1,f_2$ were selected for the next iteration. The evolutionary algorithm would then randomly generate new functions based on $f_1,f_2$ again with the given set of operations.
+        \begin{align}
+            Q_2=\{f_{1,1},\dots,f_{1,n}, f_{2,1},\dots,f_{2,n}\}
+        \end{align}
+        This process is repeated until a suitable functional equation is found.
+
+        For the genetic programming algorithm, the fitness of a candidate function is determined by how closely it matches the data as well as numerically calculated partial derivatives of each of the input variables.
 
@@
         % Examples of use of genetic programming
-        For example, both \Citeauthor{schmidt2009distilling,bongard2007automated} test their methods' capacity for obtaining a symbolic equation with physical simulation data, various pendula specifically.
-A ``meaningful'' equation in this case would be one that adheres to the laws of physics.
+        For example, both \Citeauthor{schmidt2009distilling,bongard2007automated} test their methods' capacity for obtaining a functional equation with physical simulation data, various pendula specifically.
+A ``meaningful'' equation in this case may be an equation that conserves momentum.
 
@@
         Examples of genetic programming include discovering equations governing the movement of simple harmonic and chaotic double pendula from data\cite{schmidt2009distilling}.
-In this paper the authors present an evolutionary algorithm to generate multiple candidate functions that approximate the partial derivatives of each variable that are calculated directly from the data.
+In \Citeauthor{schmidt2009distilling}, the authors present an evolutionary algorithm to generate multiple candidate functions that approximate the partial derivatives of each variable that are calculated directly from the data.
 
         % Intro to bongard
-        Another approach to symbolic regression can be found in \cite{bongard2007automated}.
-This paper proposes a method to find a symbolic equation that approximates a learned numerical equation rather than directly from data.
+        Another approach to symbolic regression can be found in \Citeauthor{bongard2007automated}\cite{bongard2007automated}.
+The authors propose a method to find a functional equation that approximates a learned numerical equation rather than directly from data.
 
         % How does this process work
-        The candidate equation is then tested against the numerical equation in such a way that the difference between the two predictions are maximised.
+        The algorithm generates a set of candidate equations.
+The candidate equations are then tested against the numerical equation in such a way that the difference between the candidate and numerical predictions are maximised.
 The algorithm will generate new initial conditions to find behaviour exhibited by the numerical equation, for example a fixed point, that is not exhibited by the functional equation.
-When a difference is found, the functional equation is adjusted to also exhibit the behaviour of the numerical equation.
+When a difference is found, the functional equations are adjusted to also exhibit the behaviour of the numerical equation.
 
         % Limitations of this process
-        Especially when using a neural network model as the numerical equation, it seems these process may not be useful if the initial conditions are outside the scope of the training data.
+        We will be using a UDE with relatively small data sets.
+The models will be trained on a small range of input values, and so we would not have confidence that any behaviour exhibited outside the range of these input values would reflect the underlying system.
+As such, this method may not yield us useful results.
 
         % Benefits of combining UDEs and symbolic regression
-        In very recent work, Kidger\cite{kidger2022neural}, demonstrates that, with UDEs, two of the assumptions necessary for symbolic regression can be overcome.
-Those are the necessity for paired observations and derivatives, as well as the assumption that the function can be expressed as a shallow tree of symbolic operations.
+        In very recent work, Kidger\cite{kidger2022neural} demonstrates that, with UDEs, two of the assumptions necessary for symbolic regression can be overcome.
+Those are the requirement for paired observations and derivatives, as well as the assumption that the function can be expressed as a shallow tree of symbolic operations.
 We are modelling a differential equation, and so will have access to the derivatives of our numerical model at any point, as neural networks are easily differentiable.
@@
         % Usefulness of symbolic regression for nnde
-        In \Citeauthor{SciML_C_Rak}\cite{SciML_C_Rak}, the authors demonstrate that using symbolic regression, as opposed to just an NNDE, can improve the accuracy of extrapolating.
-One aspect of this improvement is having accurate numerical derivative to compare to.
-To ensure this, it is important that the data is sampled very frequently.
-This seems integral to the accuracy of the found equation.
+        In \Citeauthor{SciML_C_Rak}\cite{SciML_C_Rak}, the authors demonstrate that by using symbolic regression to find a functional equation of our model, as opposed to just a UDE, we can improve the accuracy of extrapolating.
 \end{section}
@@
         % How we achieve this goal
-        To achieve this, we reinterpret each graph as a sequence of points in a latent space; that is, a space in which similar vertices (ones with many of the same neighbours) are mapped to a similar point in space.
-        We then Train a Neural Network Differential Equation (NNDE) to approximate the rate of change of the points in this latent space.
+        To achieve this, we reinterpret our temporal network as a sequence of points in a latent space; that is, a space in which similar vertices (ones with many of the same neighbours) are mapped to a similar point in space.
+        We then train a Neural Network Differential Equation (NNDE) to approximate the rate of change of the points in this latent space.
 With this numerical equation we can then use symbolic regression techniques to find a functional equation that matches the numerical equation.
-Using this process we discover an interpretable function that governs the evolution of a differential equation.
+Using this process we discover an interpretable function that governs the evolution of a temporal network.
 
@@
                 \begin{tabular}{llll}
-                \begin{subfigure}[c]{0.25\textwidth}
+                \begin{subfigure}[c]{0.3\textwidth}
                     \centering
@@
                 \centering
-                \begin{subfigure}[c]{0.25\textwidth}
+                \begin{subfigure}[c]{0.3\textwidth}
                     \centering
@@
             \end{subfigure}
+
             \begin{subfigure}[c]{1\textwidth}
@@
 
+            \begin{subfigure}[c]{1\textwidth}
                 \begin{tabular}{llll}
+                    $\begin{bmatrix}
+                        -0.82  & 0.01\\
+                        -0.64  & 0.36\\
+                        -0.95 & -0.76\\
+                        -0.64 &  0.36\\
+                        -0.48 &  0.82\\
+                        -0.17 & -0.40\\
+                        -0.20 & -0.52\\
+                        -0.07 &  0.25\\
+                    \end{bmatrix}$
+
+                &
+
+                    $\begin{bmatrix}
+                        -0.82  &  0.10\\
+                        -0.82  &  0.10\\
+                        -0.90 & -0.58\\
+                        -0.82  &  0.10\\
+                        -0.42 &  0.81\\
+                        -0.13  & -0.64\\
+                        -0.13  & -0.64\\
+                        -0.12 &  0.57\\
+                    \end{bmatrix}$
+
+                &
+                $\cdots$
+                &
+
+                    $\begin{bmatrix}
+                        -0.85 &  -0.10\\
+                        -0.85 &  -0.10\\
+                        -0.85 &  -0.10\\
+                        -0.85 &  -0.10\\
+                         0.08 &  -0.69\\
+                         0.11 &  -0.88\\
+                         0.11 &  -0.88\\
+                         0.08 &  -0.69\\
+                    \end{bmatrix}$
+                \end{tabular}
+
+            \end{subfigure}
+
+            \begin{subfigure}[c]{1\textwidth}
+                \begin{tabular}{llll}
+                \begin{subfigure}[c]{0.31\textwidth}
+                    \centering
+                    \begin{subfigure}[p]{1\textwidth}
+                        \includegraphics[width=\linewidth]{../Code/Plots/examples/plot 1.png}
+                        \label{}
+                    \end{subfigure}
+
+                \end{subfigure}
+                &
+                \centering
+                \begin{subfigure}[c]{0.31\textwidth}
+                    \centering
+                    \begin{subfigure}[p]{1\textwidth}
+                        \includegraphics[width=\linewidth]{../Code/Plots/examples/plot 2.png}
+                        \label{}
+                    \end{subfigure}
+                \end{subfigure}
+                &
+                $\cdots$
+                &
+                \centering
+                \begin{subfigure}[c]{0.31\textwidth}
+                    \centering
+                    \begin{subfigure}[p]{1\textwidth}
+                        \includegraphics[width=\linewidth]{../Code/Plots/examples/plot 3.png}
+                        \label{}
+                    \end{subfigure}
+                \end{subfigure}
 
                 \end{tabular}
+                \caption{Example sequence of networks.}
+                \label{method nets}
+
+            \end{subfigure}
 
@@
                 A&=l\sqrt{\Sigma} \sqrt{\Sigma} r' \\
-                A&=L R'
+                A&=L R' \quad \text{where} \; L=l\sqrt \Sigma,\: R=\sqrt \Sigma r'
             \end{align}
-            Where $L, R$ are real valued, orthonormal matrices.
-The columns of $L$ consist of the $n$ largest eigenvectors of $AA'$ and the columns $R$ consist of the eigenvectors of $A'A$.
+            Where $l, r$ are real valued, orthonormal matrices.
+The columns of $l$ consist of the $n$ largest eigenvectors of $AA'$ and the columns $r$ consist of the eigenvectors of $A'A$.
 $\Sigma$ is a diagonal matrix whose entries are the square root of the positive eigenvalues of $A'A$ in decreasing order.
@@
         The 2 community temporal network was selected to test whether this framework can be used to model a node changing communities in systems where there are no other processes occurring.
-Notably, the movement in the two community system is difficult for the neural network to learn because opposite sets of inputs need to result in the same output.
-In a simplified version of this system with only the nearest node as input, the input for the model begins as the position of the larger community at roughly $(0,-1)$ \autoref{2community series 3}.
+Notably, the movement in the two community system may be difficult for the neural network to learn because opposite sets of inputs need to result in the same output.
+In a simplified version of this system with only the nearest node as input, the input for the model begins as the position of the larger community at roughly $(0,-1)$ \autoref{2community series}.
 This input needs to move the target towards the top left.
@@
             \end{figure}
-            We see both the neural network model and the symbolic regression models follow quite closely to the target node throughout the test process.
+            In \autoref{2community series}, we see both the neural network model and the symbolic regression models follow quite closely to the target node throughout the test process.
 As we saw in \autoref{loss_table}, the NN model performs slightly worse than the symbolic regression model.
@@
             \end{figure}
-            In fig \autoref{longtail series} we see the true embedding of the target node move from one arm to the other between the time steps 9 and 12.
+            In \autoref{longtail series} we see the true embedding of the target node move from one arm to the other between the time steps 9 and 12.
 It is clear that neither the symbolic regression model nor the neural network model capture this movement.
@@
             \end{figure}
-            In fig \autoref{3community series} we see the symbolic regression model move in roughly the same direction as the target node.
+            In \autoref{3community series} we see the symbolic regression model move in roughly the same direction as the target node.
 The NN model however, moves quickly towards the bottom left, away from the target node.
@@
 
-    \subsection{Comparable Methods and Related Work}
-    Teneto Python
+    \subsection{Future Work}
+        The current TNE structure is not yet GPU compatible. We plan to remedy this as well as include support for constructing a TNE from Graph.jl and MetaGraph.jl objects.
 
-    packages("sna")  R
-    packages("tsna")
-    packages("ndtv")
+\end{section}
 
-    EvolvingGraphs Julia
-
-    \subsection{Past and Ongoing Research}
-    Wrote code that is general
-
-    Made a structure (TemporalNetworkEmbedding)
-
-    Useful functions include nearestNeighbours, and constructRDPG.
+\begin{section}{Conclusion}
+    In this thesis, we proposed a novel framework for modelling temporal networks.
+We then tested this framework on three types of small, synthetic network sequences.
+Throughout these tests we showed that an NNDE model can be used to approximate the movement of points in the embedded space of some temporal networks.
+We also demonstrated that a functional expression generated using symbolic regression can increase the accuracy of prediction on unseen data.
+This has been a proof of concept for this framework; we believe future work can dramatically improve the understanding and modelling of this framework.
 \end{section}
-% \begin{section}{Conclusion}
-%     In this paper, we proposed a novel framework for modelling temporal networks.
-We then tested this framework on three types of small, synthetic network sequences.
-Throughout these tests the neural network performed generally more poorly than the symbolic regression model, with the large three community sequence being especially notable due to th symbolic regression remaining so close to the target node throughout the test period.
-% \end{section}
 

### 2023-06-10 Code/PlottingCode/plotSltn.jl
illustrating movement

@@ -1,10 +1,13 @@
 using PlotlyJS
 using ColorSchemes
 using Lux
+using SymbolicRegression
+using SymbolicUtils
+using DelimitedFiles
 include("../_Modular Functions/loadGlobalConstants.jl")
 
-include("../_Modular Functions/pca.jl")
-global_consts("longTail", (182,2))
+# include("../_Modular Functions/pca.jl")
+global_consts("2communities", (182,2))
 
 include("symreg.jl")
 p1, p2 = (1,2)
@@ -31,19 +34,23 @@ sltn = readdlm("./Code/Solutions/$net_name big net test only.csv", ',')
 
 t_data[1][:AL]
 
-for i in 1:length(t_data)-datasize
-    pts = t_data[i+datasize][:AL]#get_embedding([sltn_sym_reg[:,i]'; t_data[i+datasize]], sltn[:,i])
+for i in 1:length(t_data)
+    pts = t_data[i][:AL]#get_embedding([sltn_sym_reg[:,i]'; t_data[i+datasize]], sltn[:,i])
     
-    traces0 = PlotlyJS.scatter(x=[sltn[p1,i]], y=[sltn[p2,i]], mode="markers", name="Neural Network Pred", marker_size=12)
-    traces1 = PlotlyJS.scatter(x=[sltn_sym_reg[p1,i]], y=[sltn_sym_reg[p2,i]], mode="markers", name="Symbolic Regression Pred", marker_size=12)
+    #traces0 = PlotlyJS.scatter(x=[sltn[p1,i]], y=[sltn[p2,i]], mode="markers", name="Neural Network Pred", marker_size=12)
+    #traces1 = PlotlyJS.scatter(x=[sltn_sym_reg[p1,i]], y=[sltn_sym_reg[p2,i]], mode="markers", name="Symbolic Regression Pred", marker_size=12)
+
+    traces0 = PlotlyJS.scatter(x=[], y=[], mode="markers", name="Neural Network Pred", marker_size=12)
+    traces1 = PlotlyJS.scatter(x=[], y=[], mode="markers", name="Symbolic Regression Pred", marker_size=12)
+
     traces2 = PlotlyJS.scatter(x=[pts[1,p1]], y=[pts[1,p2]], mode="markers", name="Target Node", marker_size=12)
     
     traces3 = PlotlyJS.scatter(x=pts[2:end,p1], y=pts[2:end,p2], mode="markers", name="Data")
 
[…]

### 2023-06-10 Code/PlottingCode/visualiseTraining.jl

@@ -1,6 +1,4 @@
-using SymbolicRegression
-using SymbolicUtils
-using DelimitedFiles
+
 include("../_Modular Functions/helperFunctions.jl")
 
 sltn = readdlm("./Code/Solutions/$net_name big net.csv", ',')

### 2023-06-10 Code/_Modular Functions/helperFunctions.jl

@@ -1,13 +1,7 @@
 using DataFrames
-using Graphs
-using DifferentialEquations
-using DiffEqFlux
-using OrdinaryDiffEq
-using Optim
-using SymbolicRegression
 using LinearAlgebra
 using Arpack
-using Distances
+
 
 
 

### 2023-06-10 Code/structs/TemporalEmbedding.jl

@@ -41,7 +41,7 @@ function TemporalNetworkEmbedding(TempNet::AbstractVector{T}, d::Int) where T<:A
 
 
     n = size(TempNet[1])[1]
-    svd_engine(A,d) = Arpack.svds(A,nsv=d, v0=[Float64(i%7) for i in 1:minimum(size(A))])[1]
+    svd_engine(A,d) = Arpack.svds(A,nsv=d, v0=[Float32(i%7) for i in 1:minimum(size(A))])[1]
     
 
     true_dataL = zeros(Float32, n,d, length(TempNet))

### 2023-06-11 Conference Submission/DraftDoc.tex
Chapterised

@@
-\documentclass[12pt]{amsart}
+\documentclass[12pt]{amsbook}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{array}
+\usepackage{cleveref}
 \addbibresource{bibliography.bib}
@@
 \linespread{1.5}
-
+\let\cleardoublepage\clearpage
 % Override ugly default link
@@
 
-\begin{section}{Introduction}
+\begin{chapter}{Introduction}
     Temporal networks are networks whose nodes and edges change in time.
@@
 In particular, we discuss how specific domain knowledge relative to the prediction scenario can be taken into account, moving from NNDEs to Universal Differential Equations (UDEs).
-\end{section}
-
-\begin{section}{Literature Review}
-
-    \subsection{Temporal Networks}
+\end{chapter}
+
+\begin{chapter}{Literature Review}
+
+    \section{Temporal Networks}
         % Use of temp nets
-        \subsubsection{Definitions}
+        \subsection{Definitions}
         Temporal networks are used to describe a series of interactions across time.
@@
         $_t x \in {_t} N, {_t} e\in {_t} E$, where ${_t} x, {_t} e$ are nodes and edges at time $t$ respectively, and ${_t} N, {_t} E$ are the sets of nodes and edges at time $t$ respectively.
-        An example of this can be found in \autoref{method nets}.
-
+        An example of this can be found in \cref{method nets}.
+        \begin{figure}[H]
+            \begin{tabular}{llll}
+            \begin{subfigure}[c]{0.3\textwidth}
+                \centering
+                \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology1.tex}}
+                \label{method net, a}
+            \end{subfigure}
+            &
+            \centering
+            \begin{subfigure}[c]{0.3\textwidth}
+                \centering
+                \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology2.tex}}
+                \label{method net, b}
+            \end{subfigure}
+            &
+            $\cdots$
+            &
+            \centering
+            \begin{subfigure}[c]{0.3\textwidth}
+                \centering
+                \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology3.tex}}
+                \label{method net, c}
+            \end{subfigure}
+
+            \end{tabular}
+            \caption{Example sequence of networks.}
+            \label{method nets}
+
+        \end{figure}
         %representations of temp nets as adj lists
@@
 
-        \subsubsection{Applications}
+        \subsection{Applications}
         Temporal networks are present in many areas of research interest, ranging from symptom interactions in mental health\cite{jordan2020current,contreras2020temporal}, to epidemiology\cite{masuda2013predicting}, protein interactions\cite{lucas2021inferring,jin2009identifying}, and social networks\cite{moinet2015burstiness,hanneke2010discrete}.
@@
         % intro to paper as attempt to model node state
-        In \cite{KARIMI20133476}\cite{KARIMI20133476}, the \Citeauthor{KARIMI20133476} look to model the change in node state while the network structure changes.
+        In \Citeauthor{KARIMI20133476}\cite{KARIMI20133476}, \Citeauthor{KARIMI20133476} look to model the change in node state while the network structure changes.
 
@@
         % temp net representation
-        In this case the \Citeauthor{sanna2021link} represent the temporal network as a series of adjacency matrices, each matrix representing an observation of the changing network.
+        In this case \Citeauthor{sanna2021link} represent the temporal network as a series of adjacency matrices, each matrix representing an observation of the changing network.
 
@@
 
-    \subsection{UDEs and NNDEs}
+    \section{UDEs and NNDEs}
         % Justification for DEs being useful
@@
         % Can use a new NN structure to make this framework very general
-        Our aim for this framework to be as general as possible and note that there may not yet be enough domain knowledge to perform traditional differential equation modelling to the desired accuracy.
+        Our aim for this framework is to be as general as possible and note that there may not yet be enough domain knowledge to perform traditional differential equation modelling to the desired accuracy.
 For example in network ecology models can be useful, but not perfect.
@@
 
-        \subsubsection{Theory}
+        \subsection{Theory}
 
@@
 
-        \subsubsection{Applications}
+        \subsection{Applications}
             Whilst there has been much interest in implementing UDEs and NNDEs, much of this work has been focussed on physics informed neural network and physics informed neural ordinary differential equations (PINNs and PINODEs) \cite{karniadakis2021physics,GAO2021110079,krishnapriyan2021characterizing,roehrl2020modeling}, and on improving modelling of fluids \cite{mahmoudabadbozchelou2021data,nguyen2022physics}.
@@
 
-    \subsection{Symbolic Regression}
+    \section{Symbolic Regression}
         % What is symbolic regression
@@
         % Examples of use of genetic programming
-        For example, both \Citeauthor{schmidt2009distilling,bongard2007automated} test their methods' capacity for obtaining a functional equation with physical simulation data, various pendula specifically.
+        For example, both \Citeauthor{schmidt2009distilling}\cite{schmidt2009distilling}, and \Citeauthor{bongard2007automated}\cite{bongard2007automated} test their methods' capacity for obtaining a functional equation with physical simulation data, various pendula specifically.
 A ``meaningful'' equation in this case may be an equation that conserves momentum.
@@
         % Expalaination of schmidt
-        Examples of genetic programming include discovering equations governing the movement of simple harmonic and chaotic double pendula from data\cite{schmidt2009distilling}.
-In \Citeauthor{schmidt2009distilling}, the authors present an evolutionary algorithm to generate multiple candidate functions that approximate the partial derivatives of each variable that are calculated directly from the data.
+        Examples of genetic programming include discovering equations governing the movement of simple harmonic and chaotic double pendula from data.
+In \Citeauthor{schmidt2009distilling}\cite{schmidt2009distilling}, the authors present an evolutionary algorithm to generate multiple candidate functions that approximate the partial derivatives of each variable that are calculated directly from the data.
 
@@
         In \Citeauthor{SciML_C_Rak}\cite{SciML_C_Rak}, the authors demonstrate that by using symbolic regression to find a functional equation of our model, as opposed to just a UDE, we can improve the accuracy of extrapolating.
-\end{section}
-
-\begin{section}{Methodology}
+\end{chapter}
+
+\begin{chapter}{Methodology}
 
@@
 
-        \begin{figure}
-            \centering
-            \begin{subfigure}[c]{1\textwidth}
-                \begin{tabular}{llll}
-                \begin{subfigure}[c]{0.3\textwidth}
-                    \centering
-                    \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology1.tex}}
-                    \label{method net, a}
-                \end{subfigure}
-                &
-                \centering
-                \begin{subfigure}[c]{0.3\textwidth}
-                    \centering
-                    \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology2.tex}}
-                    \label{method net, b}
-                \end{subfigure}
-                &
-                $\cdots$
-                &
-                \centering
-                \begin{subfigure}[c]{0.3\textwidth}
-                    \centering
-                    \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology3.tex}}
-                    \label{method net, c}
-                \end{subfigure}
-
-                \end{tabular}
-                \caption{Example sequence of networks.}
-                \label{method nets}
-
-            \end{subfigure}
+        \begin{figure}{H}
+            \centering
 
@@
                 \end{tabular}
-                \caption{Sequence of sparse adjacency matrices associated with the networks in \autoref{method nets}.}
+                \caption{Sequence of sparse adjacency matrices associated with the networks in \cref{method nets}.}
                 \label{method adjacency}
@@
                 \end{tabular}
-
+                \caption{Sequence of truncated SVDs associated with the networks in \cref{method nets}.}
+                \label{method embed}
             \end{subfigure}
@@
                         \includegraphics[width=\linewidth]{../Code/Plots/examples/plot 1.png}
-                        \label{}
+
                     \end{subfigure}
@@
                         \includegraphics[width=\linewidth]{../Code/Plots/examples/plot 2.png}
-                        \label{}
+
                     \end{subfigure}
@@
                         \includegraphics[width=\linewidth]{../Code/Plots/examples/plot 3.png}
-                        \label{}
+
                     \end{subfigure}
@@
                 \end{tabular}
-                \caption{Example sequence of networks.}
-                \label{method nets}
+                \caption{Sequence of embedded points associated with the networks in \cref{method nets}.}
+                \label{method plots}
 
@@
 
-    \subsection{Singular Value Decomposition and Random Dot Product Graphs}
+    \section{Singular Value Decomposition and Random Dot Product Graphs}
             \label{svd}
@@
             % Supposed to be how to interpret this as RDPG but is bad
-            The approximation of $A$ is defined as $\hat A$ and is given by \autoref{approx} can be interpreted as a graph where the entry $(i,j)$ of the matrix is the probability that an edge $(i \leftrightarrow j)$ exists.
-This approximation of $A$ is an RDPG\cite{athreya2017statistical}.
+            The approximation of $A$ is defined as $\hat A$ and is given by \cref{approx} can be interpreted as a graph where the entry $(i,j)$ of the matrix is the probability that an edge $(i \leftrightarrow j)$ exists.
+This approximation $\hat A$ is an RDPG\cite{athreya2017statistical}.
+
+            Using an RDPG lets us model the probabilities of edges existing as continuous variables, as opposed to the discontinuous observations themselves.
+A benefit of using an SVD to create the RDPG, is that, to model the probabilities of $\hat A$, we can model the change of $\hat L$ and $\hat R$ separately.
+This is useful because the rows of the matrices $\hat L$ and $\hat R$ can be viewed as vector points in a $d$-dimensional space, where $d$ is the number of singular values we take for our SVD truncation.
+Viewing $\hat L$ and $\hat R$ as a collection of vector points allows us to change the problem of modelling changing matrices to a problem of modelling a dynamical system.
+This modelling can be accomplished by finding an appropriate DE.
+
+            % SVD can give a latent space embedding
+            The SVD can be considered to give a latent space representation of the matrix\cite{hoff2002latent}.
+That is, in this space similar nodes in the network are mapped to similar points in space.
+A visual representation of this process can be seen in \cref{framework illustration}.
 
@@
 
-            % SVD can give a latent space embedding
-            The SVD can be considered to give a latent space representation of the matrix\cite{hoff2002latent}.
-That is, the rows of the matrices $\hat L,\hat R$ can be viewed as vector points in a $d$-dimensional space, where $d$ is the number of singular values we take for our SVD truncation.
-In this space similar nodes in the network are mapped to similar points in space.
-A visual representation of this process can be seen in \autoref{framework illustration}.
-
             % Explicit process for how we process our data
-            When obtaining the RDPGs for our temporal network, we take each network observation \autoref{method nets} and represent them in the form of an adjacency matrix \autoref{method adjacency}.
+            When obtaining the RDPGs for our temporal network, we take each network observation \cref{method nets} and represent them in the form of an adjacency matrix \cref{method adjacency}.
 We then use a truncated singular value decomposition to reduce the dimensionality of our adjacency matrices\cite{golub1971singular}.
@@
 
-    \subsection{Neural Network Differential Equation}
+    \section{Neural Network Differential Equation}
         Once we have the SVD embedding of points, we look to model the trajectories of a target point.
@@
 
-        From \autoref{UDE} our problem can be represented as the UDE:
+        From \cref{UDE} our problem can be represented as the UDE:
         \begin{align}
@@
 
-    \subsection{Symbolic Regression}
+    \section{Symbolic Regression}
         With our trained NNDE, we have a black box that approximates the system that governs the movement of the target node in the embedded space.
-To make this more interpretable.
-We then look to approximate this black box into a combination of known functions using symbolic regression\cite{pysr}.
-
-        We use the genetic programming algorithm found in \cite{pysr}. The process for which can be seen in \autoref{symbreg}.
+To make this more interpretable, we then look to approximate this black box into a combination of known functions using symbolic regression\cite{pysr}.
+
+        We use the genetic programming algorithm found in \cite{pysr}. The process for which can be seen in \cref{symbreg}.
 
@@
 
-    \subsection{Reconstructing the Temporal Network}
-        To recover a final prediction of the edges of $u$, we multiply the point vector of $u$ with the matrix $R'$.
-This gives a vector of probabilities of connections between the target node and the rest of the network.
+    \section{Reconstructing the Temporal Network}
+        $u$ the first row of the matrix $\hat L$.
+By taking $u\hat R'$, this is equivalent to finding $\hat A = \hat L \hat R'$ and looking at $\hat A_{1\cdot}$.
+Hence, to recover a final prediction of the edges of $u$, we take:
+        \begin{align}
+            p &= u \hat R'
+        \end{align}
+        This gives a vector $p$ of probabilities of connections between the target node and the rest of the network.
 As the results can be interpreted as a probability, the most likely graph is given by setting any entry with a value of $0.5$ or higher to one (predict that the edge exists), and setting any entry with a value of less than $0.5$ to zero (predict that an edge does not exist).
-\end{section}
-
-\begin{section}{Data}
+\end{chapter}
+
+\begin{chapter}{Data}
     In this paper we simulate three temporal sequences of undirected graphs.
@@
 For each sequence we train the model on the first 25 time steps and compare the predictions for the next 15 time steps.
-For clarity, each diagram \autoref{2community train series} \autoref{longTail train series} \autoref{3community train series} has been simplified and illustrates the movement of the target node in each sequence.
+For clarity, \cref{2community train series,longTail train series,3community train series} have been simplified and illustrates the movement of the target node in each sequence.
 
@@
 
-    \subsection{Two Community System}
+    \section{Two Community System}
         The 2 community network has communities of size 40 and 50, each of which are fully connected.
 The target node is initially fully connected to the 50 node community.
-In our simplified diagram \autoref{2community train series, a} the 50 node community is represented by the 5 fully connected nodes, while the 40 node community is represented by the 4 node component.
-At each time step one edge is removed between the target node and the larger community and replaced with an edge between the target node and the smaller community \autoref{2community train series, b}.
-This process is then continued \autoref{2community train series, c} for thirty-five time steps to generate our training and test data.
-Once we have this data in the form of a sequence of adjacency matrices, we find the singular value decomposition using the framework described in \autoref{svd}.
+In our simplified diagram \cref{2community train series a} the 50 node community is represented by the 5 fully connected nodes, while the 40 node community is represented by the 4 node component.
+At each time step one edge is removed between the target node and the larger community and replaced with an edge between the target node and the smaller community \cref{2community train series b}.
+This process is then continued \cref{2community train series c} for thirty-five time steps to generate our training and test data.
+Once we have this data in the form of a sequence of adjacency matrices, we find the singular value decomposition using the framework described in \cref{svd}.
 
@@
                 \caption{$t=1$}
-                \label{2community train series, a}
+                \label{2community train series a}
             \end{subfigure}
@@
                 \caption{$t=2$}
-                \label{2community train series, b}
+                \label{2community train series b}
             \end{subfigure}
@@
                 \caption{$t=3$}
-                \label{2community train series, c}
+                \label{2community train series c}
             \end{subfigure}
@@
 Notably, the movement in the two community system may be difficult for the neural network to learn because opposite sets of inputs need to result in the same output.
-In a simplified version of this system with only the nearest node as input, the input for the model begins as the position of the larger community at roughly $(0,-1)$ \autoref{2community series}.
+In a simplified version of this system with only the nearest node as input, the input for the model begins as the position of the larger community at roughly $(0,-1)$ \cref{2community illustration}.
 This input needs to move the target towards the top left.
@@
 
-    \subsection{Long Tail System}
+        \begin{figure}{H}
+            \foreach \i/\j in {1/0,21/20,40/40} {%
+                \begin{subfigure}[p]{0.4\textwidth}
+                    \includegraphics[width=\linewidth]{../Code/Plots/Test Only/2communities/2communities \i \space illustration.png}
+                    \caption{$t=\j$}
+                    \label{2community illustration \i}
+                \end{subfigure}\quad
+            }
+            \caption{2 Community test series. This series shows the movement of the target node within the SVD embedding.}
+            \label{2community illustration}
+        \end{figure}
+
+    \section{Long Tail System}
         \label{longtaildata}
-        In the long tail network \autoref{longTail train series}, we have a long chain with 50 nodes and a fully connected component with forty nodes at one end of the chain.
+        In the long tail network \cref{longTail train series}, we have a long chain with 50 nodes and a fully connected component with forty nodes at one end of the chain.
 This is used to orient the embedding and model.
@@
 With a large, connected group at one end however, that group will always be aligned with itself and so the rest of the chain will also be aligned properly.
-The target node starts attached to the node that is attached to this large component \autoref{longTail train series, a}.
-At each time step the target node move one node further down the tail \autoref{longTail train series, b}.
-Again, this is repeated to generate the training and test data \autoref{longTail train series, c}.
+The target node starts attached to the node that is attached to this large component \cref{longTail train series a}.
+At each time step the target node move one node further down the tail \cref{longTail train series b}.
+Again, this is repeated to generate the training and test data \cref{longTail train series c}.
         \begin{figure}[H]
@@
                 \caption{$t=1$}
-                \label{longTail train series, a}
+                \label{longTail train series a}
             \end{subfigure}
@@
                 \caption{$t=2$}
-                \label{longTail train series, b}
+                \label{longTail train series b}
             \end{subfigure}
@@
                 \caption{$t=3$}
-                \label{longTail train series, c}
+                \label{longTail train series c}
             \end{subfigure}\\
@@
 
-    \subsection{Three community System}
+    \section{Three community System}
     We also simulate a sequence with three communities.
 The communities have sizes 40, 35, 30 and have 25, 24, and 23 edges to the target node respectively.
-In \autoref{3community train series} the communities have been simplified to have sizes of 5, 4, and 3.
-The target node starts connected to all of these communities with each community having a different number of edges \autoref{3community train series, a}.
-The community with the fewest edges between the target node will have one edge removed at each time step \autoref{3community train series, b}, and this process is repeated to create the required number of time steps \autoref{3community train series, c}.
+In \cref{3community train series} the communities have been simplified to have sizes of 5, 4, and 3.
+The target node starts connected to all of these communities with each community having a different number of edges \cref{3community train series a}.
+The community with the fewest edges between the target node will have one edge removed at each time step \cref{3community train series b}, and this process is repeated to create the required number of time steps \cref{3community train series c}.
     \begin{figure}[H]
@@
             \caption{$t=1$}
-            \label{3community train series, a}
+            \label{3community train series a}
         \end{subfigure}
@@
             \caption{$t=2$}
-            \label{3community train series, b}            
+            \label{3community train series b}            
         \end{subfigure}
@@
             \caption{$t=3$}
-            \label{3community train series, c}
+            \label{3community train series c}
         \end{subfigure}
@@
 
-\end{section}
-
-\begin{section}{Results and Discussion}
-    \subsection{Embedding Prediction}
+\end{chapter}
+
+\begin{chapter}{Results and Discussion}
+    \section{Embedding Prediction}
         For each of these systems, we took embedded the temporal network in two dimensions at each time step.
@@
 
-        When we do this for the SVD, NN, and symbolic regression, we get \autoref{loss_table}.
-        \begin{figure}
+        When we do this for the SVD, NN, and symbolic regression, we get \cref{loss_table}.
+        \begin{table}
             \begin{center}
@@
                 \label{loss_table}
-        \end{figure}
-
-        As can be seen in \autoref{loss_table}, the symbolic regression model performed better for both the 2 and 3 community system.
+        \end{table}
+
+        As can be seen in \cref{loss_table}, the symbolic regression model performed better for both the 2 and 3 community system.
 However, for the long tail system the symbolic regression model performed notably worse.
@@
 
-    \subsection{Further Exploration}
-        In fig \autoref{2community series}, \autoref{longtail series},\autoref{3community series} the purple points are the embedded coordinates of the node in each of the communities.
+    \section{Further Exploration}
+        In this section, we study the long tail, and 2 and 3 community systems. 
+        In \cref{2community series,longtail series,3community series} we identify the embedded coordinates of each non-target node with a purple point in the Cartesian plane.
 Each cluster is one separate community.
-The green point is the true coordinate of the embedded target node at each time step.
-The blue point is our neural network model prediction at each time step.
-The orange point is the symbolic regression prediction.
+The green point identifies the true coordinate of the embedded target node at each time step.
+The blue point identifies the coordinate of the neural network model prediction at each time step, and the orange point identifies the symbolic regression prediction.
 
@@
 
-        As the time progresses, we see the true node move from one community cluster to the other.
-This is because, at the beginning of the training phase, the target node starts as very similar to the first community (as it has many connections with nodes in that community) and as time progresses, it gradually becomes less and less similar to the first community and more similar to the second (as the edges between the target node and the first community are replaced with edges to the second community).
+        In \cref{2community illustration}, as the time progresses, we see the true node move from one community cluster to the other.
+This is because, at the beginning of the training phase when $(t=0)$, the target node starts as very similar to the first community (as it has many connections with nodes in that community) and as time progresses, it gradually becomes less and less similar to the first community and more similar to the second (as the edges between the target node and the first community are replaced with edges to the second community).
 Because the SVD embeds nodes with many of the same connections close to each other, we see the target node move towards the second community.
 
-        \subsubsection{2 Community}
+        \subsection{2 Community}
             \begin{figure}
-                \foreach \i in {3,6,9,12,15} {%
+                \foreach \i/\j in {3/28,6/31,9/34,12/37,15/40} {%
                     \begin{subfigure}[p]{0.4\textwidth}
                         \includegraphics[width=\linewidth]{../Code/Plots/Test Only/2communities/2communities \i \space small net.png}
-                        \caption{t=\i}
+                        \caption{$t=\j$}
                         \label{2community series \i}
@@
             \end{figure}
-            In \autoref{2community series}, we see both the neural network model and the symbolic regression models follow quite closely to the target node throughout the test process.
-As we saw in \autoref{loss_table}, the NN model performs slightly worse than the symbolic regression model.
+            In \cref{2community series}, we see both the neural network model and the symbolic regression models follow quite closely to the target node throughout the test process.
+As we saw in \cref{loss_table}, the NN model performs slightly worse than the symbolic regression model.
 This improvement of symbolic regression was present throughout the test period.
@@
 
-        \subsubsection{Long Tail}
+        \subsection{Long Tail}
             \begin{figure} 
-                \foreach \i in {3,6,9,12,15} {%
+                \foreach \i/\j in {3/28,6/31,9/34,12/37,15/40} {%
                     \begin{subfigure}[p]{0.4\textwidth}
                         \includegraphics[width=\linewidth]{../Code/Plots/Test Only/longTail/longTail \i \space small net.png}
-                        \caption{t=\i}
+                        \caption{$t=\j$}
                         \label{longtail series \i}
@@
             \end{figure}
-            In \autoref{longtail series} we see the true embedding of the target node move from one arm to the other between the time steps 9 and 12.
+            In \cref{longtail series} we see the true embedding of the target node move from one arm to the other between the time steps 9 and 12.
 It is clear that neither the symbolic regression model nor the neural network model capture this movement.
 
-            From \autoref{loss_table}, we see that the NN model had a higher accuracy than the symbolic regression.
+            From \cref{loss_table}, we see that the NN model had a higher accuracy than the symbolic regression.
 However, the NN model does not follow the true node; instead it stays in relatively the same spot, as opposed to the symbolic regression model, which does move.
@@
 
-            The solutions to this symmetry in this problem would be to break the symmetry by including the absolute position of the target node as input for the model, or to have multiple time steps as input.
+            To solve this problem we could break the symmetry by including the absolute position of the target node as input for the model, or to have multiple time steps as input.
 
             Another potential reason for the poor behavior could be that the embedding of the temporal network does not contain enough information to train a NNDE model.
-This is discussed in \autoref{longtaildata}.
-
-        \subsubsection{Three Community}
+This is discussed in \cref{longtaildata}.
+
+        \subsection{Three Community}
             \begin{figure}
-                \foreach \i in {3,6,9,12,15} {%
+                \foreach \i/\j in {3/28,6/31,9/34,12/37,15/40} {%
                     \begin{subfigure}[p]{0.4\textwidth}
                         \includegraphics[width=\linewidth]{../Code/Plots/Test Only/3community/3community \i \space small net.png}
-                        \caption{t=\i}
+                        \caption{$t=\j$}
                         \label{3community series \i}
@@
             \end{figure}
-            In \autoref{3community series} we see the symbolic regression model move in roughly the same direction as the target node.
+            In \cref{3community series} we see the symbolic regression model move in roughly the same direction as the target node.
 The NN model however, moves quickly towards the bottom left, away from the target node.
@@
 
-    \subsection{Summary}
+    \section{Summary}
       In the 2 and 3 community systems, we see that symbolic regression improved the accuracy of the predictions across all time steps when compared to the NN model.
@@
 
-\end{section}
-
-\begin{section}{Code}
-    \subsection{Summary}
+\end{chapter}
+
+\begin{chapter}{Code}
+    \section{Summary}
         The idea of this code is to provide a foundation for a streamline research into temporal network modelling.
@@
 
-    \subsection{Statement of Need}
+    \section{Statement of Need}
         Throughout this thesis, we have demonstrated that temporal networks are found in many different areas, that, on small networks, temporal progression of embedded nodes can be modelled with NNDEs, and that there are still problems to be overcome.
@@
 
-    \subsection{Package Methods}
+    \section{Package Methods}
         In the package \cite{DotProductGraphs}, I created code for constructing:
@@
 
-    \subsection{Future Work}
+    \section{Future Work}
         The current TNE structure is not yet GPU compatible. We plan to remedy this as well as include support for constructing a TNE from Graph.jl and MetaGraph.jl objects.
 
-\end{section}
-
-\begin{section}{Conclusion}
+\end{chapter}
+
+\begin{chapter}{Conclusion}
     In this thesis, we proposed a novel framework for modelling temporal networks.
@@
 This has been a proof of concept for this framework; we believe future work can dramatically improve the understanding and modelling of this framework.
-\end{section}
+\end{chapter}
 

### 2023-06-12 Code/PlottingCode/plotSltn.jl
cleaned plots

@@ -34,8 +34,8 @@ sltn = readdlm("./Code/Solutions/$net_name big net test only.csv", ',')
 
 t_data[1][:AL]
 
-for i in 1:length(t_data)
-    pts = t_data[i][:AL]#get_embedding([sltn_sym_reg[:,i]'; t_data[i+datasize]], sltn[:,i])
+for i in 1:length(t_data)-datasize
+    pts = t_data[i+datasize][:AL]#get_embedding([sltn_sym_reg[:,i]'; t_data[i+datasize]], sltn[:,i])
     
     #traces0 = PlotlyJS.scatter(x=[sltn[p1,i]], y=[sltn[p2,i]], mode="markers", name="Neural Network Pred", marker_size=12)
     #traces1 = PlotlyJS.scatter(x=[sltn_sym_reg[p1,i]], y=[sltn_sym_reg[p2,i]], mode="markers", name="Symbolic Regression Pred", marker_size=12)

### 2023-06-12 Code/structs/test.jl

@@ -13,8 +13,11 @@ t = TemporalNetworkEmbedding(A, 2)
 
 using PlotlyJS
 i = 3
+layout = Layout(xaxis=attr(showgrid=false),yaxis=attr(showgrid=false))
 trace = scatter(x=t[i,:AL][:,1], y=t[i,:AL][:,2], mode="markers")
-plot(trace)
+trace["marker"] = Dict(:size => 12)
+
+plot(trace, layout)
 PlotlyJS.savefig(plot(trace), "./Code/Plots/examples/plot $i.png")
 
 t.AL

### 2023-10-01 Code/main_script.jl
Renaming folders

@@ -17,10 +17,10 @@ import DiffEqFlux: NeuralODE
 # Things that are important:
 # embedding dim, initial vec for SVD, amount of data
 CUDA.allowscalar(false)
-include("../_Modular Functions/helperFunctions.jl")
-include("../_Modular Functions/loadGlobalConstants.jl")
-include("../_Modular Functions/constructNN.jl")
-include("../_Modular Functions/NODEproblem.jl")
+include("_Modular Functions/helperFunctions.jl")
+include("_Modular Functions/loadGlobalConstants.jl")
+include("_Modular Functions/constructNN.jl")
+include("_Modular Functions/NODEproblem.jl")
 
 global_consts("longTail", (182,2))
 device = Lux.cpu

### 2023-10-01 Code/structs/TemporalNetwork.jl

@@ -1,3 +1,0 @@
-struct TemporalNetwork
-    A::AbstractArray
-end

### 2023-10-01 Code/structs/constructRDPG.jl

@@ -1,16 +1,0 @@
-using LinearAlgebra
-
-function constructRDPG(TempNet::TemporalNetworkEmbedding; tsteps=false)
-    # p ∈ s, n, t
-    # pR' = a
-    # round(a)
-    if typeof(tsteps)==Bool
-        tsteps = 1:length(TempNet)
-    end
-
-
-    Ls = [TempNet[t][:AL] for t in tsteps]
-    Rs = [TempNet[t][:AR]' for t in tsteps]
-
-    rdpg = Ls.*Rs
-end

### 2025-08-07 paper/paper.tex
add latex stuff

--- 2023-06-06 Conference Submission/DraftDoc.tex
@@
 \usepackage{array}
+\usepackage{cleveref}
 \addbibresource{bibliography.bib}
 \usepackage{hyperref,thmtools}
+%\usepackage{chngcounter}
+
+\usetikzlibrary{decorations.markings}
+\usetikzlibrary{arrows,automata}
+\usetikzlibrary{positioning}
+\usetikzlibrary{arrows.meta,positioning}
+
+\counterwithin{figure}{chapter}
+\counterwithin{section}{chapter}
+\counterwithin{table}{chapter}
+\counterwithin{subsection}{section}
+
 \linespread{1.5}
-
+\let\cleardoublepage\clearpage
 % Override ugly default link
@@
 \begin{document}
-
-\begin{section}{Introduction}
-    Temporal networks are networks whose nodes and edges change in time. In this thesis we look to model temporal networks. That is, describe the temporal network using mathematical language. 
-    % Why temp nets are important
-    The modelling of temporal networks is an important task in many real world applications including symptom interactions for mental health \cite{jordan2020current,contreras2020temporal}, epidemiology \cite{masuda2013predicting}, and protein interactions \cite{lucas2021inferring,jin2009identifying}.
-
-    % Temp nets are dynam systs
-    Temporal networks can be seen as a system in which points, in our case nodes in a network, whose states, the edges connecting them, that vary dependent in time, a dynamical system.
-
-    % Hard to find dynam systs because of discrete events 
-    Discovering the underlying equations governing these dynamical systems proves challenging.
-That is because changes in network structure are typically observed in the form of discrete jumps from one state to another, for example an edge between two nodes not being observed at the first time step then being observed at the next.
-
-    % We are proposing a solution
-    In this thesis, we propose a hybrid statistical and deep learning framework.
-That is a framework in which a neural network is used to model probabilistic values of the temporal network.
-This framework allows us to model temporal networks as continuous-time dynamical systems, discover a fitting set of differential equations describing it, and, exploiting that discovery, predict the time evolution of a network.
-
-    % DEs are useful for modelling interacting states
-    Differential equations are useful for modelling systems where the state of one variable can effect the trajectories of other variables.
-
-    % Temp nets have interacting states 
-    We observe this behavior in temporal networks; nodes' connections within the network can influence the observation of edges between other nodes, for example the phenomenon observed in \cite{newman2001clustering,capocci2006preferential}, where a node is more likely to gain the connections the more connections it has (preferential attachment).
-With this in mind we might wish to draw on the rich mathematical literature of differential equation modelling.
-
-    % Temp net events are discrete
-    In the common representation of networks as binary-valued adjacency matrices, matrices where the observation, or lack thereof, of an edge is represented as a 1 or 0 respectively, the events recorded in a temporal sequence of networks correspond to the appearance or the disappearance of link.
-
-    % Difficult to model discrete events
-    Because of the discrete nature of events, directly modelling the temporal networks as dynamical systems would require us to handle discrete jumps.
-    The topological nature of temporal networks, and the discontinuous character of their temporal evolution, make it challenging to use differential equations techniques.
-
-    % We propose a solution
-    Here, we overcome the discreteness problem by interpreting networks as a well established statistical model for complex networks, that embeds nodes in a continuous, low-dimensional metric space by using a truncated singular value decomposition (Random Dot Product Graphs\cite{athreya2017statistical}).
-In this way we translate the hard problem of modelling discrete events in the space of networks to the easier problem of modelling continuous change in the embedding space.
-
-    % Our solution is interpretable because we use symb reg
-    We then define and use systems of Neural Network Differential Equations (NNDE)\cite{SciML_C_Rak} to approximate the time evolution of the embedding space, and symbolic regression techniques to discover the functional form of the fitted NNDEs.
-These functional forms are interpretable (as they read as classic differential equations) and allow us to predict forward in time the evolution of the temporal networks.
-
-    % We propose a solution
-    In this manuscript, we show that the temporal network prediction problem can be successfully re-interpreted as a dynamical system modelling problem by taking the singular value decomposition of a sequence of adjacency matrices and training a NNDE to model an approximation to the underlying differential equation.
-We then go on to create a symbolic equation of this approximation.
-
-    % We will do some small tests on the proposed framework
-    We apply our proposed framework to three small example temporal networks with the hope of exploring the limitations and strengths of the proposed framework.
-
-    % The framework can and should be tweaked to make it optimised
-    The framework we are introducing is extremely flexible, and our research regarding the optimal structure of the Neural Networks used for the NNDEs is just started.
-    We are confident that future research can identify more fitting Neural Network structures than the simple one adopted here.
-    For this reason, we did not yet attempt to benchmark our model against other classic temporal network prediction methods.
-
-    % The framework can be applied to lots of fields
-    As it is completely general, we believe that the framework we are introducing can be usefully applied to areas of medicine, especially protein interaction networks; population dynamics for network ecology; and social network modelling.
-In particular, we discuss how specific domain knowledge relative to the prediction scenario can be taken into account, moving from NNDEs to Universal Differential Equations.
-\end{section}
-
-\begin{section}{Literature Review}
-
-    \subsection{Temporal Networks}
-        % Use of temp nets
-        Temporal networks are used to describe a series of interactions across time.
-        A temporal network $G$ is defined as:  
-        \begin{align}
-            G=\{ {_t} G=({_t} N, {_t} E)\} _{t \in 1\ldots T } 
-        \end{align}
-        $_t x \in {_t} N, {_t} e\in {_t} E$, where ${_t} x, {_t} e$ are nodes and edges at time $t$ respectively, and ${_t} N, {_t} E$ are the sets of nodes and edges at time $t$ respectively.
-        An example of this can be found in \autoref{method nets}.
-
-        %representations of temp nets as adj lists
-        This can be represented in many ways, for example as a series of interactions.
-The series of interactions is generally represented as a list of tuples containing the node that interacted and the time that the interaction took place.
-        \begin{align}
-            G=\{(i, j, t)|\space i,j\in {_t} N, (i\leftrightarrow j)\in {_t}E \}
-        \end{align}
-
-        % representation of temp nets as adj mats
-        A temporal network can also be represented as a sequence of adjacency matrices.
-In the representation of a series of adjacency matrices, the columns and rows of the matrix each refer to each of the nodes.
-In this way, if an edge exists between nodes $i$ and $j$, the entry $(i,j)$ of the adjacency matrix will be 1; if an edge does not exist the entry will be 0.
-        \begin{align}
-            _t G &= {_t} A\\
-            _t A_{ij} &=  
-            \left\{
-                \begin{array}{ll} 
-                1 & (i\leftrightarrow j)\in {_t} E\\
-                0 & otherwise
-                \end{array}
-            \right.
-        \end{align}
-        The row $_t A_{i\cdot}$ describes the outgoing edges of the node $i$, while the column $_t A_{\cdot j}$ describes the incoming edges of the node $j$.
-
-        % Uses of temp nets
-        Temporal networks are present in many areas of research interest, ranging from symptom interactions in mental health\cite{jordan2020current,contreras2020temporal}, to epidemiology\cite{masuda2013predicting}, protein interactions\cite{lucas2021inferring,jin2009identifying}, and social networks\cite{moinet2015burstiness,hanneke2010discrete}.
-
-        % Overview of modelling attempts
-        Generally attempts to model temporal networks either model the change in node state or the change in network structure.
-
-        The node state describes some information about that node:
-        \begin{align}
-            _t x &= (m_1,\ldots, m_p)
-        \end{align}
-        Where $m_i$ is some metadata about the node $_t x$.
-
-        An example of modelling the change in a node state could be the severity of a symptom at a given time, as in \Citeauthor{contreras2020temporal}\cite{contreras2020temporal}.
-Where the node $_t x$ represents the symptom and $m_1$ would represent the severity of that symptom.
-
-        Other effort focus on modelling the changing structure of the network as in \Citeauthor{sanna2021link}\cite{sanna2021link}, which looks to model $_t G$ as a whole.
-
-        % Intro contreras as attempt to model changes in nodes
-        \Citeauthor{contreras2020temporal}\cite{contreras2020temporal} model the change in node state over time while the structure of the network remains constant.
-\Citeauthor{contreras2020temporal} look at the severity of symptoms over time, i.e.
-the state of the nodes, as a temporal network where the network structure remains constant.
-
-        % Contreras methods
-        They use multilevel vector autoregression, a method that finds correlations between the current state of a variable and the states of variables at previous time steps \cite{singer2003applied}, to model how the current symptoms of people with paranoia might predict their future symptoms.
-These models were then used to create three networks that linked symptoms.
-
-        % Focal point of the paper is their temporal network
-        Of particular interest to this thesis is the temporal network created by having a fully connected network of all symptoms including self-loops, where a symptom connects to itself; this self loop comes about from a symptom being correlated with itself from one time step to the next.
-The edge weights represent the extent to which the severity of each symptom at time $(t)$ predicts the severity of itself and other symptoms at time $(t+1)$.
-
-        % Why this is the focal point
-        This framework keeps the overall structure of the network fixed throughout time and so is not particularly flexible, but is extremely human interpretable and can be used to extrapolate and predict into the future.
-
-        % intro to paper as attempt to model node state
-        In \cite{KARIMI20133476}, the \Citeauthor{KARIMI20133476} look to model the change in node state while the network structure changes.
-
-        % How network is represented
-        \Citeauthor{KARIMI20133476} represent their temporal network as a series of interactions (a list of tuples in the form $(i,j,t)$, where $i,j$ are the nodes interacting and $t$ is the time the at which the interaction occurred).
-
-        % what state the paper attempts to model
-        The authors use a model to predict when a node will change from state 0 to state 1, in practice this could represent whether a user of a social network believes a rumour, or an ecological patch being colonised.
-
-        % Model limitation
-        Notably, in their model the node never changes back; this is done to keep the model analytically tractable, but does limit its usefulness in some contexts.
-In this model an organism could not become locally extinct in an ecological patch for example.
-
-        % Methods to model node state
-        To model the change in a nodes' state, the model uses a sliding time window and if the fraction of interactions with nodes of state 1 within that time window exceeds a given threshold, the node switches to state 1 as well.
-
-        % Limitation of model
-        In this work I aim to present a model for predicting the state of a node in the future.
-Instead, \Citeauthor{KARIMI20133476} aim to present a tool for understanding the spread of ideas, viruses, etc.
-within a network.
-
-        % Intro to pasino et al as modelling structure of temp net
-        \Citeauthor{sanna2021link}\cite{sanna2021link} model the change in the structure of a temporal network.
-
-        % temp net representation
-        In this case the \Citeauthor{sanna2021link} represent the temporal network as a series of adjacency matrices, each matrix representing an observation of the changing network.
-
-        % Methods for embedding
-        The authors look to model the structure of edges by using a spectral embedding (SVD).
-A spectral embedding uses the eigenvectors of a network's adjacency matrix to find vectors that represent the nodes of the network.
-The spectral embedding transforms their temporal sequence into a sequence of observations of a latent space.
-
-        % What is a latent space
-        A latent space is a continuous space in which similar nodes (nodes with many of the same neighbours) are positioned near each other.
-In this space nodes are represented as points in a continuous, low dimensional space.
-Another feature of this latent space, is that the dot product of any two points in the space gives us the probability that the nodes related to those points are connected.
-
-        % methods for time series
-        With this series of embeddings, the authors employ a variety of time series techniques to predict the network structure at future time steps.
-
-    \subsection{UDEs and NNDEs}
-        % Justification for DEs being useful
-        In some temporal networks the state of a node might influence the evolution of its neighbours.
-For example, in social networks we often observe the power law distribution of edges, where the more neighbours a node has, the more likely they are to gain more neighbours\cite{zhao2012multi,garg2009evolution}.
-We also see that the state of symptoms (occurrence, severity, and distress), can influence the states of other symptoms in patients undergoing chemotherapy \cite{papachristou2019network,kalantari2022network}, and for mental health disorders \cite{contreras2020temporal}.
-As well as in ecological networks where the interactions of species are often represented as a network, and the populations of one species may influence the population growth of another \cite{elton2001animal,volterra1927variazioni}; that is, the state (in this case the population) of a species (node), may influence the movement of another species.
-
-        % DEs have lots of research
-        With the observation that nodes in real world temporal networks may influence others, differential equations or difference equations seem appropriate for modelling the evolution of nodes as there is a rich body of literature exploring these methods use in modelling interacting variables.
-
-        % The data we have is discrete, which is a problem for DEs
-        One of the issues that the differential equation method encounters is the prevalence of discrete jumps of edges forming and decaying.
-Because of this we may consider exploring the possibility of using difference equations.
-
-        % time is continuous so good to have our model be cont too
-        We note that the progression of the network is generally continuous even if the events happen as discrete jumps.
-Because of this, we may wish to preserve the continuous temporal progression in our model.
-
-        %This approach may overcome the problem of discrete observations, by defining a progression function that will only predict discrete formation or decay of edges\cite{hanneke2010discrete}.
-However, this imposes a significant limitation on the temporal granularity with which we can predict the state of the network.
-We would be limited to the granularity our data is collected at.
-This may be a problem if for example we had a series of weekly or monthly observations of networks we would not be able to predict interactions at each day.
-We can overcome both this limitation and the discrete jump limitation by using random dot product graphs.
-Interpolation may be possible in this case, but we would have no way of knowing if the interpolation had any basis in the real world.
-
-        % passino has discrete data but uses a method to view it as cont
-        Looking at the work of Passino et al.\cite{sanna2021link}, the authors use random dot produce graphs\cite{athreya2017statistical} to approximate a temporal network as a matrix of probabilities of an edge existing between two nodes.
-In contrast to edges, these probabilities can evolve continuously, and so we can use differential equations to generate probabilistic networks at any temporal resolution we require.
-That is, we will be able to model the changes in the probabilities of edges continuous and from this, generate a network at any time step.
-
-        %  we can use the same method we can view data as dynam sys and use DEs
-        Using the method in Passino et al.\cite{sanna2021link}, we can treat the sequence of embeddings as a dynamical system and then use differential equation modelling in a continuous space.
-That is, once we have found a latent space for each network.
-We know that each point in this space refers to a specific node in the network, and so, as the network changes, so too does the position of each of the points in the latent space.
-We then look to model this movement using differential equations.
-
-        % Can use a new NN structure to make this framework very general
-        Our aim for this framework to be as general as possible and note that there may not yet be enough domain knowledge to perform traditional differential equation modelling to the desired accuracy.
-For example in network ecology models can be useful, but not perfect XXX cite XXX.
-Hence, we might wish to build on these models rather than trying to create something entirely new.
-This can be achieved by using this partial domain knowledge using it to create a universal differential equation (UDE) \cite{SciML_C_Rak}.
-
-        \subsubsection{Theory}
-
-            % Overview of why UDEs are useful
-            Developed by \Citeauthor{SciML_C_Rak}\cite{SciML_C_Rak}, Universal Iifferential Equation (UDEs) are a novel neural network architecture that aims to take the best of both traditional neural differential equation modelling and of flexible machine learning approaches to modelling.
-
-            If we consider a comparison to an Ordinary Differential Equation (ODE), the ODE is written as:
-            \begin{align}
-                y(0) &= y_0 \\
-                \frac{dy}{dt}(t)&=f(t,y(t))
-            \end{align}
-
-            The UDE will incorporate some component of $f(t,y(t))\approx \hat f(t,y(t))$, and will learn the difference with a Neural Network (NN) such that:
-            \begin{align}
-                \label{UDE}
-                y(0) &= y_0 \\
-                \frac{dy}{dt}(t)&=\hat f(t,y(t))+NN(t,y(t), \theta)
-            \end{align}
-            Where $\theta$ is a vector of the parameters of the NN.
-            % Structure of UDE
-            UDEs combine domain knowledge in the form of a differential equation, with a neural network. This hybrid machine learning model is then trained on the observed data.
-
-            % Overview of why UDEs are useful
-            Combining the two allows for most of the movement in the data to be captured by the differential equation, which contains the domain knowledge.
-In this way the neural network will only need to learn a theoretically simpler equation, given that a part of the system has already been captured.
-
-            % Why this structure is useful
-            This then allows the neural network to be smaller, require fewer data, and be trained much faster than traditional neural network models.
-Given the flexibility of neural networks, the use of UDEs is natural when modelling a process that is not entirely understood\cite{kidger2022neural}.
-
-            % Software used for coding
-            There is an ecosystem of packages specifically designed for performing machine learning with UDEs.
-The ecosystem is called SciML or scientific machine learning\cite{SciML_C_Rak}.
-Largely, the SciML ecosystem has been optimised for flexibility and efficiency with respect to models available and training performance.
-Given there does not seem to be any other ecosystem with this feature, it seemed like
-            an obvious choice.
-
-        \subsubsection{Applications}
-            Whilst there has been much interest in implementing UDEs and neural ODEs, much of this work has been focussed on physics informed neural network and physics informed ordinary differential equations (PINNs and PINODEs) \cite{karniadakis2021physics,GAO2021110079,krishnapriyan2021characterizing,roehrl2020modeling}, and on improving modelling of fluids \cite{mahmoudabadbozchelou2021data,nguyen2022physics}.
-Alongside this, and given UDEs have gained popularity in the last few years, there have been a number of studies exploring their usefulness in modeling the effect of restrictions due to COVID-19 on the virus' spread \cite{Dandekar2020.04.03.20052084}.
-Although there has been a large amount of research into the usefulness of these types of models, to the best of this author's knowledge they have never been applied to the problem of predicting temporal networks.
-This seems to be a natural fit for UDEs and neural ODEs, given we may know relatively little about the processes that govern the evolution of temporal networks, and any information we do have can be incorporated into the model.
-
-    \subsection{Symbolic Regression}
-        % What is symbolic regression
-        Symbolic regression is a type of analysis that looks to find a relationship between input variables that describe the output variables.
-For symbolic regression, we define a set of equations that may be used to find this relationship.
-The algorithm then generates combinations of these equations to find an expression that matches the output variables.
-Because we define the set of potential equations, the resulting expression is interpretable by humans, as opposed to a NN for example.
-
-        % Why is symbolic regression useful
-        Having interpretable models that capture underlying relations is relevant to all fields of study, and so the applications of symbolic regression are incredibly varied.
-
-        % Where has symbolic regression been used 
-        Various methods of symbolic regression have been use in manufacturing systems, chemical systems, and tumor research\cite{can2011comparison,keith2021combining,yoshihara2013inferring}.
-As well research into improvements is still on going.
-
-        % How is this done
-        This can be achieved in many ways and remains active area of research. One of the most popular algorithms is genetic programming\cite{schmidt2009distilling}.
-
-        % How genetic programming works
-        Genetic programming involves constructing a search tree using a genetic algorithm to yield a potential equation, which may match the data as well as numerically calculated partial derivatives of each of the input variables.
-
-        % Why are the derivatives important
-        Comparing with these derivatives is useful as it helps to ensure that the produced function equations have some grounding in the real world process that generated the data.
-The search tree is then pruned by comparing the partial derivatives of the candidate equation, with partial derivatives calculated from data.
-This process is then iterated many times to generate a suitable equation.
-
-        % What symbolic regression aims to solve
-        The problem that symbolic regression aims to solve is to generate interpretable and ``meaningful'' equations from observed data.
-
-        % Examples of use of genetic programming
-        For example, both \Citeauthor{schmidt2009distilling,bongard2007automated} test their methods' capacity for obtaining a symbolic equation with physical simulation data, various pendula specifically.
-A ``meaningful'' equation in this case would be one that adheres to the laws of physics.
-
-        % Expalaination of schmidt
-        Examples of genetic programming include discovering equations governing the movement of simple harmonic and chaotic double pendula from data\cite{schmidt2009distilling}.
-In this paper the authors present an evolutionary algorithm to generate multiple candidate functions that approximate the partial derivatives of each variable that are calculated directly from the data.
-
-        % Intro to bongard
-        Another approach to symbolic regression can be found in \cite{bongard2007automated}.
-This paper proposes a method to find a symbolic equation that approximates a learned numerical equation rather than directly from data.
-
-        % How does this process work
-        The candidate equation is then tested against the numerical equation in such a way that the difference between the two predictions are maximised.
-The algorithm will generate new initial conditions to find behaviour exhibited by the numerical equation, for example a fixed point, that is not exhibited by the functional equation.
-When a difference is found, the functional equation is adjusted to also exhibit the behaviour of the numerical equation.
-
-        % Limitations of this process
-        Especially when using a neural network model as the numerical equation, it seems these process may not be useful if the initial conditions are outside the scope of the training data.
-
-        % Benefits of combining UDEs and symbolic regression
-        In very recent work, Kidger\cite{kidger2022neural}, demonstrates that, with UDEs, two of the assumptions necessary for symbolic regression can be overcome.
-Those are the necessity for paired observations and derivatives, as well as the assumption that the function can be expressed as a shallow tree of symbolic operations.
-We are modelling a differential equation, and so will have access to the derivatives of our numerical model at any point, as neural networks are easily differentiable.
-
-        % Usefulness of symbolic regression for nnde
-        In \Citeauthor{SciML_C_Rak}\cite{SciML_C_Rak}, the authors demonstrate that using symbolic regression, as opposed to just an NNDE, can improve the accuracy of extrapolating.
-One aspect of this improvement is having accurate numerical derivative to compare to.
-To ensure this, it is important that the data is sampled very frequently.
-This seems integral to the accuracy of the found equation.
-\end{section}
-
-\begin{section}{Methodology}
+\begin{chapter}{Methodology}
 
@@
         We are given a sequence of graphs, and our goal is to predict the next graph in the sequence.
+To achieve this, we reinterpret our temporal network as a sequence of points in a latent space; that is, a space in which similar vertices (ones with many of the same neighbours) are mapped to a similar point in space.
+        We then train a Neural Ordinary Differential Equation (NODE) to approximate the rate of change of the points in this latent space.
+With this numerical equation, we can then use symbolic regression techniques to find a functional equation that matches the numerical equation.
+Using this process we discover an interpretable function that governs the evolution of a temporal network.
 
-        % How we achieve this goal
-        To achieve this, we reinterpret each graph as a sequence of points in a latent space; that is, a space in which similar vertices (ones with many of the same neighbours) are mapped to a similar point in space.
-        We then Train a Neural Network Differential Equation (NNDE) to approximate the rate of change of the points in this latent space.
-With this numerical equation we can then use symbolic regression techniques to find a functional equation that matches the numerical equation.
-Using this process we discover an interpretable function that governs the evolution of a differential equation.
+    \begin{        Initial vector is [1 2 3 4 ... mod 7] (Double check)
+        Initial vector is used to align the vectors but it kind of doesn't work
+section}{Singular Value Decomposition and Random Dot Product Graphs}
+        SVD Calculated with XXX Arpack XXX Julia
+        Each system has 2 singular values
+        L and R are related by [1 0; 0 -1] as the network is not directed (IE the matrix is symetrical) 
+        We only model L and transform it for analysis
+        Reconstruct the RDPG L*(L*transform)'
+    \end{section}
 
-        \begin{figure}
-            \centering
-            \begin{subfigure}[c]{1\textwidth}
-                \begin{tabular}{llll}
-                \begin{subfigure}[c]{0.25\textwidth}
-                    \centering
-                    \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology1.tex}}
-                    \label{method net, a}
-                \end{subfigure}
-                &
-                \centering
-                \begin{subfigure}[c]{0.25\textwidth}
-                    \centering
-                    \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology2.tex}}
-                    \label{method net, b}
-                \end{subfigure}
-                &
-                $\cdots$
-                &
-                \centering
-                \begin{subfigure}[c]{0.25\textwidth}
-                    \centering
-                    \resizebox{.6\width}{!}{\input{SynthDataDiagrams/methodology3.tex}}
-                    \label{method net, c}
-                \end{subfigure}
-
-                \end{tabular}
-                \caption{Example sequence of networks.}
-                \label{method nets}
-
-            \end{subfigure}
-            \begin{subfigure}[c]{1\textwidth}
-                \begin{tabular}{llll}
-                    $\begin{bmatrix}
-                        \cdot & 1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
-                        1 & \cdot & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
-                        1 & 1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot\\
-                        1 & \cdot & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
-                        \cdot & \cdot & 1 & \cdot & \cdot & 1 & 1 & \cdot\\
-                        \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & \cdot\\
-                        \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & 1\\
-                        \cdot & \cdot & \cdot & \cdot & \cdot & \cdot & 1 & \cdot
-                    \end{bmatrix}$
-                    &
-                    $\begin{bmatrix}
-                        \cdot & 1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
-                        1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
-                        1 & 1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot\\
-                        1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
-                        \cdot & \cdot & 1 & \cdot & \cdot & 1 & 1 & \cdot\\
-                        \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & 1\\
-                        \cdot & \cdot & \cdot & \cdot & 1 & \cdot & \cdot & 1\\
-                        \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot
-                    \end{bmatrix}$
-                    &
-                    $\cdots$
-                    &
-                    $\begin{bmatrix}
-                        \cdot & 1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
-                        1 & \cdot & 1 & 1 & \cdot & \cdot & \cdot & \cdot\\
-                        1 & 1 & \cdot & 1 & \cdot & \cdot & \cdot & \cdot\\
-                        1 & 1 & 1 & \cdot & \cdot & \cdot & \cdot & \cdot\\
-                        \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot\\
-                        \cdot & \cdot & \cdot & \cdot & 1 & \cdot & 1 & 1\\
-                        \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot & 1\\
-                        \cdot & \cdot & \cdot & \cdot & \cdot & 1 & 1 & \cdot
-                    \end{bmatrix}$
-
-                \end{tabular}
-                \caption{Sequence of sparse adjacency matrices associated with the networks in \autoref{method nets}.}
-                \label{method adjacency}
-            \end{subfigure}
-
-            \begin{tabular}{llll}
-
-            \end{tabular}
-
-            \caption{Visual illustration of the proposed framework.}
-            \label{framework illustration}
-        \end{figure}
-
-    \subsection{Singular Value Decomposition and Random Dot Product Graphs}
-            \label{svd}
-            % Over view of section
-            In this section we discuss the Singular Value Decomposition (SVD) of a matrix, and its usefulness in creating Random Dot Product Graphs (RDPG).
-
-            % Definition of SVD
-            We define the matrix $A$ to be a real $m \times n$ with $n \le m$. $A$ can be expressed as \cite{forsythe1967computer}:
-            \begin{align}
-                A&=l\sqrt{\Sigma} \sqrt{\Sigma} r' \\
-                A&=L R'
-            \end{align}
-            Where $L, R$ are real valued, orthonormal matrices.
-The columns of $L$ consist of the $n$ largest eigenvectors of $AA'$ and the columns $R$ consist of the eigenvectors of $A'A$.
-$\Sigma$ is a diagonal matrix whose entries are the square root of the positive eigenvalues of $A'A$ in decreasing order.
-
-            % How to reduce problem size
-            In order to reduce the problem size, we can truncate the $L,R$ to the first $d$ columns to yield, $\hat L, \hat R$ such that:
-
-            \begin{align}
-                A &\approx \hat L \hat R' \\
-                \hat A &= \hat L \hat R'
-                \label{approx}
-            \end{align}
-
-            % Supposed to be how to interpret this as RDPG but is bad
-            The approximation of $A$ is defined as $\hat A$ and is given by \autoref{approx} can be interpreted as a graph where the entry $(i,j)$ of the matrix is the probability that an edge $(i \leftrightarrow j)$ exists.
-This approximation of $A$ is an RDPG\cite{athreya2017statistical}.
-
-            % Introduce problem of alignment
-            It is important to note that the SVD is not unique.
-The distances between points will be the same for every embedding, but the orientation may be different, and so, if the SVD of each time step is not aligned, learning will be effectively impossible as we will essentially be trying to model random noise.
-
-            % How to solve alignment problem
-            Here, we can use Procrustes alignment\cite{DotProductGraphs} to align the matrices after they have been generated.
-
-            % SVD can give a latent space embedding
-            The SVD can be considered to give a latent space representation of the matrix\cite{hoff2002latent}.
-That is, the rows of the matrices $\hat L,\hat R$ can be viewed as vector points in a $d$-dimensional space, where $d$ is the number of singular values we take for our SVD truncation.
-In this space similar nodes in the network are mapped to similar points in space.
-A visual representation of this process can be seen in \autoref{framework illustration}.
-
-            % Explicit process for how we process our data
-            When obtaining the RDPGs for our temporal network, we take each network observation \autoref{method nets} and represent them in the form of an adjacency matrix \autoref{method adjacency}.
-We then use a truncated singular value decomposition to reduce the dimensionality of our adjacency matrices\cite{golub1971singular}.
-
-            % Introduce problem of loss from SVD
-            This truncation introduces some loss, but can dramatically reduce the size of our problem.
-\Citeauthor{Runghen2021}\cite{Runghen2021} effectively employ this method to reduce a problem involving over 130,000 visitors to a 6 dimensional latent space, whilst preserving 70\% of the information.
-
-            % What code we use
-            To execute the SVD we use the ARPACK Julia package \cite{lehoucq1998arpack}.
-This package uses an iterative approach to approximate the eigenvectors and singular values of each of our adjacency matrices\cite{lehoucq1996deflation}.
-
-    \subsection{Neural Network Differential Equation}
-        Once we have the SVD embedding of points, we look to model the trajectories of a target point.
-That is, with some input data, point location, distance to neighbours, etc, we want to model the differential equation that governs the movement of a point.
-        % Modelling multiple points
-        Notably this method can be used to model multiple points by simply changing the node being predicted and trained on.
-
-        From \autoref{UDE} our problem can be represented as the UDE:
-        \begin{align}
-            \frac{d \hat A}{dt} &= \hat f(t,\hat A(t)) + NN(t, \hat A, \theta)
-        \end{align}
-        The focus of this thesis is to understand the behaviour of the neural network when modelling temporal neural networks.
-Hence, we set $\hat f(t, \hat A(t))=0 \space \forall t$.
-With this, the problem becomes:
-        \begin{align}
-            \frac{d \hat A}{dt} &= NN(t, \hat A, \theta)
-        \end{align}
-        A special case of a UDE called a Neural Network Differential Equation(NNDE).
-
-        In this thesis, as a proof of concept, we focus on a modelling the change in structure of a single node, referred to as the target node $u$, where $u(t)={_t}\hat L_{1\cdot}$.
-To model $u$ we use the direction vectors from $u$ to its $k$ (15) nearest neighbours in $\hat L$.
-We define the function $K(\hat L(t), k)$ to find the direction vectors of the $k$ nearest neighbours to $u(t)$.
-We use the function $K$ to limit the complexity of our model.
-
-        \begin{align}
-            \frac{du}{dt} &= NN(t, K(\hat L, k), \theta)
-        \end{align}
-
-        Because we are only modelling the movement of a single node, we assume that we have access to the rest of the network structure at every time step for the prediction.
-This would likely not be the case in a real world application, but will allow us to observe some of the strengths and weaknesses of this framework in a controlled setting.
-If we wanted to predict the whole network we would extrapolate out every point and use the dot product of each point to predict the edges.
-
-        Here we train a neural network to approximate the function $g(u(t),t)=NN(u(t),t,\theta)$. Where $\theta$ is the parameters of the neural network.
-
-        To obtain a suitable set of parameters $\theta$, we make use of the SciML ecosystem of packages in the Julia programming language\cite{SciML_C_Rak}.
+    \begin{section}{Neural Ordinary Differential Equation}
+        Used Julia SciML ecosystem
+        Basic copy pasted code 
+        Modelling the whole state
+        Loss function is abs2 sum Data-pred + disabove 1 and below 0 (L*(L*transform)' )
+        NN structure 3 layers 256, 128, 128 celu activation function
+    \end{section}
 
@@
 
-    \subsection{Symbolic Regression}
-        With our trained NNDE, we have a black box that approximates the system that governs the movement of the target node in the embedded space.
-To make this more interpretable.
-We then look to approximate this black box into a combination of known functions using symbolic regression\cite{pysr}.
-
-        We use the genetic programming algorithm found in \cite{pysr}. The process for which can be seen in \autoref{symbreg}.
-
-        \begin{figure}
-            \centering
-            \resizebox{\width}{!}{\input{SynthDataDiagrams/symbreg.tex}}
-            \caption{Illustration of the genetic programming symbolic regression process.}
-            \label{symbreg}
-        \end{figure}
-
-        The fitness of a candidate function is determined by comparing the predicted value to the given data, as well as the derivatives of the candidate equations to numerically found partial derivatives of the data variable.
-
-        For this process we need to define a set of functions which the algorithm will use to generate a tree of functions to find the best approximation to our NNDE with.
-When using this method we are usually required to make two assumptions: that we have paired observations of $u(t), \frac{du}{dt}$, and that the tree of expressions we will need is shallow.
-We will train the symbolic regression on the predictions of the neural network.
-By doing this, we can remove these assumptions\cite{kidger2022neural}.
-
-    \subsection{Reconstructing the Temporal Network}
-        To recover a final prediction of the edges of $u$, we multiply the point vector of $u$ with the matrix $R'$.
-This gives a vector of probabilities of connections between the target node and the rest of the network.
-As the results can be interpreted as a probability, the most likely graph is given by setting any entry with a value of $0.5$ or higher to one (predict that the edge exists), and setting any entry with a value of less than $0.5$ to zero (predict that an edge does not exist).
+    \begin{section}{Symbolic Regression}
+        ???
     \end{section}
 
-\begin{section}{Data}
-    In this paper we simulate three temporal sequences of undirected graphs.
-For each sequence we will be modelling the node in red, we will refer to this as the target node.
-For each sequence we train the model on the first 25 time steps and compare the predictions for the next 15 time steps.
-For clarity, each diagram \autoref{2community train series} \autoref{longTail train series} \autoref{3community train series} has been simplified and illustrates the movement of the target node in each sequence.
-
-    Each model was trained on a neural network with 4 hidden layers (64,8,8,8).
-
-    \subsection{Two Community System}
-        The 2 community network has communities of size 40 and 50, each of which are fully connected.
-The target node is initially fully connected to the 50 node community.
-In our simplified diagram \autoref{2community train series, a} the 50 node community is represented by the 5 fully connected nodes, while the 40 node community is represented by the 4 node component.
-At each time step one edge is removed between the target node and the larger community and replaced with an edge between the target node and the smaller community \autoref{2community train series, b}.
-This process is then continued \autoref{2community train series, c} for thirty-five time steps to generate our training and test data.
-Once we have this data in the form of a sequence of adjacency matrices, we find the singular value decomposition using the framework described in \autoref{svd}.
-
-        Figures obtained from \cite{Emma2023}.
-        \begin{figure}[H]
-            \centering
-            \centering
-            \begin{subfigure}[c]{0.3\textwidth}
-                \centering
-                \resizebox{.6\width}{!}{\input{SynthDataDiagrams/2community1.tex}}
-                \caption{$t=1$}
-                \label{2community train series, a}
-            \end{subfigure}
-            \hfill
-            \centering
-            \begin{subfigure}[c]{0.3\textwidth}
-                \centering
-                \resizebox{.6\width}{!}{\input{SynthDataDiagrams/2community2.tex}}
-                \caption{$t=2$}
-                \label{2community train series, b}
-            \end{subfigure}
-            \hfill
-            \centering
-            \begin{subfigure}[c]{0.3\textwidth}
-                \centering
-                \resizebox{.6\width}{!}{\input{SynthDataDiagrams/2community3.tex}}
-                \caption{$t=3$}
-                \label{2community train series, c}
-            \end{subfigure}
-            \caption{First 3 time steps of the simplified, synthetic 2 community network.
-The red node represents the target node that we are aiming to model.
-The 4 node and 5 node fully connected components represent the 40 and 50 node communities of the sequence respectively.
-At each time step, an edge from the target node to the larger community is replaced with and edge from the target node to the smaller community.}
-            \label{2community train series}
-        \end{figure}
-        The 2 community temporal network was selected to test whether this framework can be used to model a node changing communities in systems where there are no other processes occurring.
-Notably, the movement in the two community system is difficult for the neural network to learn because opposite sets of inputs need to result in the same output.
-In a simplified version of this system with only the nearest node as input, the input for the model begins as the position of the larger community at roughly $(0,-1)$ \autoref{2community series 3}.
-This input needs to move the target towards the top left.
-However, as the sequence progresses, the nearest neighbours will be the small community at roughly $(-1,0)$, which also needs to move the target node towards the top left.
-
-    \subsection{Long Tail System}
-        \label{longtaildata}
-        In the long tail network \autoref{longTail train series}, we have a long chain with 50 nodes and a fully connected component with forty nodes at one end of the chain.
-This is used to orient the embedding and model.
-The SVD does not take into account the index of the individual node in the adjacency matrix; it only distinguishes based on their distance to each other.
-Because of this a chain of nodes, even when aligned, could be flipped when it is embedded.
-That is, between one time step and the next the first node in the chain could be aligned with the last node.
-With a large, connected group at one end however, that group will always be aligned with itself and so the rest of the chain will also be aligned properly.
-The target node starts attached to the node that is attached to this large component \autoref{longTail train series, a}.
-At each time step the target node move one node further down the tail \autoref{longTail train series, b}.
-Again, this is repeated to generate the training and test data \autoref{longTail train series, c}.
-        \begin{figure}[H]
-            \centering
-            \begin{subfigure}[c]{0.3\textwidth}
-                \centering
-                \resizebox{.6\width}{!}{\input{SynthDataDiagrams/longTail1.tex}}
-                \caption{$t=1$}
-                \label{longTail train series, a}
-            \end{subfigure}
-            \hfill
-            \centering
-            \begin{subfigure}[c]{0.3\textwidth}
-                \centering
-                \resizebox{.6\width}{!}{\input{SynthDataDiagrams/longTail2.tex}}
-                \caption{$t=2$}
-                \label{longTail train series, b}
-            \end{subfigure}
-            \hfill
-            \centering
-            \begin{subfigure}[c]{0.3\textwidth}
-                \centering
-                \resizebox{.6\width}{!}{\input{SynthDataDiagrams/longTail3.tex}}
-                \caption{$t=3$}
-                \label{longTail train series, c}
-            \end{subfigure}\\
-            \caption{First 3 time steps of the simplified, synthetic long tail network.
-The red node represents the target node that we are aiming to model.
-The fully connected, 5 node component represents a 50 node community at the end of the long tail.
-At each time step the target node moves one step further along the chain, away from the large community.}
-            \label{longTail train series}
-        \end{figure}
-
-        The long tail network was selected because the SVD performs poorly on highly diagonal matrices; that is matrices with long chains.
-The long tail problem is difficult for the embedding because a large portion of the network is along the off diagonals; meaning that, to get an accurate embedding, the dimension of the embedding would need to be close to the length of the tail.
-As such we wish to see how the framework performs when it is presented with a system that the SVD cannot capture.
-
-    \subsection{Three community System}
-    We also simulate a sequence with three communities.
-The communities have sizes 40, 35, 30 and have 25, 24, and 23 edges to the target node respectively.
-In \autoref{3community train series} the communities have been simplified to have sizes of 5, 4, and 3.
-The target node starts connected to all of these communities with each community having a different number of edges \autoref{3community train series, a}.
-The community with the fewest edges between the target node will have one edge removed at each time step \autoref{3community train series, b}, and this process is repeated to create the required number of time steps \autoref{3community train series, c}.
-    \begin{figure}[H]
-        \centering
-        \centering
-        \begin{subfigure}[c]{0.3\textwidth}
-            \centering
-            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/3community1.tex}}
-            \caption{$t=1$}
-            \label{3community train series, a}
-        \end{subfigure}
-        \hfill
-        \centering
-        \begin{subfigure}[c]{0.3\textwidth}
-            \centering
-            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/3community2.tex}}
-            \caption{$t=2$}
-            \label{3community train series, b}            
-        \end{subfigure}
-        \hfill
-        \centering
-        \begin{subfigure}[c]{0.3\textwidth}
-            \centering
-            \resizebox{.6\width}{!}{\input{SynthDataDiagrams/3community3.tex}}
-            \caption{$t=3$}
-            \label{3community train series, c}
-        \end{subfigure}
-        \caption{First 3 time steps of the simplified, synthetic 3 community networks.
-The red node represents the target node which we aim to model.
-The 3, 4, and 5 node components represent the 30, 35, and 40 node communities respectively.
-At each time step the one edge is removed between the target node and the community it has the fewest connections with.}
-        \label{3community train series}
-    \end{figure}
-
-    The three community was chosen as a best case scenario system to model.
-It has been constructed to avoid the challenges that are posed by the 2 community and long tail systems.
-That is, because in this system the target node is moving away from its least similar community, not moving from one community to another, it is not required to overcome the issue of symmetrical input.
-And because there are no long tails in this system, the SVD is able to capture a lot of the system with a low dimensional.
-
+    \begin{section}{Reconstructing the Temporal Network}
+        $u$ is the first row of the matrix $\hat L$.
+By taking $u\hat R'$, this is equivalent to finding $\hat A = \hat L \hat R'$ and looking at $\hat A_{1\cdot}$; to recover a final prediction of the edges of $u$, we take:
+        \begin{align}
+            q &= u \hat R'
+        \end{align}
+        This gives a vector $q$ of probabilities of connections between the target node and the rest of the network.
+As the results can be interpreted as a probability, the most likely graph is given by setting any entry with a value of $0.5$ or higher to one (predict that the edge exists), and setting any entry with a value of less than $0.5$ to zero (predict that an edge does not exist).
+However, this may not provide the best fit in terms of the accuracy of edges, and techniques to find the best threshold exist (for more information see \Citeauthor{strydomEtAl}\cite{strydomEtAl})
     \end{section}
-
-\begin{section}{Results and Discussion}
-    \subsection{Embedding Prediction}
-        For each of these systems, we took embedded the temporal network in two dimensions at each time step.
-The temporal embeddings were then divided into a training set of 20 and a testing set of 15.
-The output of the trained neural networks was then used to train a symbolic regression model that could use a simple set of addition, subtraction, and multiplication.
-
-        We predicted the evolution of the 2 community, long tail, and 3 community systems for 15 time steps after the training period using both a NNDE model and a symbolic regression model.
-
-        To compare our models, we look at the distance of the predictions to the embedding of the target node.
-Note that this does not include the loss from the SVD, which con be reduced by increasing the number of singular values taken in for the SVD.
-
-        To find the predicted probability of the edges of node $i$, $\mathbb{P}(i \leftrightarrow j:j\in V\smallsetminus \{i\})$, we use: 
-        \begin{align}
-            _tA_{i,\cdot} &\approxeq (\bar p) _t\hat R
-        \end{align}
-        Where $\bar p$ is the predicted location of the target node $i$ in the embedding at time $t$.
-
-        To find calculate the loss of our prediction at time $t$, we use:
-        \begin{align}
-            \bar j &= V \smallsetminus \{i\}  \\
-            L &= \frac{1}{||\bar j||}\sum{(_t\hat A_{i,\cdot} \hat R_{\cdot,\bar j} - (\bar p) _t\hat R_{\cdot,\bar j})^2}
-        \end{align}
-        That is the mean squared error between the probabilities given by the true embedding and the prediction.
-
-        When we do this for the SVD, NN, and symbolic regression, we get \autoref{loss_table}.
-        \begin{figure}
-            \begin{center}
-                \begin{tabular}{| m{0.17\textwidth} | m{0.25\textwidth} | m{0.25\textwidth} |}
-                    \hline
-                    Sequence & Neural Network Prediction Loss & Symbolic Regression Prediction Loss\\ 
-                    \hline
-                    \hline
-                    2 Community & 0.224 & 0.145 \\ 
-                    \hline 
-                    Long Tail  & 0.093 & 0.331 \\ 
-                    \hline 
-                    3 Community & 43.064 & 2.768 \\ 
-                    \hline 
-                \end{tabular}
-                \end{center}
-                \caption{A summary of the mean loss of the predictions at the fifth to ninth time steps.
-The neural network and symbolic prediction loss comes from the RDPG being reconstructed but with the position of the target node replaced with the location of the respective prediction.
-Loss is calculated as the mean squared error between the prediction predicted edge probability and the edge probability of the embedding.}
-                \label{loss_table}
-        \end{figure}
-
-        As can be seen in \autoref{loss_table}, the symbolic regression model performed better for both the 2 and 3 community system.
-However, for the long tail system the symbolic regression model performed notably worse.
-
-        The loss of one system should not be compared with another.
-That is the 2 community losses should not be compared to the long tail.
-This is because the long tail system will only ever have one edge to predict, whereas the 2 community will have 50 edges that need to be predicted.
-
-        Instead, we may compare predictions within the same system.
-However, we do not necessarily get a good understanding of the behaviour of our models with just this summary.
-We plot our predictions at every third time step to further understand the behavior of the models generated by our framework.
-
-    \subsection{Further Exploration}
-        In fig \autoref{2community series}, \autoref{longtail series},\autoref{3community series} the purple points are the embedded coordinates of the node in each of the communities.
-Each cluster is one separate community.
-The green point is the true coordinate of the embedded target node at each time step.
-The blue point is our neural network model prediction at each time step.
-The orange point is the symbolic regression prediction.
-
-        To illustrate how the changing structure of the network is represented in the embedding, we give a brief description of the movement of the target node throughout the 2 community system below.
-
-        As the time progresses, we see the true node move from one community cluster to the other.
-This is because, at the beginning of the training phase, the target node starts as very similar to the first community (as it has many connections with nodes in that community) and as time progresses, it gradually becomes less and less similar to the first community and more similar to the second (as the edges between the target node and the first community are replaced with edges to the second community).
-Because the SVD embeds nodes with many of the same connections close to each other, we see the target node move towards the second community.
-
-        \subsubsection{2 Community}
-            \begin{figure}
-                \foreach \i in {3,6,9,12,15} {%
-                    \begin{subfigure}[p]{0.4\textwidth}
-                        \includegraphics[width=\linewidth]{../Code/Plots/Test Only/2communities/2communities \i \space small net.png}
-                        \caption{t=\i}
-                        \label{2community series \i}
-                    \end{subfigure}\quad
-                }
-                \caption{2 Community test series.
-This series shows the comparison of the neural network model, the symbolic regression model trained on the neural network model, and the true solution of the two community system.}
-                \label{2community series}
-            \end{figure}
-            We see both the neural network model and the symbolic regression models follow quite closely to the target node throughout the test process.
-As we saw in \autoref{loss_table}, the NN model performs slightly worse than the symbolic regression model.
-This improvement of symbolic regression was present throughout the test period.
-
-            In spite of the simple movement of the target node, these close predictions were unexpected.
-When creating this system, we were looking to test how the model would perform with symmetrical input data.
-We hypothesised that this may be difficult for the NN model to learn, as it would need to learn to give the same output with opposite input.
-
-            In this case however, it seems that predicting the movement of the target node was not affected by this symmetry.
-
-        \subsubsection{Long Tail}
-            \begin{figure} 
-                \foreach \i in {3,6,9,12,15} {%
-                    \begin{subfigure}[p]{0.4\textwidth}
-                        \includegraphics[width=\linewidth]{../Code/Plots/Test Only/longTail/longTail \i \space small net.png}
-                        \caption{t=\i}
-                        \label{longtail series \i}
-                    \end{subfigure}\quad
-                }
-                \caption{Long Tail test series.
-This series shows the comparison of the neural network model, the symbolic regression model trained on the neural network model, and the true solution of the long tail system.}
-                \label{longtail series}
-            \end{figure}
-            In fig \autoref{longtail series} we see the true embedding of the target node move from one arm to the other between the time steps 9 and 12.
-It is clear that neither the symbolic regression model nor the neural network model capture this movement.
-
-            From \autoref{loss_table}, we see that the NN model had a higher accuracy than the symbolic regression.
-However, the NN model does not follow the true node; instead it stays in relatively the same spot, as opposed to the symbolic regression model, which does move.
-
-            We see that neither the neural network model capture the movement of the target node to any real extent.
-One reason for this may be that by the time the system progresses to the test section the number of nearest neighbours (k=15) means that the input for the model no longer includes the large community used to orient the system.
-Because of this, the model will essentially be given the same input at every time step, but will have to somehow produce the alternating behaviour of the target node.
-This again is an issue of symmetry.
-
-            The solutions to this symmetry in this problem would be to break the symmetry by including the absolute position of the target node as input for the model, or to have multiple time steps as input.
-
-            Another potential reason for the poor behavior could be that the embedding of the temporal network does not contain enough information to train a NNDE model.
-This is discussed in \autoref{longtaildata}.
-
-        \subsubsection{Three Community}
-            \begin{figure}
-                \foreach \i in {3,6,9,12,15} {%
-                    \begin{subfigure}[p]{0.4\textwidth}
-                        \includegraphics[width=\linewidth]{../Code/Plots/Test Only/3community/3community \i \space small net.png}
-                        \caption{t=\i}
-                        \label{3community series \i}
-                    \end{subfigure}\quad
-                }
-                \caption{3 community test series.
-This series shows the comparison of the neural network model, the symbolic regression model trained on the neural network model, and the true solution of the 3 community system.}
-                \label{3community series}
-            \end{figure}
-            In fig \autoref{3community series} we see the symbolic regression model move in roughly the same direction as the target node.
-The NN model however, moves quickly towards the bottom left, away from the target node.
-
-            In contrast, after the third time step, the symbolic regression model prediction maintains a relatively constant distance to the target node.
-
-            This system was constructed to avoid the symmetrical input of the other two systems. Because of this, it is interesting to see the poor predictive performance of the NN model.
-
-            We see that the symbolic regression model significantly improved the predictions, which supports the notion that symbolic regression, can give more robust predictive models than a NNDE alone.
-
-    \subsection{Summary}
-      In the 2 and 3 community systems, we see that symbolic regression improved the accuracy of the predictions across all time steps when compared to the NN model.
-This is especially prominent in the 3 community system.
-In the long tail system, where the symbolic regression model performed worse than the NN model, neither performed well, with the NN model remaining in relatively the same spot throughout the test period.
-
-\end{section}
-
-\begin{section}{Code}
-    \subsection{Summary}
-        The idea of this code is to provide a foundation for a streamline research into temporal network modelling.
-To that end it is planned to be compatible with popular Julia packages such as Graphs, the SciML ecosystem, and EcologicalNetworks.
-
-        The core of the code developed for this project is the TemporalNetworkEmbedding (TNE) structure.
-This structure was developed not only for me to be able to interface with data quickly and easily, but also so the SciML ecosystem could interface with it during training of the NN.
-In particular, the ability to index the TNE with a float was essential for the continuous time evolution of the UDEs and NNDEs to function.
-
-    \subsection{Statement of Need}
-        Throughout this thesis, we have demonstrated that temporal networks are found in many different areas, that, on small networks, temporal progression of embedded nodes can be modelled with NNDEs, and that there are still problems to be overcome.
-
-        With this in mind, the code has been developed to:
-
-            1: Allow for interface with popular packages
-
-            2: Allow for further exploration of optimal network structures for deep learning
-
-            3: Provide opportunities for collaboration of experts from other fields
-
-    \subsection{Package Methods}
-        In the package \cite{DotProductGraphs}, I created code for constructing:
-        % ADD NOTATION
-        The TemporalNetworkEmbedding structure.
-This structure stores the temporal network as tensors of the $\hat L, \hat R$ matrices.
-This structure has many methods for streamlining interactions with the TemporalNetworkEmbedding.
-These include indexing with integers and floats, where the floats will linearly interpolate between time steps.
-Other methods include viewing and or removing specific nodes from the network.
-
-        As well as constructRDPG, which takes a temporal network embedding and optionally the time steps of interest, and outputs the RDPG from the embedding.
-
-        I also added the nearestNeighbours method which takes a vector point in the dimension of the embedding, the time step, a TemporalNetworkEmbedding and the number of nearest neighbours required.
-The method then outputs the indices of the nearest nodes of the network to the vector in descending order.
-
-    \subsection{Comparable Methods and Related Work}
-    Teneto Python
-
-    packages("sna")  R
-    packages("tsna")
-    packages("ndtv")
-
-    EvolvingGraphs Julia
-
-    \subsection{Past and Ongoing Research}
-    Wrote code that is general
-
-    Made a structure (TemporalNetworkEmbedding)
-
-    Useful functions include nearestNeighbours, and constructRDPG.
-\end{section}
-% \begin{section}{Conclusion}
-%     In this paper, we proposed a novel framework for modelling temporal networks.
-We then tested this framework on three types of small, synthetic network sequences.
-Throughout these tests the neural network performed generally more poorly than the symbolic regression model, with the large three community sequence being especially notable due to th symbolic regression remaining so close to the target node throughout the test period.
-% \end{section}
-
-\printbibliography
+\end{chapter}
 
 \end{document}
-
-% draft for miguel
-% all absolute pos of nodes
-% polar positions
-
-% questions for Giulio:
-%     Why both NN and sym reg not just sym reg
-%     Why cos dist

### 2025-08-07 Analysis/analysis.jl
switch to 2D plots of L

@@ -6,33 +6,43 @@ using ComponentArrays, Lux, DiffEqFlux, OrdinaryDiffEq, Optimization, Optimizati
       OptimizationOptimisers, Random, Plots
 
 include("create_forecast.jl")
+n = 5
+d = 2
 
 
-function get_preds(data_index, data_path, model_path)
+function get_preds(data_index, data_path, model_path, n, d)
     data = JSON.parsefile(data_path)
     data = [[L[1] L[2]] for L in data[data_index]] 
-
-    forecast, tsteps = create_forecast(model_path, Array(reshape(data[1]', 10)))
-    preds = collect.(Array.(reshape.(forecast, 2,5))')
+    println(data[1])
+    forecast, tsteps = create_forecast(model_path, Array(reshape(data[1]', n*d)), n, d)
+    preds = collect.(Array.(reshape.(forecast, d,n))')
     return preds, data, tsteps
 end
 
-L_preds, L_data, tsteps = get_preds("L_series", "data/1_community_oscillation.json", "models/1_community_oscillation/25-07-2025-L.jls")
-R_preds, R_data, tsteps = get_preds("R_series", "data/1_community_oscillation.json", "models/1_community_oscillation/25-07-2025-R.jls")
+L_preds, L_data, tsteps = get_preds("L_series", "data/1_community_oscillation.json", "models/1_community_oscillation/big-NN-07-08-2025-L.jls", n, d)
 
 
 
+
+loss_seq = []
 for i in 1:30
     loss_matrix = L_preds[i]*(L_preds[i]*[1 0; 0 -1])'.-L_data[i]*(L_data[i]*[1 0; 0 -1])'
     # println(round.(abs.(loss_matrix[1,:]),sigdigits=2))
-    println(loss_matrix)
-    println("")
+    push!(loss_seq, sum(abs.(loss_matrix)))
 end
+
+
+
 
 gr()
 
 L_trace_d = hcat([d[1,:] for d in L_data]...)
 L_trace_p = hcat([p[1,:] for p in L_preds]...)
-plt = plot(1:tsteps, L_trace_d[1,:], L_trace_d[2,:]; label = "data")
-plot!(plt, 1:tsteps, L_trace_p[1,:], L_trace_p[2,:]; label = "prediction")
[…]

### 2025-08-07 generate_data/L_R_series.jl
round SVD digits to 10 to push towards 0

@@ -12,8 +12,8 @@ function L_R_series(d, tsteps)
 
     for i in 1:tsteps
         L, R = svd_decompose(series[i], convert(Int, d))
-        push!(L_series, L)
-        push!(R_series, R)
+        push!(L_series, round.(L, digits=10))
+        push!(R_series, round.(R, digits=10))
 
     end
     return L_series, R_series

### 2025-08-07 generate_data/1_community_oscilation/1_community_oscillation.jl
back to 2 SVDs

@@ -1,8 +1,5 @@
 using LinearAlgebra
-using BlockDiagonals
-using Arpack
-using DotProductGraphs
-using Distances
+using BlockDiagonals, Arpack, DotProductGraphs, Distances
 using JSON
 
 
@@ -11,23 +8,24 @@ include("../L_R_series.jl")
 tsteps = 30
 
 n = 5 # Total number of nodes in the network
-d = 4 # Number of dimentions to find for SVD
+d = 2 # Number of dimentions to find for SVD
 c = n-1 # Size of the community; Always one less than total number of nodes
 
 series = create_series(c, tsteps)
 L_series, R_series = L_R_series(d, tsteps) # Note that this version no longer uses ortho procrustes, as Dot Product reconstruction is much worse, with little improvement in cos distances. 
 
-series[]
+
 
 i=2
 series[i]
 L_series[i]*R_series[i]
-ltest = [L_series[i]*(L_series[i]*[1 0 0; 0 -1 0;0 0 -1 ])' for i in eachindex(L_series)]
+ltest = [L_series[i]*(L_series[i]*[1 0; 0 -1 ])' for i in eachindex(L_series)]
 rtest = [L_series[i]*R_series[i]' for i in eachindex(L_series)]
 
 unique(ltest .≈ rtest)
 
-
+L_series[2]
+R_series[2]
 
 data_dict = Dict("graph_series"=>series, "L_series"=>L_series, "R_series"=>R_series)
 

### 2025-08-14 paper/paper.tex
latex stuff

@@
 
-    \begin{        Initial vector is [1 2 3 4 ... mod 7] (Double check)
-        Initial vector is used to align the vectors but it kind of doesn't work
-section}{Singular Value Decomposition and Random Dot Product Graphs}
+    \begin{section}{Singular Value Decomposition and Random Dot Product Graphs}
         SVD Calculated with XXX Arpack XXX Julia
         Each system has 2 singular values
+        Aligning The L and R matrices is important (The SVDs can each be fliped)
+        We use an initial vector to ensure that the first eigenvector is oriented the same for each time step
+        Then calculate a transformation for the subsequent eigenvectors, which is used for training loss and prediction.
         L and R are related by [1 0; 0 -1] as the network is not directed (IE the matrix is symetrical) 
@@
     \begin{section}{Reconstructing the Temporal Network}
+        XXX Is this necessary XXX
+
         $u$ is the first row of the matrix $\hat L$.

### 2025-08-14 symbolic_regression/symbolic_regression.jl
use symbolic regression to approximate NODE

@@ -1,0 +1,88 @@
+import MLJ: machine, fit!, predict, report
+using ComponentArrays, Lux, DiffEqFlux, OrdinaryDiffEq, Optimization, OptimizationOptimJL,
+      OptimizationOptimisers, Random, Plots
+using JSON
+# Dataset with two named features:
+# Aim: f(x)=x'
+# Ie NN(x)=y
+using Serialization
+import SymbolicRegression: Options, equation_search
+u = deserialize("models/1_community_oscillation/big-NN-07-08-2025-L.jls")
+data = JSON.parsefile("data/1_community_oscillation.json")
+
+datasize = 10
+tspan = (0.0f0, 9.0f0)
+
+n = 5
+d = 2
+u0 = reshape(hcat(data["L_series"][1]...), n*d, 1)
+
+L_data = [Float64.([L[1]; L[2]])[:,:] for L in data["L_series"]]
+
+
+tsteps = range(tspan[1], tspan[2]; length = datasize)
+
+
+rng = Xoshiro(0)
+
+dudt2 = Chain(x -> x, Dense(n*d, 256, celu), Dense(256, 128, celu), Dense(128, 128, celu), Dense(128, n*d))
+p, st = Lux.setup(rng, dudt2)
+prob_neuralode = NeuralODE(dudt2, tspan, Tsit5(); saveat = tsteps)
+
+
+
+X = L_data
+test = dudt2(X[1], u, st)
+
+Y = [dudt2(x, u, st)[1] for x in X]
+
+X̂ = hcat(X...)
+Ŷ = hcat(Y...)
+
+options = Options(
+    populations=25,
+    binary_operators=[+, -, *],
+    unary_operators=[cos, sin],
+    should_optimize_constants=true,
+    should_simplify=true,
+)
+
+hall_of_fame = equation_search(
+    X̂, Ŷ, niterations=50, options=options,
+    parallelism=:multithreading
+)
+
+import SymbolicRegression: calculate_pareto_frontier
+
+dominating = calculate_pareto_frontier.(hall_of_fame)
+trees = [d[5].tree for d in dominating]
+
+
+import SymbolicRegression: eval_tree_array
+
+function dudt2_symb(X)::Matrix{Float64}
+    output = eval_tree_array.(trees, [X], [options])
+    Y = collect(hcat([o[1] for o in output]...)')
+    return Y
+
+end
+
[…]
